---
title: "Adiposity Radiomics"
author: "Christelle Colin-Leitzinger"
date: '`r Sys.Date()`'
output: 
  html_document:
    toc: true
    toc_float: true
    toc_collapsed: false
    theme: united
    highlight: pygments
    df_print: paged
editor_options: 
  chunk_output_type: console
---

<style type="text/css">

.figure {
   margin-top: 25px;
   margin-bottom: 100px;
}

table {
    margin-top: 10px;
    margin-bottom: 25px;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE,
                      cache = FALSE,
                      fig.align='center'
                      )
options(gtsummary.print_engine = "gt")
options(gtsummary.as_gt.addl_cmds = "gt::tab_options(table.font.size = 14, data_row.padding = gt::px(1))")
```

```{r library}
library(tidyverse)
library(ggplot2)
library(mclust)
library(data.table)
library(gtsummary)
library(survival)
library(survminer)
# library(VIM)
library(mice)
```

```{r load test-retest}
# path <- fs::path("","Volumes","Peres_Research", "Ovarian - Radiomics", "CTbased adiposity")

adipose_data <- read_rds(paste0(here::here(), "/adipose_data.rds")) %>% 
  mutate(debulking_status = as.factor(debulking_status))
```

<br>

Note: I excluded the patient noted in "should exclude" variable.  
Also the patient with missing TNM was removed.  

<br>

***

# Data summary
## Table 1. Patient characteristics overall

```{r}
adipose_data %>% 
  select(age_at_diagnosis, year_of_diagnosis, raceeth, raceeth1,
         treatment_type, 
         debulking_status, tnm_cs_mixed_group_stage, ecog_pretrt, 
         preDx_comorbidities, preDx_hypertension, preDx_diabetes_mellitus, 
         preDx_hypercholesterolemia, preDx_cardiac_conditions, 
         preDx_chronic_kidney_disease, 
         ascites,
         vital_new, os_time, 
         has_the_patient_recurred, recurrence_time) %>% 
  
  tbl_summary(
    type = list(year_of_diagnosis ~ "categorical", 
                          all_dichotomous() ~ "categorical"), 
            statistic=list(all_continuous() ~ "{mean} ({sd})"), 
            digits = all_continuous() ~ 1
    ) %>%  
  bold_labels() %>% add_stat_label() %>% 
  modify_footnote(update = everything() ~ NA)
```

### Imputation for debulking_status

Select the variables that may be important for predicting debulking status: 
id, recurrence_time, rec_event, debulking_status,
         weight, height_cms_, bmi_cat,
         thickness, muscle_area_cm2, muscle_area_cm2_ind,
         imat_area_cm2, imat_area_cm2_ind,
         vat_area_cm2, vat_area_cm2_ind,
         sat_area_cm2, sat_area_cm2_ind,
         muscle_mean_hu, v_s_ratio, 
         total_fat_area, total_fat_area_ind,
         tnm_cs_mixed_group_stage, treatment_type,
         age_at_diagnosis, histology,
         raceeth1, grade_differentiation,
         starts_with("preDx"), starts_with("postDx")

```{r}
data <- adipose_data %>% 
  select(id, recurrence_time, rec_event, debulking_status,
         weight, height_cms_, bmi_cat,
         thickness, muscle_area_cm2, muscle_area_cm2_ind,
         imat_area_cm2, imat_area_cm2_ind,
         vat_area_cm2, vat_area_cm2_ind,
         sat_area_cm2, sat_area_cm2_ind,
         muscle_mean_hu, v_s_ratio, 
         total_fat_area, total_fat_area_ind,
         tnm_cs_mixed_group_stage, treatment_type,
         age_at_diagnosis, histology,
         raceeth1, grade_differentiation,
         starts_with("preDx"), starts_with("postDx")
  
)
nonimp_cox_model <-
  coxph(Surv(recurrence_time, rec_event) ~ 
          raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type + bmi_cat, 
        data =  adipose_data)
nonimp_cox_model
Hazard <- nelsonaalen(data, recurrence_time, rec_event)
dataset <- data.frame(data, Hazard)
```

Start imputation to look at matrix
```{r}
Cox.imp <- mice(dataset, m=1, maxit=0, seed=123, printFlag=F)
# summary(Cox.imp)
Pred <- Cox.imp$predictorMatrix
# Pred["debulking", "recurrence_time"] <- 0
Pred
```

id is used and treatment_type IS NOT.
```{r}
Pred[, "id"] <- 0
Pred[, "treatment_type"] <- 1
Pred["treatment_type", "treatment_type"] <- 0
Pred
```

Imputation and cox regression model on imputed data using the new predictor matrix.
```{r}
# Start imputations using mice
Cox.imp <- mice(dataset, m=5, maxit=50, 
                predictorMatrix=Pred,
                seed=123, printFlag=F)
check1 <- with(data = Cox.imp,
       exp = coxph(
         Surv(recurrence_time, rec_event) ~ 
          raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type + bmi_cat
       ))
pool(check1)$pooled
```

Do m = 10 (how to choose is explained in https://www.ebpi.uzh.ch/dam/jcr:dc0cef17-29c7-4e61-8d33-e690561ab7ae/mi_intro20191001.pdf depends of the fmi. The max fmi = 0.1 that we multiply by 100)
```{r}
Cox.imp <- mice(dataset, m=34, maxit=50, 
                predictorMatrix=Pred,
                seed=123, printFlag=F)
fit.Cox <-
  with(data = Cox.imp,
       exp = coxph(
         Surv(recurrence_time, rec_event) ~ 
          raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type + bmi_cat
       ))
summary(pool(fit.Cox), conf.int = TRUE, exponentiate = TRUE) %>%
  kableExtra::kable() %>%
  kableExtra::kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```

Above results are exponentiated (imputed data).  
As a reminder before imputation results are :
```{r}
nonimp_cox_model
```

Complete the data and merge with original
```{r}
imputed_data <- complete(Cox.imp, include = FALSE) %>% 
  rename(imp_debulking_status = debulking_status)

adipose_data <- 
  full_join(adipose_data, imputed_data %>% 
              select(id, starts_with("imp_")), 
            by = "id") 
```












# ```{r}
# adipose_data1 <- adipose_data %>% 
#   select(-c(ecog_posttrt, ecog_recurr, has_the_patient_recurredafter_surg,
#             contains("date"), contains("months"), contains("age")),
#          age_at_surgery)
# 
# imputed_Data <- mice(adipose_data1, m=5, maxit = 50, seed = 500)
# # summary(imputed_Data)
# # table(imputed_Data$imp$debulking_status[1])
# ```

<!-- Proportion of debulking status in the imputed data -->
# ```{r}
# prop.table(table(imputed_Data$imp$debulking_status[4]))*100
# #get complete data ( 2nd out of 5)
# completeData <- complete(imputed_Data,4)
# 
# ##### EXTRA #####
# # Also, if you wish to build models on all 5 datasets, 
# # you can do it in one go using with() command. 
# # You can also combine the result from these models and obtain 
# # a consolidated output using pool() command.
# #build predictive model
# # fit <- with(data = iris.mis, exp = lm(Sepal.Width ~ Sepal.Length + Petal.Width)) 
# #combine results of all 5 models
# # combine <- pool(fit)
# # summary(combine)
# ##### _____ #####
# 
# adipose_data <- adipose_data %>% 
#   mutate(mrn = as.character(mrn)) %>%
#   select(-debulking_status) %>% 
#   full_join(.,
#             completeData %>% 
#               select(mrn, debulking_status),
#             by = "mrn")
# ```


New table:
```{r}
adipose_data %>% 
  select(age_at_diagnosis, year_of_diagnosis, raceeth, raceeth1,
         treatment_type, 
         debulking_status, imp_debulking_status,
         tnm_cs_mixed_group_stage, ecog_pretrt, 
         preDx_comorbidities, preDx_hypertension, preDx_diabetes_mellitus, 
         preDx_hypercholesterolemia, preDx_cardiac_conditions, 
         preDx_chronic_kidney_disease, 
         ascites,
         vital_new, os_time, bmi,
         has_the_patient_recurred, recurrence_time) %>% 
  
  tbl_summary(
    type = list(year_of_diagnosis ~ "categorical", 
                          all_dichotomous() ~ "categorical"), 
            statistic=list(all_continuous() ~ "{mean} ({sd})"), 
            digits = all_continuous() ~ 1
    ) %>%  
  bold_labels() %>% add_stat_label() %>% 
  modify_footnote(update = everything() ~ NA)
```

## Table 2. CT-based measures of adiposity

```{r}
tbl1 <- adipose_data %>% 
  select(thickness, muscle_area_cm2, muscle_area_cm2_ind,
         imat_area_cm2, imat_area_cm2_ind,
         vat_area_cm2, vat_area_cm2_ind,
         sat_area_cm2, sat_area_cm2_ind,
         muscle_mean_hu,                    
         v_s_ratio, 
         total_fat_area, total_fat_area_ind) %>% 
  tbl_summary(
            statistic=list(all_continuous() ~ "{mean} ({sd})"), 
            digits = all_continuous() ~ 1
            ) %>%  
  bold_labels() %>% 
  modify_header(
    update = list(
      stat_0 ~ "**Mean (SD)**"))

tbl2 <- adipose_data %>% 
  select(thickness, muscle_area_cm2, muscle_area_cm2_ind,
         imat_area_cm2, imat_area_cm2_ind,
         vat_area_cm2, vat_area_cm2_ind,
         sat_area_cm2, sat_area_cm2_ind,
         muscle_mean_hu,                    
         v_s_ratio, 
         total_fat_area, total_fat_area_ind) %>% 
  tbl_summary(
            statistic=list(all_continuous() ~ "{median}"), 
            digits = all_continuous() ~ 1
            ) %>%  
  bold_labels()  %>% 
  modify_header(
    update = list(
      stat_0 ~ "**Median**"))
tbl3 <- adipose_data %>% 
  select(thickness, muscle_area_cm2, muscle_area_cm2_ind,
         imat_area_cm2, imat_area_cm2_ind,
         vat_area_cm2, vat_area_cm2_ind,
         sat_area_cm2, sat_area_cm2_ind,
         muscle_mean_hu,                    
         v_s_ratio, 
         total_fat_area, total_fat_area_ind) %>% 
  tbl_summary(
            statistic=list(all_continuous() ~ "{min} - {max}"), 
            digits = all_continuous() ~ 1
            ) %>%  
  bold_labels() %>% 
  modify_header(
    update = list(
      stat_0 ~ "**Range**"))
tbl_merge(list(tbl1, tbl2, tbl3)) %>%
  modify_spanning_header(everything() ~ NA_character_)
```

```{r, fig.width= 12, fig.height= 12}
# adipose_data %>% 
#   select(mrn, bmi_cat,
#          "muscle_area_cm2", muscle_area_cm2_ind,
#          imat_area_cm2, imat_area_cm2_ind,
#          vat_area_cm2, vat_area_cm2_ind,
#          sat_area_cm2, sat_area_cm2_ind,
#          "total_fat_area", total_fat_area_ind,
#          muscle_mean_hu,                    
#          imat_mean_hu,
#          muscle_hu_sd, v_s_ratio) %>% 
#   pivot_longer(-c(mrn, bmi_cat)) %>% 
#   ggplot(aes(x= name, y= value, color = bmi_cat))+
#   geom_boxplot()+
#   theme_minimal()+
#   coord_flip()

adipose_data %>% 
  select(mrn, bmi_cat,
         muscle_area_cm2, muscle_area_cm2_ind,
         imat_area_cm2, imat_area_cm2_ind,
         vat_area_cm2, vat_area_cm2_ind,
         sat_area_cm2, sat_area_cm2_ind,
         total_fat_area, total_fat_area_ind,
         muscle_mean_hu,                    
         v_s_ratio) %>% 
  pivot_longer(-c(mrn, bmi_cat)) %>% 
  mutate(name = factor(name, 
                       levels = c(
                         "muscle_area_cm2", "muscle_area_cm2_ind",
                         "imat_area_cm2", "imat_area_cm2_ind",
                         "vat_area_cm2", "vat_area_cm2_ind",
                         "sat_area_cm2", "sat_area_cm2_ind",
                         "total_fat_area", "total_fat_area_ind",
                         "muscle_mean_hu",                    
                         "v_s_ratio"
                       ))) %>% 
  ggplot(aes(x= bmi_cat, y= value, color = bmi_cat))+
  geom_boxplot()+
  theme_minimal()+
  coord_flip()+
  # facet_grid(cols = vars(name), scales = "free")
  facet_wrap(.~ name, scales = "free", ncol = 2)
```
<br>

```{r}
adipose_data %>% 
  select(muscle_area_cm2, muscle_area_cm2_ind,
         imat_area_cm2, imat_area_cm2_ind,
         vat_area_cm2, vat_area_cm2_ind,
         sat_area_cm2, sat_area_cm2_ind,
         muscle_mean_hu,                    
         v_s_ratio, 
         total_fat_area, total_fat_area_ind,
         treatment_type) %>% 
  tbl_summary(by = treatment_type,
            statistic=list(all_continuous() ~ "{mean} ({sd})"), 
            digits = all_continuous() ~ 1
            ) %>%  
  bold_labels() %>% add_p() %>% bold_p(t= 0.05)
```
<br>

<!-- ## Unknown debulking_status look like Complete/Optimal debulking_status -->

```{r}
# data <- adipose_data %>% 
#   mutate(debulking_status = case_when(
#     is.na(debulking_status)           ~ "unkn",
#     TRUE                              ~ debulking_status
#   ))
# mysurv <- Surv(data$recurrence_time, event = data$rec_event)
# myplot <- survfit(mysurv~debulking_status, data = data)
# ggsurvplot(myplot, data = data,
#            title = "Recurrence Analysis",
#            font.main = c(20, "bold", "black"),
#            font.x = c(18, "bold", "black"),
#            font.y = c(18, "bold", "black"),
#            font.legend = c(16, "black"),
#            font.tickslab = c(16, "bold", "black"),
#            size = 1.5,
# 
#            xlab = "Time in months",
#            legend = "top",
#            legend.title = "",
#            pval = TRUE,
#            conf.int = FALSE,
#            # Censor
#            censor = TRUE
# ) + guides(colour = guide_legend(ncol = 1))
# ```
# ```{r}
# mysurv <- Surv(data$os_time, event = data$os_event)
# myplot <- survfit(mysurv~debulking_status, data = data)
# ggsurvplot(myplot, data = data,
#            title = "OS Analysis",
#            font.main = c(20, "bold", "black"),
#            font.x = c(18, "bold", "black"),
#            font.y = c(18, "bold", "black"),
#            font.legend = c(16, "black"),
#            font.tickslab = c(16, "bold", "black"),
#            size = 1.5,
# 
#            xlab = "Time in months",
#            legend = "top",
#            legend.title = "",
#            pval = TRUE,
#            conf.int = FALSE,
#            # Censor
#            censor = TRUE
# ) + guides(colour = guide_legend(ncol = 1))
```
<br>

## KM BMI (unknown debulking status are not removed)
<br>

```{r echo=TRUE}
# BMI cat grouping
# (bmi_cat = case_when(
#     bmi < 25                    ~ "Underweight and normal weight",
#     bmi >= 25 &
#       bmi < 30                  ~ "Overweight",
#     bmi >= 30                   ~ "Obese"
#   ))
```

```{r}
mysurv <- Surv(adipose_data$recurrence_time, event = adipose_data$rec_event)
myplot <- survfit(mysurv~bmi_cat, data = adipose_data)
ggsurvplot(myplot, data = adipose_data,
           title = "Recurrence Analysis",
           font.main = c(20, "bold", "black"),
           font.x = c(18, "bold", "black"),
           font.y = c(18, "bold", "black"),
           font.legend = c(16, "black"),
           font.tickslab = c(16, "bold", "black"),
           size = 1.5,

           xlab = "Time in months",
           legend = "top",
           legend.title = "",
           # legend.labs = c("White Non-Hispanic", "Hispanic", "Black"),
           # palette = c("#03051AFF", "blue", "red"),
           pval = TRUE,
           conf.int = FALSE,
           # Censor
           censor = TRUE
) + guides(colour = guide_legend(ncol = 1))
```

```{r}
tbl1 <- adipose_data %>% select(rec_event, recurrence_time,
                            raceeth1, age_at_diagnosis, tnm_cs_mixed_group_stage, 
                            treatment_type, #debulking_status, 
                            bmi, bmi_cat) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$recurrence_time,
                             event = adipose_data$rec_event)),
                   exponentiate = TRUE) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <- 
  coxph(Surv(time = adipose_data$recurrence_time,
             event = adipose_data$rec_event) ~ raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type + bmi_cat, data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))
```

```{r}
mysurv <- Surv(adipose_data$os_time, event = adipose_data$os_event)
myplot <- survfit(mysurv~bmi_cat, data = adipose_data)
ggsurvplot(myplot, data = adipose_data,
           title = "OS Analysis",
           font.main = c(20, "bold", "black"),
           font.x = c(18, "bold", "black"),
           font.y = c(18, "bold", "black"),
           font.legend = c(16, "black"),
           font.tickslab = c(16, "bold", "black"),
           size = 1.5,

           xlab = "Time in months",
           legend = "top",
           legend.title = "",
           # legend.labs = c("White Non-Hispanic", "Hispanic", "Black"),
           # palette = c("#03051AFF", "blue", "red"),
           pval = TRUE,
           conf.int = FALSE,
           # Censor
           censor = TRUE
) + guides(colour = guide_legend(ncol = 1))
```

```{r}
tbl1 <- adipose_data %>% select(os_event, os_time,
                            raceeth1, age_at_diagnosis, tnm_cs_mixed_group_stage, 
                            treatment_type, #debulking_status, 
                            bmi, bmi_cat) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$os_time,
                             event = adipose_data$os_event)),
                   exponentiate = TRUE) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <- 
  coxph(Surv(time = adipose_data$os_time,
             event = adipose_data$os_event) ~ raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type + bmi_cat, data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))
```
<br>
<br>

### Stratified by stage
```{r}
stage1_2 <- adipose_data %>% filter(tnm_cs_mixed_group_stage == "I-II")
stage3 <- adipose_data %>% filter(tnm_cs_mixed_group_stage == "III")
stage4 <- adipose_data %>% filter(tnm_cs_mixed_group_stage == "IV")
```

#### Recurrence

<div class = "row">
<div class = "col-md-4">
```{r}
myplot <- survfit(Surv(recurrence_time, event = rec_event) ~ bmi_cat, data = stage1_2)
ggsurvplot(myplot, data = stage1_2,
           title = "Recurrence Analysis in stage I-II",
           font.main = c(20, "bold", "black"),
           font.x = c(18, "bold", "black"),
           font.y = c(18, "bold", "black"),
           font.legend = c(16, "black"),
           font.tickslab = c(16, "bold", "black"),
           size = 1.5,

           xlab = "Time in months",
           legend = "top",
           legend.title = "",
           # legend.labs = c("White Non-Hispanic", "Hispanic", "Black"),
           # palette = c("#03051AFF", "blue", "red"),
           pval = TRUE,
           conf.int = FALSE,
           # Censor
           censor = TRUE
) + guides(colour = guide_legend(ncol = 1))

tbl1 <- stage1_2 %>% select(rec_event, recurrence_time,
                            raceeth1, age_at_diagnosis, 
                            treatment_type, #debulking_status, 
                            bmi, bmi_cat) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = stage1_2$recurrence_time,
                             event = stage1_2$rec_event)),
                   exponentiate = TRUE) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <- 
  coxph(Surv(time = stage1_2$recurrence_time,
             event = stage1_2$rec_event) ~ raceeth1 + age_at_diagnosis + treatment_type + bmi_cat, data =  stage1_2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))
```
</div>

<div class = "col-md-4">
```{r}
myplot <- survfit(Surv(recurrence_time, event = rec_event) ~ bmi_cat, data = stage3)
ggsurvplot(myplot, data = stage3,
           title = "Recurrence Analysis in stage III",
           font.main = c(20, "bold", "black"),
           font.x = c(18, "bold", "black"),
           font.y = c(18, "bold", "black"),
           font.legend = c(16, "black"),
           font.tickslab = c(16, "bold", "black"),
           size = 1.5,

           xlab = "Time in months",
           legend = "top",
           legend.title = "",
           # legend.labs = c("White Non-Hispanic", "Hispanic", "Black"),
           # palette = c("#03051AFF", "blue", "red"),
           pval = TRUE,
           conf.int = FALSE,
           # Censor
           censor = TRUE
) + guides(colour = guide_legend(ncol = 1))

tbl1 <- stage3 %>% select(rec_event, recurrence_time,
                            raceeth1, age_at_diagnosis, 
                            treatment_type, #debulking_status, 
                            bmi, bmi_cat) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = stage3$recurrence_time,
                             event = stage3$rec_event)),
                   exponentiate = TRUE) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <- 
  coxph(Surv(time = stage3$recurrence_time,
             event = stage3$rec_event) ~ raceeth1 + age_at_diagnosis + treatment_type + bmi_cat, data =  stage3) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))
```
</div>

<div class = "col-md-4">
```{r}
myplot <- survfit(Surv(recurrence_time, event = rec_event) ~ bmi_cat, data = stage4)
ggsurvplot(myplot, data = stage4,
           title = "Recurrence Analysis in stage IV",
           font.main = c(20, "bold", "black"),
           font.x = c(18, "bold", "black"),
           font.y = c(18, "bold", "black"),
           font.legend = c(16, "black"),
           font.tickslab = c(16, "bold", "black"),
           size = 1.5,

           xlab = "Time in months",
           legend = "top",
           legend.title = "",
           # legend.labs = c("White Non-Hispanic", "Hispanic", "Black"),
           # palette = c("#03051AFF", "blue", "red"),
           pval = TRUE,
           conf.int = FALSE,
           # Censor
           censor = TRUE
) + guides(colour = guide_legend(ncol = 1))

tbl1 <- stage4 %>% select(rec_event, recurrence_time,
                            raceeth1, age_at_diagnosis, 
                            treatment_type, #debulking_status, 
                            bmi, bmi_cat) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = stage4$recurrence_time,
                             event = stage4$rec_event)),
                   exponentiate = TRUE) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <- 
  coxph(Surv(time = stage4$recurrence_time,
             event = stage4$rec_event) ~ raceeth1 + age_at_diagnosis + treatment_type + bmi_cat, data =  stage4) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))
```
</div>
</div>

#### OS

<div class = "row">
<div class = "col-md-4">
```{r}
myplot <- survfit(Surv(os_time, event = os_event) ~ bmi_cat, data = stage1_2)
ggsurvplot(myplot, data = stage1_2,
           title = "OS Analysis in stage I-II",
           font.main = c(20, "bold", "black"),
           font.x = c(18, "bold", "black"),
           font.y = c(18, "bold", "black"),
           font.legend = c(16, "black"),
           font.tickslab = c(16, "bold", "black"),
           size = 1.5,

           xlab = "Time in months",
           legend = "top",
           legend.title = "",
           # legend.labs = c("White Non-Hispanic", "Hispanic", "Black"),
           # palette = c("#03051AFF", "blue", "red"),
           pval = TRUE,
           conf.int = FALSE,
           # Censor
           censor = TRUE
) + guides(colour = guide_legend(ncol = 1))

tbl1 <- stage1_2 %>% select(os_event, os_time,
                            raceeth1, age_at_diagnosis, 
                            treatment_type, #debulking_status, 
                            bmi, bmi_cat) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = stage1_2$os_time,
                             event = stage1_2$os_event)),
                   exponentiate = TRUE) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <- 
  coxph(Surv(time = stage1_2$os_time,
             event = stage1_2$os_event) ~ raceeth1 + age_at_diagnosis + treatment_type + bmi_cat, data =  stage1_2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))
```
</div>

<div class = "col-md-4">
```{r}
myplot <- survfit(Surv(os_time, event = os_event) ~ bmi_cat, data = stage3)
ggsurvplot(myplot, data = stage3,
           title = "OS Analysis in stage I-II",
           font.main = c(20, "bold", "black"),
           font.x = c(18, "bold", "black"),
           font.y = c(18, "bold", "black"),
           font.legend = c(16, "black"),
           font.tickslab = c(16, "bold", "black"),
           size = 1.5,

           xlab = "Time in months",
           legend = "top",
           legend.title = "",
           # legend.labs = c("White Non-Hispanic", "Hispanic", "Black"),
           # palette = c("#03051AFF", "blue", "red"),
           pval = TRUE,
           conf.int = FALSE,
           # Censor
           censor = TRUE
) + guides(colour = guide_legend(ncol = 1))

tbl1 <- stage3 %>% select(os_event, os_time,
                            raceeth1, age_at_diagnosis, 
                            treatment_type, #debulking_status, 
                            bmi, bmi_cat) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = stage3$os_time,
                             event = stage3$os_event)),
                   exponentiate = TRUE) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <- 
  coxph(Surv(time = stage3$os_time,
             event = stage3$os_event) ~ raceeth1 + age_at_diagnosis + treatment_type + bmi_cat, data =  stage3) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))
```
</div>

<div class = "col-md-4">
```{r}
myplot <- survfit(Surv(os_time, event = os_event) ~ bmi_cat, data = stage4)
ggsurvplot(myplot, data = stage4,
           title = "OS Analysis in stage I-II",
           font.main = c(20, "bold", "black"),
           font.x = c(18, "bold", "black"),
           font.y = c(18, "bold", "black"),
           font.legend = c(16, "black"),
           font.tickslab = c(16, "bold", "black"),
           size = 1.5,

           xlab = "Time in months",
           legend = "top",
           legend.title = "",
           # legend.labs = c("White Non-Hispanic", "Hispanic", "Black"),
           # palette = c("#03051AFF", "blue", "red"),
           pval = TRUE,
           conf.int = FALSE,
           # Censor
           censor = TRUE
) + guides(colour = guide_legend(ncol = 1))

tbl1 <- stage4 %>% select(os_event, os_time,
                            raceeth1, age_at_diagnosis, 
                            treatment_type, #debulking_status, 
                            bmi, bmi_cat) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = stage4$os_time,
                             event = stage4$os_event)),
                   exponentiate = TRUE) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <- 
  coxph(Surv(time = stage4$os_time,
             event = stage4$os_event) ~ raceeth1 + age_at_diagnosis + treatment_type + bmi_cat, data =  stage4) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))
```
</div>
</div>

## KM ascites

<div class = "row">
<div class = "col-md-6">
```{r}
myplot <- survfit(Surv(recurrence_time, event = rec_event) ~ ascites, data = adipose_data)
ggsurvplot(myplot, data = adipose_data,
           title = "Recurrence Analysis",
           font.main = c(20, "bold", "black"),
           font.x = c(18, "bold", "black"),
           font.y = c(18, "bold", "black"),
           font.legend = c(16, "black"),
           font.tickslab = c(16, "bold", "black"),
           size = 1.5,

           xlab = "Time in months",
           legend = "top",
           legend.title = "",
           # legend.labs = c("White Non-Hispanic", "Hispanic", "Black"),
           # palette = c("#03051AFF", "blue", "red"),
           pval = TRUE,
           conf.int = FALSE,
           # Censor
           censor = TRUE
) + guides(colour = guide_legend(ncol = 1))

tbl1 <- adipose_data %>% select(rec_event, recurrence_time,
                            raceeth1, age_at_diagnosis, 
                            tnm_cs_mixed_group_stage,
                            treatment_type, #debulking_status, 
                            bmi, ascites) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$recurrence_time,
                             event = adipose_data$rec_event)),
                   exponentiate = TRUE) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <- 
  coxph(Surv(time = adipose_data$recurrence_time,
             event = adipose_data$rec_event) ~ 
          raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type + bmi + ascites, 
        data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))
```
</div>

<div class = "col-md-6">
```{r}
myplot <- survfit(Surv(os_time, event = os_event) ~ ascites, data = adipose_data)
ggsurvplot(myplot, data = adipose_data,
           title = "OS Analysis",
           font.main = c(20, "bold", "black"),
           font.x = c(18, "bold", "black"),
           font.y = c(18, "bold", "black"),
           font.legend = c(16, "black"),
           font.tickslab = c(16, "bold", "black"),
           size = 1.5,

           xlab = "Time in months",
           legend = "top",
           legend.title = "",
           # legend.labs = c("White Non-Hispanic", "Hispanic", "Black"),
           # palette = c("#03051AFF", "blue", "red"),
           pval = TRUE,
           conf.int = FALSE,
           # Censor
           censor = TRUE
) + guides(colour = guide_legend(ncol = 1))

tbl1 <- adipose_data %>% select(os_event, os_time,
                            raceeth1, age_at_diagnosis, 
                            tnm_cs_mixed_group_stage,
                            treatment_type, #debulking_status, 
                            bmi, ascites) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$os_time,
                             event = adipose_data$os_event)),
                   exponentiate = TRUE) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <- 
  coxph(Surv(time = adipose_data$os_time,
             event = adipose_data$os_event) ~ 
          raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type + bmi + ascites, 
        data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))
```
</div>
</div>

### Stratified by stage
#### Recurrence

<div class = "row">
<div class = "col-md-4">
```{r}
myplot <- survfit(Surv(recurrence_time, event = rec_event) ~ ascites, data = stage1_2)
ggsurvplot(myplot, data = stage1_2,
           title = "Recurrence Analysis in stage I-II",
           font.main = c(20, "bold", "black"),
           font.x = c(18, "bold", "black"),
           font.y = c(18, "bold", "black"),
           font.legend = c(16, "black"),
           font.tickslab = c(16, "bold", "black"),
           size = 1.5,

           xlab = "Time in months",
           legend = "top",
           legend.title = "",
           # legend.labs = c("White Non-Hispanic", "Hispanic", "Black"),
           # palette = c("#03051AFF", "blue", "red"),
           pval = TRUE,
           conf.int = FALSE,
           # Censor
           censor = TRUE
) + guides(colour = guide_legend(ncol = 1))

tbl1 <- stage1_2 %>% select(rec_event, recurrence_time,
                            raceeth1, age_at_diagnosis, 
                            treatment_type, #debulking_status, 
                            bmi, ascites) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = stage1_2$recurrence_time,
                             event = stage1_2$rec_event)),
                   exponentiate = TRUE) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <- 
  coxph(Surv(time = stage1_2$recurrence_time,
             event = stage1_2$rec_event) ~ 
          raceeth1 + age_at_diagnosis + treatment_type + bmi + ascites, 
        data =  stage1_2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))
```
</div>

<div class = "col-md-4">
```{r}
myplot <- survfit(Surv(recurrence_time, event = rec_event) ~ ascites, data = stage3)
ggsurvplot(myplot, data = stage3,
           title = "Recurrence Analysis in stage III",
           font.main = c(20, "bold", "black"),
           font.x = c(18, "bold", "black"),
           font.y = c(18, "bold", "black"),
           font.legend = c(16, "black"),
           font.tickslab = c(16, "bold", "black"),
           size = 1.5,

           xlab = "Time in months",
           legend = "top",
           legend.title = "",
           # legend.labs = c("White Non-Hispanic", "Hispanic", "Black"),
           # palette = c("#03051AFF", "blue", "red"),
           pval = TRUE,
           conf.int = FALSE,
           # Censor
           censor = TRUE
) + guides(colour = guide_legend(ncol = 1))

tbl1 <- stage3 %>% select(rec_event, recurrence_time,
                            raceeth1, age_at_diagnosis, 
                            treatment_type, #debulking_status, 
                            bmi, ascites) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = stage3$recurrence_time,
                             event = stage3$rec_event)),
                   exponentiate = TRUE) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <- 
  coxph(Surv(time = stage3$recurrence_time,
             event = stage3$rec_event) ~ 
          raceeth1 + age_at_diagnosis + treatment_type + bmi + ascites, 
        data =  stage3) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))
```
</div>

<div class = "col-md-4">
```{r}
myplot <- survfit(Surv(recurrence_time, event = rec_event) ~ ascites, data = stage4)
ggsurvplot(myplot, data = stage4,
           title = "Recurrence Analysis in stage IV",
           font.main = c(20, "bold", "black"),
           font.x = c(18, "bold", "black"),
           font.y = c(18, "bold", "black"),
           font.legend = c(16, "black"),
           font.tickslab = c(16, "bold", "black"),
           size = 1.5,

           xlab = "Time in months",
           legend = "top",
           legend.title = "",
           # legend.labs = c("White Non-Hispanic", "Hispanic", "Black"),
           # palette = c("#03051AFF", "blue", "red"),
           pval = TRUE,
           conf.int = FALSE,
           # Censor
           censor = TRUE
) + guides(colour = guide_legend(ncol = 1))

tbl1 <- stage4 %>% select(rec_event, recurrence_time,
                            raceeth1, age_at_diagnosis, 
                            treatment_type, #debulking_status, 
                            bmi, ascites) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = stage4$recurrence_time,
                             event = stage4$rec_event)),
                   exponentiate = TRUE) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <- 
  coxph(Surv(time = stage4$recurrence_time,
             event = stage4$rec_event) ~ 
          raceeth1 + age_at_diagnosis + treatment_type + bmi + ascites, 
        data =  stage4) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))
```
</div>
</div>

#### OS

<div class = "row">
<div class = "col-md-4">
```{r}
myplot <- survfit(Surv(os_time, event = os_event) ~ ascites, data = stage1_2)
ggsurvplot(myplot, data = stage1_2,
           title = "OS Analysis in stage I-II",
           font.main = c(20, "bold", "black"),
           font.x = c(18, "bold", "black"),
           font.y = c(18, "bold", "black"),
           font.legend = c(16, "black"),
           font.tickslab = c(16, "bold", "black"),
           size = 1.5,

           xlab = "Time in months",
           legend = "top",
           legend.title = "",
           # legend.labs = c("White Non-Hispanic", "Hispanic", "Black"),
           # palette = c("#03051AFF", "blue", "red"),
           pval = TRUE,
           conf.int = FALSE,
           # Censor
           censor = TRUE
) + guides(colour = guide_legend(ncol = 1))

tbl1 <- stage1_2 %>% select(os_event, os_time,
                            raceeth1, age_at_diagnosis, 
                            treatment_type, #debulking_status, 
                            bmi, ascites) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = stage1_2$os_time,
                             event = stage1_2$os_event)),
                   exponentiate = TRUE) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <- 
  coxph(Surv(time = stage1_2$os_time,
             event = stage1_2$os_event) ~ 
          raceeth1 + age_at_diagnosis + treatment_type + bmi + ascites, 
        data =  stage1_2) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))
```
</div>

<div class = "col-md-4">
```{r}
myplot <- survfit(Surv(os_time, event = os_event) ~ ascites, data = stage3)
ggsurvplot(myplot, data = stage3,
           title = "OS Analysis in stage I-II",
           font.main = c(20, "bold", "black"),
           font.x = c(18, "bold", "black"),
           font.y = c(18, "bold", "black"),
           font.legend = c(16, "black"),
           font.tickslab = c(16, "bold", "black"),
           size = 1.5,

           xlab = "Time in months",
           legend = "top",
           legend.title = "",
           # legend.labs = c("White Non-Hispanic", "Hispanic", "Black"),
           # palette = c("#03051AFF", "blue", "red"),
           pval = TRUE,
           conf.int = FALSE,
           # Censor
           censor = TRUE
) + guides(colour = guide_legend(ncol = 1))

tbl1 <- stage3 %>% select(os_event, os_time,
                            raceeth1, age_at_diagnosis, 
                            treatment_type, #debulking_status, 
                            bmi, ascites) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = stage3$os_time,
                             event = stage3$os_event)),
                   exponentiate = TRUE) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <- 
  coxph(Surv(time = stage3$os_time,
             event = stage3$os_event) ~ 
          raceeth1 + age_at_diagnosis + treatment_type + bmi + ascites,
        data =  stage3) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))
```
</div>

<div class = "col-md-4">
```{r}
myplot <- survfit(Surv(os_time, event = os_event) ~ ascites, data = stage4)
ggsurvplot(myplot, data = stage4,
           title = "OS Analysis in stage I-II",
           font.main = c(20, "bold", "black"),
           font.x = c(18, "bold", "black"),
           font.y = c(18, "bold", "black"),
           font.legend = c(16, "black"),
           font.tickslab = c(16, "bold", "black"),
           size = 1.5,

           xlab = "Time in months",
           legend = "top",
           legend.title = "",
           # legend.labs = c("White Non-Hispanic", "Hispanic", "Black"),
           # palette = c("#03051AFF", "blue", "red"),
           pval = TRUE,
           conf.int = FALSE,
           # Censor
           censor = TRUE
) + guides(colour = guide_legend(ncol = 1))

tbl1 <- stage4 %>% select(os_event, os_time,
                            raceeth1, age_at_diagnosis, 
                            treatment_type, #debulking_status, 
                            bmi, ascites) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = stage4$os_time,
                             event = stage4$os_event)),
                   exponentiate = TRUE) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <- 
  coxph(Surv(time = stage4$os_time,
             event = stage4$os_event) ~ 
          raceeth1 + age_at_diagnosis + treatment_type + bmi + ascites, 
        data =  stage4) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))
```
</div>
</div>

<br>
<br>

***

<br>

# Pre-treatment CT-based measures of adiposity
## Univariable HR continous radiomics : recurrence
```{r}
tbl1 <- adipose_data %>% select(rec_event, recurrence_time,
                        muscle_area_cm2_HR, muscle_area_cm2_ind_HR,
                        imat_area_cm2_HR, imat_area_cm2_ind_HR,
                        vat_area_cm2_HR, vat_area_cm2_ind_HR,
                        sat_area_cm2_HR, sat_area_cm2_ind_HR,
                        total_fat_area_HR, total_fat_area_ind_HR,
                        muscle_mean_hu_HR,                    
                        v_s_ratio_HR) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$recurrence_time,
                             event = adipose_data$rec_event)),
                   exponentiate = TRUE) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")

tbl2 <-
  coxph(Surv(time = adipose_data$recurrence_time,
         event = adipose_data$rec_event) ~ muscle_area_cm2_HR + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = muscle_area_cm2_HR) %>% bold_p(t = .05)
tbl3 <-
  coxph(Surv(time = adipose_data$recurrence_time,
         event = adipose_data$rec_event) ~ muscle_area_cm2_ind_HR + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = muscle_area_cm2_ind_HR) %>% bold_p(t = .05)
tbl4 <-
  coxph(Surv(time = adipose_data$recurrence_time,
         event = adipose_data$rec_event) ~ imat_area_cm2_HR + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = imat_area_cm2_HR) %>% bold_p(t = .05)
tbl5 <-
  coxph(Surv(time = adipose_data$recurrence_time,
         event = adipose_data$rec_event) ~ imat_area_cm2_ind_HR + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = imat_area_cm2_ind_HR) %>% bold_p(t = .05)
tbl6 <-
  coxph(Surv(time = adipose_data$recurrence_time,
         event = adipose_data$rec_event) ~ vat_area_cm2_HR + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = vat_area_cm2_HR) %>% bold_p(t = .05)
tbl7 <-
  coxph(Surv(time = adipose_data$recurrence_time,
         event = adipose_data$rec_event) ~ vat_area_cm2_ind_HR + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = vat_area_cm2_ind_HR) %>% bold_p(t = .05)
tbl8 <-
  coxph(Surv(time = adipose_data$recurrence_time,
         event = adipose_data$rec_event) ~ sat_area_cm2_HR + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = sat_area_cm2_HR) %>% bold_p(t = .05)
tbl9 <-
  coxph(Surv(time = adipose_data$recurrence_time,
         event = adipose_data$rec_event) ~ sat_area_cm2_ind_HR + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = sat_area_cm2_ind_HR) %>% bold_p(t = .05)
tbl10 <-
  coxph(Surv(time = adipose_data$recurrence_time,
         event = adipose_data$rec_event) ~ total_fat_area_HR + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = total_fat_area_HR) %>% bold_p(t = .05)
tbl11 <-
  coxph(Surv(time = adipose_data$recurrence_time,
         event = adipose_data$rec_event) ~ total_fat_area_ind_HR + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = total_fat_area_ind_HR) %>% bold_p(t = .05)
tbl12 <-
  coxph(Surv(time = adipose_data$recurrence_time,
         event = adipose_data$rec_event) ~ muscle_mean_hu_HR + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = muscle_mean_hu_HR) %>% bold_p(t = .05)
tbl13 <-
  coxph(Surv(time = adipose_data$recurrence_time,
         event = adipose_data$rec_event) ~ v_s_ratio_HR + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = v_s_ratio_HR) %>% bold_p(t = .05)
tbl14 <-
  coxph(Surv(time = adipose_data$recurrence_time,
         event = adipose_data$rec_event) ~ v_s_ratio_HR + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type + ascites,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                label = list(v_s_ratio_HR ~ "V/S adjusted by ascites"),
                 include = v_s_ratio_HR) %>% bold_p(t = .05)

tbl2 <- tbl_stack(list(tbl2, tbl3, tbl4, tbl5,
               tbl6, tbl7, tbl8, tbl9, tbl10,
               tbl11, tbl12, tbl13, tbl14))

tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))
```

Adjusted for ascites
```{r}
coxph(Surv(time = adipose_data$recurrence_time,
         event = adipose_data$rec_event) ~ vat_area_cm2_HR + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type + ascites,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = vat_area_cm2_HR) %>% bold_p(t = .05)
coxph(Surv(time = adipose_data$recurrence_time,
         event = adipose_data$rec_event) ~ vat_area_cm2_ind_HR + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type + ascites,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = vat_area_cm2_ind_HR) %>% bold_p(t = .05)

```

## Univariable HR continous radiomics : OS
```{r}
tbl1 <- adipose_data %>% select(os_event, os_time,
                        muscle_area_cm2_HR, muscle_area_cm2_ind_HR,
                        imat_area_cm2_HR, imat_area_cm2_ind_HR,
                        vat_area_cm2_HR, vat_area_cm2_ind_HR,
                        sat_area_cm2_HR, sat_area_cm2_ind_HR,
                        total_fat_area_HR, total_fat_area_ind_HR,
                        muscle_mean_hu_HR,                    
                        v_s_ratio_HR) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$os_time,
                             event = adipose_data$os_event)),
                   exponentiate = TRUE) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")

tbl2 <-
  coxph(Surv(time = adipose_data$os_time,
         event = adipose_data$os_event) ~ muscle_area_cm2_HR + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = muscle_area_cm2_HR) %>% bold_p(t = .05)
tbl3 <-
  coxph(Surv(time = adipose_data$os_time,
         event = adipose_data$os_event) ~ muscle_area_cm2_ind_HR + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = muscle_area_cm2_ind_HR) %>% bold_p(t = .05)
tbl4 <-
  coxph(Surv(time = adipose_data$os_time,
         event = adipose_data$os_event) ~ imat_area_cm2_HR + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = imat_area_cm2_HR) %>% bold_p(t = .05)
tbl5 <-
  coxph(Surv(time = adipose_data$os_time,
         event = adipose_data$os_event) ~ imat_area_cm2_ind_HR + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = imat_area_cm2_ind_HR) %>% bold_p(t = .05)
tbl6 <-
  coxph(Surv(time = adipose_data$os_time,
         event = adipose_data$os_event) ~ vat_area_cm2_HR + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = vat_area_cm2_HR) %>% bold_p(t = .05)
tbl7 <-
  coxph(Surv(time = adipose_data$os_time,
         event = adipose_data$os_event) ~ vat_area_cm2_ind_HR + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = vat_area_cm2_ind_HR) %>% bold_p(t = .05)
tbl8 <-
  coxph(Surv(time = adipose_data$os_time,
         event = adipose_data$os_event) ~ sat_area_cm2_HR + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = sat_area_cm2_HR) %>% bold_p(t = .05)
tbl9 <-
  coxph(Surv(time = adipose_data$os_time,
         event = adipose_data$os_event) ~ sat_area_cm2_ind_HR + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = sat_area_cm2_ind_HR) %>% bold_p(t = .05)
tbl10 <-
  coxph(Surv(time = adipose_data$os_time,
         event = adipose_data$os_event) ~ total_fat_area_HR + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = total_fat_area_HR) %>% bold_p(t = .05)
tbl11 <-
  coxph(Surv(time = adipose_data$os_time,
         event = adipose_data$os_event) ~ total_fat_area_ind_HR + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = total_fat_area_ind_HR) %>% bold_p(t = .05)
tbl12 <-
  coxph(Surv(time = adipose_data$os_time,
         event = adipose_data$os_event) ~ muscle_mean_hu_HR + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = muscle_mean_hu_HR) %>% bold_p(t = .05)
tbl13 <-
  coxph(Surv(time = adipose_data$os_time,
         event = adipose_data$os_event) ~ v_s_ratio_HR + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = v_s_ratio_HR) %>% bold_p(t = .05)
tbl14 <-
  coxph(Surv(time = adipose_data$os_time,
         event = adipose_data$os_event) ~ v_s_ratio_HR + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type + ascites,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 label = list(v_s_ratio_HR ~ "V/S adjusted by ascites"),
                 include = v_s_ratio_HR) %>% bold_p(t = .05)

tbl2 <- tbl_stack(list(tbl2, tbl3, tbl4, tbl5,
               tbl6, tbl7, tbl8, tbl9, tbl10,
               tbl11, tbl12, tbl13, tbl14))

tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))
```
Adjusted for ascites
```{r}
coxph(Surv(time = adipose_data$os_time,
         event = adipose_data$os_event) ~ vat_area_cm2_HR + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type + ascites,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = vat_area_cm2_HR) %>% bold_p(t = .05)
coxph(Surv(time = adipose_data$os_time,
         event = adipose_data$os_event) ~ vat_area_cm2_ind_HR + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type + ascites,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = vat_area_cm2_ind_HR) %>% bold_p(t = .05)
```
Difficulty to decide if indexed data is better -> Will create groups.  
<br>

***

<br>

# Make group
## Make group : tertile

```{r tertile}
adipose_data <- adipose_data %>% 
  mutate(tertile = ntile(muscle_area_cm2, 3)) %>% 
  mutate(tert_muscle_area_cm2 = case_when(
    tertile == 1 ~ "Low",
    tertile == 2 ~ "Medium",
    tertile == 3 ~ "High",
  ), 
  tert_muscle_area_cm2 = factor(tert_muscle_area_cm2, levels = c("Low", "Medium", "High"))) %>% 
  mutate(tertile = ntile(muscle_area_cm2_ind, 3)) %>% 
  mutate(tert_muscle_area_cm2_ind = case_when(
    tertile == 1 ~ "Low",
    tertile == 2 ~ "Medium",
    tertile == 3 ~ "High",
  ), 
  tert_muscle_area_cm2_ind = factor(tert_muscle_area_cm2_ind, levels = c("Low", "Medium", "High"))) %>% 
  mutate(tertile = ntile(imat_area_cm2, 3)) %>% 
  mutate(tert_imat_area_cm2 = case_when(
    tertile == 1 ~ "Low",
    tertile == 2 ~ "Medium",
    tertile == 3 ~ "High",
  ), 
  tert_imat_area_cm2 = factor(tert_imat_area_cm2, levels = c("Low", "Medium", "High"))) %>% 
  mutate(tertile = ntile(imat_area_cm2_ind, 3)) %>% 
  mutate(tert_imat_area_cm2_ind = case_when(
    tertile == 1 ~ "Low",
    tertile == 2 ~ "Medium",
    tertile == 3 ~ "High",
  ), 
  tert_imat_area_cm2_ind = factor(tert_imat_area_cm2_ind, levels = c("Low", "Medium", "High"))) %>% 
  mutate(tertile = ntile(vat_area_cm2, 3)) %>% 
  mutate(tert_vat_area_cm2 = case_when(
    tertile == 1 ~ "Low",
    tertile == 2 ~ "Medium",
    tertile == 3 ~ "High",
  ), 
  tert_vat_area_cm2 = factor(tert_vat_area_cm2, levels = c("Low", "Medium", "High"))) %>% 
  mutate(tertile = ntile(vat_area_cm2_ind, 3)) %>% 
  mutate(tert_vat_area_cm2_ind = case_when(
    tertile == 1 ~ "Low",
    tertile == 2 ~ "Medium",
    tertile == 3 ~ "High",
  ), 
  tert_vat_area_cm2_ind = factor(tert_vat_area_cm2_ind, levels = c("Low", "Medium", "High"))) %>% 
  mutate(tertile = ntile(sat_area_cm2, 3)) %>% 
  mutate(tert_sat_area_cm2 = case_when(
    tertile == 1 ~ "Low",
    tertile == 2 ~ "Medium",
    tertile == 3 ~ "High",
  ), 
  tert_sat_area_cm2 = factor(tert_sat_area_cm2, levels = c("Low", "Medium", "High"))) %>% 
  mutate(tertile = ntile(sat_area_cm2_ind, 3)) %>% 
  mutate(tert_sat_area_cm2_ind = case_when(
    tertile == 1 ~ "Low",
    tertile == 2 ~ "Medium",
    tertile == 3 ~ "High",
  ), 
  tert_sat_area_cm2_ind = factor(tert_sat_area_cm2_ind, levels = c("Low", "Medium", "High"))) %>% 
  mutate(tertile = ntile(total_fat_area, 3)) %>% 
  mutate(tert_total_fat_area = case_when(
    tertile == 1 ~ "Low",
    tertile == 2 ~ "Medium",
    tertile == 3 ~ "High",
  ), 
  tert_total_fat_area = factor(tert_total_fat_area, levels = c("Low", "Medium", "High"))) %>% 
  mutate(tertile = ntile(total_fat_area_ind, 3)) %>% 
  mutate(tert_total_fat_area_ind = case_when(
    tertile == 1 ~ "Low",
    tertile == 2 ~ "Medium",
    tertile == 3 ~ "High",
  ), 
  tert_total_fat_area_ind = factor(tert_total_fat_area_ind, levels = c("Low", "Medium", "High"))) %>% 
  mutate(tertile = ntile(muscle_mean_hu, 3)) %>% 
  mutate(tert_muscle_mean_hu = case_when(
    tertile == 1 ~ "Low",
    tertile == 2 ~ "Medium",
    tertile == 3 ~ "High",
  ), 
  tert_muscle_mean_hu = factor(tert_muscle_mean_hu, levels = c("Low", "Medium", "High"))) %>% 
  mutate(tertile = ntile(imat_mean_hu, 3)) %>% 
  mutate(tert_imat_mean_hu = case_when(
    tertile == 1 ~ "Low",
    tertile == 2 ~ "Medium",
    tertile == 3 ~ "High",
  ), 
  tert_imat_mean_hu = factor(tert_imat_mean_hu, levels = c("Low", "Medium", "High"))) %>% 
  mutate(tertile = ntile(muscle_hu_sd, 3)) %>% 
  mutate(tert_muscle_hu_sd = case_when(
    tertile == 1 ~ "Low",
    tertile == 2 ~ "Medium",
    tertile == 3 ~ "High",
  ), 
  tert_muscle_hu_sd = factor(tert_muscle_hu_sd, levels = c("Low", "Medium", "High"))) %>% 
  mutate(tertile = ntile(v_s_ratio, 3)) %>% 
  mutate(tert_v_s_ratio = case_when(
    tertile == 1 ~ "Low",
    tertile == 2 ~ "Medium",
    tertile == 3 ~ "High",
  ), 
  tert_v_s_ratio = factor(tert_v_s_ratio, levels = c("Low", "Medium", "High"))) %>% 
  select(-tertile)
```
 Here an example of tertiles
```{r}
adipose_data %>% 
  # pivot_longer()
  ggplot(aes(x= tert_muscle_area_cm2, y = muscle_area_cm2))+
  geom_boxplot()
```
<br>

### Tertile summary

```{r}
tbl1 <- adipose_data %>% 
  select(sat_area_cm2, 
         imat_area_cm2,
         vat_area_cm2
         ) %>% 
  tbl_summary(
            statistic=list(all_continuous() ~ "{mean}"), 
            digits = all_continuous() ~ 1
            ) %>%  
  bold_labels() %>% 
  modify_footnote(update = everything() ~ NA)

tbl2 <- adipose_data %>% 
  select(sat_area_cm2, 
         imat_area_cm2,
         vat_area_cm2
         ) %>% 
  tbl_summary(
            statistic=list(all_continuous() ~ "{min} - {max}"), 
            digits = all_continuous() ~ 1
            ) %>%  
  bold_labels() %>% 
  modify_footnote(update = everything() ~ NA)

tbl3 <- adipose_data %>% 
  select(sat_area_cm2, 
         imat_area_cm2,
         vat_area_cm2
         ) %>% 
  tbl_summary(
            statistic=list(all_continuous() ~ "{median}"), 
            digits = all_continuous() ~ 1
            ) %>%  
  bold_labels() %>% 
  modify_footnote(update = everything() ~ NA)
tbl_merge(list(tbl1, tbl2, tbl3), tab_spanner = c("Mean", "Min-Max", "Median"))


tbl3 <- adipose_data %>% 
  select(tert_sat_area_cm2, sat_area_cm2) %>% 
  tbl_summary(by = tert_sat_area_cm2,
            statistic=list(all_continuous() ~ "{min} - {max}"), 
            digits = all_continuous() ~ 1
            ) %>%  
  bold_labels()

tbl4 <- adipose_data %>% 
  select(tert_imat_area_cm2, imat_area_cm2) %>% 
  tbl_summary(by = tert_imat_area_cm2,
            statistic=list(all_continuous() ~ "{min} - {max}"), 
            digits = all_continuous() ~ 1
            ) %>%  
  bold_labels()

tbl5 <- adipose_data %>% 
  select(tert_vat_area_cm2, vat_area_cm2) %>% 
  tbl_summary(by = tert_vat_area_cm2,
            statistic=list(all_continuous() ~ "{min} - {max}"), 
            digits = all_continuous() ~ 1
            ) %>%  
  bold_labels()
tbl_stack(list(tbl3, tbl4, tbl5))
```


## Make group : Mclust
clusters_non_ind, muscle_mean_hu and imat_mean_hu are forced to make 3 group when it would give only 1 group by mclust - decide on 3 groups to compare with tertiles group and see what is more meaningful.

```{r cluster}
clust_data <- adipose_data %>% 
  select(id, muscle_area_cm2, 
         imat_area_cm2,
         vat_area_cm2,
         sat_area_cm2,
         total_fat_area,
         muscle_mean_hu,                    
         imat_mean_hu,
         muscle_hu_sd, 
         v_s_ratio)

set.seed(123)
clust <- Mclust(scale(
  clust_data[,c(2:ncol(clust_data))]
  ), G = 3)
summary(clust)
clust_data$clusters_non_ind <- clust$classification
clust_data$clusters_non_ind <- factor(clust_data$clusters_non_ind,
                                           levels = c(2, 3, 1),
                                           labels = c("low", "mid", "high"))
clust_data <- clust_data %>% mutate(clusters_non_ind = factor(clusters_non_ind, levels = c("low", "mid", "high")))
clust_data %>% 
  pivot_longer(cols = -c(id, clusters_non_ind), names_to = "name", values_to = "value") %>% 
  ggplot(aes(x=id, y=value, group=name,  color=name))+
  geom_boxplot()+
  facet_grid(.~ clusters_non_ind)

adipose_data <- 
  full_join(adipose_data, clust_data %>% select(id, starts_with("clusters_")), by = "id")
```

```{r}
clust_data <- adipose_data %>% 
  select(id, muscle_area_cm2, muscle_area_cm2_ind, 
         imat_area_cm2, imat_area_cm2_ind,
         vat_area_cm2, vat_area_cm2_ind,
         sat_area_cm2, sat_area_cm2_ind,
         total_fat_area, total_fat_area_ind,
         muscle_mean_hu,                    
         imat_mean_hu,
         muscle_hu_sd, 
         v_s_ratio)

clust <- Mclust(clust_data$muscle_area_cm2)
summary(clust)
clust_data$clusters_muscle_area_cm2 <- clust$classification
clust_data$clusters_muscle_area_cm2 <- factor(clust_data$clusters_muscle_area_cm2,
                                           levels = c(1, 2),
                                           labels = c("low", "high"))
clust_data %>% 
  ggplot(aes(x=clusters_muscle_area_cm2, y=muscle_area_cm2))+
  geom_boxplot()

clust <- Mclust(clust_data$muscle_area_cm2_ind)
summary(clust)
clust_data$clusters_muscle_area_cm2_ind <- clust$classification
clust_data$clusters_muscle_area_cm2_ind <- factor(clust_data$clusters_muscle_area_cm2_ind,
                                           levels = c(1, 2),
                                           labels = c("low", "high"))
clust_data %>% 
  ggplot(aes(x=clusters_muscle_area_cm2_ind, y=muscle_area_cm2_ind))+
  geom_boxplot()

clust <- Mclust(clust_data$imat_area_cm2)
summary(clust)
clust_data$clusters_imat_area_cm2 <- clust$classification
clust_data$clusters_imat_area_cm2 <- factor(clust_data$clusters_imat_area_cm2,
                                           levels = c(1, 2),
                                           labels = c("low", "high"))
clust_data %>% 
  ggplot(aes(x=clusters_imat_area_cm2, y=imat_area_cm2))+
  geom_boxplot()

clust <- Mclust(clust_data$imat_area_cm2_ind)
summary(clust)
clust_data$clusters_imat_area_cm2_ind <- clust$classification
clust_data$clusters_imat_area_cm2_ind <- factor(clust_data$clusters_imat_area_cm2_ind,
                                           levels = c(1, 2, 3, 4),
                                           labels = c("low", "mid-low", "mid_high", "high"))
clust_data %>% 
  ggplot(aes(x=clusters_imat_area_cm2_ind, y=imat_area_cm2_ind))+
  geom_boxplot()

clust <- Mclust(clust_data$vat_area_cm2)
summary(clust)
clust_data$clusters_vat_area_cm2 <- clust$classification
clust_data$clusters_vat_area_cm2 <- factor(clust_data$clusters_vat_area_cm2,
                                           levels = c(1, 2, 3, 4, 5),
                                           labels = c("low", "mid-low", "mid", "mid-high", "high"))
clust_data %>% 
  ggplot(aes(x=clusters_vat_area_cm2, y=vat_area_cm2))+
  geom_boxplot()

clust <- Mclust(clust_data$vat_area_cm2_ind)
summary(clust)
clust_data$clusters_vat_area_cm2_ind <- clust$classification
clust_data$clusters_vat_area_cm2_ind <- factor(clust_data$clusters_vat_area_cm2_ind,
                                           levels = c(1, 2, 3, 4, 5),
                                           labels = c("low", "mid-low", "mid", "mid-high", "high"))
clust_data %>% 
  ggplot(aes(x=clusters_vat_area_cm2_ind, y=vat_area_cm2_ind))+
  geom_boxplot()

clust <- Mclust(clust_data$sat_area_cm2)
summary(clust)
clust_data$clusters_sat_area_cm2 <- clust$classification
clust_data$clusters_sat_area_cm2 <- factor(clust_data$clusters_sat_area_cm2,
                                           levels = c(1, 2),
                                           labels = c("low", "high"))
clust_data %>% 
  ggplot(aes(x=clusters_sat_area_cm2, y=sat_area_cm2))+
  geom_boxplot()

clust <- Mclust(clust_data$sat_area_cm2_ind)
summary(clust)
clust_data$clusters_sat_area_cm2_ind <- clust$classification
clust_data$clusters_sat_area_cm2_ind <- factor(clust_data$clusters_sat_area_cm2_ind,
                                           levels = c(1, 2),
                                           labels = c("low", "high"))
clust_data %>% 
  ggplot(aes(x=clusters_sat_area_cm2_ind, y=sat_area_cm2_ind))+
  geom_boxplot()

clust <- Mclust(clust_data$total_fat_area)
summary(clust)
clust_data$clusters_total_fat_area <- clust$classification
clust_data$clusters_total_fat_area <- factor(clust_data$clusters_total_fat_area,
                                           levels = c(1, 2),
                                           labels = c("low", "high"))
clust_data %>% 
  ggplot(aes(x=clusters_total_fat_area, y=total_fat_area))+
  geom_boxplot()

clust <- Mclust(clust_data$total_fat_area_ind)
summary(clust)
clust_data$clusters_total_fat_area_ind <- clust$classification
clust_data$clusters_total_fat_area_ind <- factor(clust_data$clusters_total_fat_area_ind,
                                           levels = c(1, 2),
                                           labels = c("low", "high"))
clust_data %>% 
  ggplot(aes(x=clusters_total_fat_area_ind, y=total_fat_area_ind))+
  geom_boxplot()

clust <- Mclust(clust_data$muscle_mean_hu, G = 3)
summary(clust)
clust_data$clusters_muscle_mean_hu <- clust$classification
clust_data$clusters_muscle_mean_hu <- factor(clust_data$clusters_muscle_mean_hu,
                                           levels = c(1, 2, 3),
                                           labels = c("low", "mid", "high"))
clust_data %>% 
  ggplot(aes(x=clusters_muscle_mean_hu, y=muscle_mean_hu))+
  geom_boxplot()

clust <- Mclust(clust_data$imat_mean_hu, G = 3)
summary(clust)
clust_data$clusters_imat_mean_hu <- clust$classification
clust_data$clusters_imat_mean_hu <- factor(clust_data$clusters_imat_mean_hu,
                                           levels = c(1, 2, 3),
                                           labels = c("low", "mid", "high"))
clust_data %>% 
  ggplot(aes(x=clusters_imat_mean_hu, y=imat_mean_hu))+
  geom_boxplot()

clust <- Mclust(clust_data$muscle_hu_sd)
summary(clust)
clust_data$clusters_muscle_hu_sd <- clust$classification
clust_data$clusters_muscle_hu_sd <- factor(clust_data$clusters_muscle_hu_sd,
                                           levels = c(1, 2),
                                           labels = c("low", "high"))
clust_data %>% 
  ggplot(aes(x=clusters_muscle_hu_sd, y=muscle_hu_sd))+
  geom_boxplot()

clust <- Mclust(clust_data$v_s_ratio)
summary(clust)
clust_data$clusters_v_s_ratio <- clust$classification
clust_data$clusters_v_s_ratio <- factor(clust_data$clusters_v_s_ratio,
                                           levels = c(1, 2, 3, 4, 5),
                                           labels = c("mid", "low", "mid-low", "mid-high", "high"))
clust_data %>% 
  ggplot(aes(x=clusters_v_s_ratio, y=v_s_ratio))+
  geom_boxplot()

adipose_data <- 
  full_join(adipose_data, clust_data %>% select(id, starts_with("clusters_")), by = "id")
# write_rds(adipose_data, "adipose_data_with_groups.rds")
```
<br>

## Visualize tertile and cluster on survival
### OS
<div class = "row">
<div class = "col-md-6">
```{r, fig.height = 8}
surv_model <-
  survfit(Surv(time = os_time, event = os_event) ~ tert_muscle_area_cm2, data = adipose_data)
ggsurvplot(surv_model, data = adipose_data,
           title = "Overall Survival analysis",
           font.main = c(22, "bold", "black"),
           font.x = c(20, "bold", "black"),
           font.y = c(20, "bold", "black"),
           font.legend = c(20, "black"),
           font.tickslab = c(18, "bold", "black"),
           size = 1.5,
           
           xlab = "Time (months)", legend.title = "", 
           pval = TRUE,
           conf.int = FALSE,
           tables.height = 0.25,
           risk.table.title = "Risk table",
           risk.table = TRUE,
           risk.table.y.text = FALSE,
           risk.table.fontsize = 4,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(14, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(14, "bold", "black"))
) + guides(colour = guide_legend(ncol = 1))

surv_model <-
  survfit(Surv(time = os_time, event = os_event) ~ tert_muscle_area_cm2_ind, data = adipose_data)
ggsurvplot(surv_model, data = adipose_data,
           title = "Overall Survival analysis",
           font.main = c(22, "bold", "black"),
           font.x = c(20, "bold", "black"),
           font.y = c(20, "bold", "black"),
           font.legend = c(20, "black"),
           font.tickslab = c(18, "bold", "black"),
           size = 1.5,
           
           xlab = "Time (months)", legend.title = "", 
           pval = TRUE,
           conf.int = FALSE,
           tables.height = 0.25,
           risk.table.title = "Risk table",
           risk.table = TRUE,
           risk.table.y.text = FALSE,
           risk.table.fontsize = 4,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(14, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(14, "bold", "black"))
) + guides(colour = guide_legend(ncol = 1))

surv_model <-
  survfit(Surv(time = os_time, event = os_event) ~ tert_imat_area_cm2, data = adipose_data)
ggsurvplot(surv_model, data = adipose_data,
           title = "Overall Survival analysis",
           font.main = c(22, "bold", "black"),
           font.x = c(20, "bold", "black"),
           font.y = c(20, "bold", "black"),
           font.legend = c(20, "black"),
           font.tickslab = c(18, "bold", "black"),
           size = 1.5,
           
           xlab = "Time (months)", legend.title = "", 
           pval = TRUE,
           conf.int = FALSE,
           tables.height = 0.25,
           risk.table.title = "Risk table",
           risk.table = TRUE,
           risk.table.y.text = FALSE,
           risk.table.fontsize = 4,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(14, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(14, "bold", "black"))
) + guides(colour = guide_legend(ncol = 1))

surv_model <-
  survfit(Surv(time = os_time, event = os_event) ~ tert_imat_area_cm2_ind, data = adipose_data)
ggsurvplot(surv_model, data = adipose_data,
           title = "Overall Survival analysis",
           font.main = c(22, "bold", "black"),
           font.x = c(20, "bold", "black"),
           font.y = c(20, "bold", "black"),
           font.legend = c(20, "black"),
           font.tickslab = c(18, "bold", "black"),
           size = 1.5,
           
           xlab = "Time (months)", legend.title = "", 
           pval = TRUE,
           conf.int = FALSE,
           tables.height = 0.25,
           risk.table.title = "Risk table",
           risk.table = TRUE,
           risk.table.y.text = FALSE,
           risk.table.fontsize = 4,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(14, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(14, "bold", "black"))
) + guides(colour = guide_legend(ncol = 1))

surv_model <-
  survfit(Surv(time = os_time, event = os_event) ~ tert_vat_area_cm2, data = adipose_data)
ggsurvplot(surv_model, data = adipose_data,
           title = "Overall Survival analysis",
           font.main = c(22, "bold", "black"),
           font.x = c(20, "bold", "black"),
           font.y = c(20, "bold", "black"),
           font.legend = c(20, "black"),
           font.tickslab = c(18, "bold", "black"),
           size = 1.5,
           
           xlab = "Time (months)", legend.title = "", 
           pval = TRUE,
           conf.int = FALSE,
           tables.height = 0.25,
           risk.table.title = "Risk table",
           risk.table = TRUE,
           risk.table.y.text = FALSE,
           risk.table.fontsize = 4,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(14, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(14, "bold", "black"))
) + guides(colour = guide_legend(ncol = 1))

surv_model <-
  survfit(Surv(time = os_time, event = os_event) ~ tert_vat_area_cm2_ind, data = adipose_data)
ggsurvplot(surv_model, data = adipose_data,
           title = "Overall Survival analysis",
           font.main = c(22, "bold", "black"),
           font.x = c(20, "bold", "black"),
           font.y = c(20, "bold", "black"),
           font.legend = c(20, "black"),
           font.tickslab = c(18, "bold", "black"),
           size = 1.5,
           
           xlab = "Time (months)", legend.title = "", 
           pval = TRUE,
           conf.int = FALSE,
           tables.height = 0.25,
           risk.table.title = "Risk table",
           risk.table = TRUE,
           risk.table.y.text = FALSE,
           risk.table.fontsize = 4,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(14, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(14, "bold", "black"))
) + guides(colour = guide_legend(ncol = 1))

surv_model <-
  survfit(Surv(time = os_time, event = os_event) ~ tert_sat_area_cm2, data = adipose_data)
ggsurvplot(surv_model, data = adipose_data,
           title = "Overall Survival analysis",
           font.main = c(22, "bold", "black"),
           font.x = c(20, "bold", "black"),
           font.y = c(20, "bold", "black"),
           font.legend = c(20, "black"),
           font.tickslab = c(18, "bold", "black"),
           size = 1.5,
           
           xlab = "Time (months)", legend.title = "", 
           pval = TRUE,
           conf.int = FALSE,
           tables.height = 0.25,
           risk.table.title = "Risk table",
           risk.table = TRUE,
           risk.table.y.text = FALSE,
           risk.table.fontsize = 4,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(14, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(14, "bold", "black"))
) + guides(colour = guide_legend(ncol = 1))

surv_model <-
  survfit(Surv(time = os_time, event = os_event) ~ tert_sat_area_cm2_ind, data = adipose_data)
ggsurvplot(surv_model, data = adipose_data,
           title = "Overall Survival analysis",
           font.main = c(22, "bold", "black"),
           font.x = c(20, "bold", "black"),
           font.y = c(20, "bold", "black"),
           font.legend = c(20, "black"),
           font.tickslab = c(18, "bold", "black"),
           size = 1.5,
           
           xlab = "Time (months)", legend.title = "", 
           pval = TRUE,
           conf.int = FALSE,
           tables.height = 0.25,
           risk.table.title = "Risk table",
           risk.table = TRUE,
           risk.table.y.text = FALSE,
           risk.table.fontsize = 4,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(14, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(14, "bold", "black"))
) + guides(colour = guide_legend(ncol = 1))


surv_model <-
  survfit(Surv(time = os_time, event = os_event) ~ tert_total_fat_area, data = adipose_data)
ggsurvplot(surv_model, data = adipose_data,
           title = "Overall Survival analysis",
           font.main = c(22, "bold", "black"),
           font.x = c(20, "bold", "black"),
           font.y = c(20, "bold", "black"),
           font.legend = c(20, "black"),
           font.tickslab = c(18, "bold", "black"),
           size = 1.5,
           
           xlab = "Time (months)", legend.title = "", 
           pval = TRUE,
           conf.int = FALSE,
           tables.height = 0.25,
           risk.table.title = "Risk table",
           risk.table = TRUE,
           risk.table.y.text = FALSE,
           risk.table.fontsize = 4,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(14, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(14, "bold", "black"))
) + guides(colour = guide_legend(ncol = 1))

surv_model <-
  survfit(Surv(time = os_time, event = os_event) ~ tert_total_fat_area_ind, data = adipose_data)
ggsurvplot(surv_model, data = adipose_data,
           title = "Overall Survival analysis",
           font.main = c(22, "bold", "black"),
           font.x = c(20, "bold", "black"),
           font.y = c(20, "bold", "black"),
           font.legend = c(20, "black"),
           font.tickslab = c(18, "bold", "black"),
           size = 1.5,
           
           xlab = "Time (months)", legend.title = "", 
           pval = TRUE,
           conf.int = FALSE,
           tables.height = 0.25,
           risk.table.title = "Risk table",
           risk.table = TRUE,
           risk.table.y.text = FALSE,
           risk.table.fontsize = 4,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(14, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(14, "bold", "black"))
) + guides(colour = guide_legend(ncol = 1))

surv_model <-
  survfit(Surv(time = os_time, event = os_event) ~ tert_muscle_mean_hu, data = adipose_data)
ggsurvplot(surv_model, data = adipose_data,
           title = "Overall Survival analysis",
           font.main = c(22, "bold", "black"),
           font.x = c(20, "bold", "black"),
           font.y = c(20, "bold", "black"),
           font.legend = c(20, "black"),
           font.tickslab = c(18, "bold", "black"),
           size = 1.5,
           
           xlab = "Time (months)", legend.title = "", 
           pval = TRUE,
           conf.int = FALSE,
           tables.height = 0.25,
           risk.table.title = "Risk table",
           risk.table = TRUE,
           risk.table.y.text = FALSE,
           risk.table.fontsize = 4,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(14, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(14, "bold", "black"))
) + guides(colour = guide_legend(ncol = 1))

surv_model <-
  survfit(Surv(time = os_time, event = os_event) ~ tert_imat_mean_hu, data = adipose_data)
ggsurvplot(surv_model, data = adipose_data,
           title = "Overall Survival analysis",
           font.main = c(22, "bold", "black"),
           font.x = c(20, "bold", "black"),
           font.y = c(20, "bold", "black"),
           font.legend = c(20, "black"),
           font.tickslab = c(18, "bold", "black"),
           size = 1.5,
           
           xlab = "Time (months)", legend.title = "", 
           pval = TRUE,
           conf.int = FALSE,
           tables.height = 0.25,
           risk.table.title = "Risk table",
           risk.table = TRUE,
           risk.table.y.text = FALSE,
           risk.table.fontsize = 4,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(14, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(14, "bold", "black"))
) + guides(colour = guide_legend(ncol = 1))

surv_model <-
  survfit(Surv(time = os_time, event = os_event) ~ tert_muscle_hu_sd, data = adipose_data)
ggsurvplot(surv_model, data = adipose_data,
           title = "Overall Survival analysis",
           font.main = c(22, "bold", "black"),
           font.x = c(20, "bold", "black"),
           font.y = c(20, "bold", "black"),
           font.legend = c(20, "black"),
           font.tickslab = c(18, "bold", "black"),
           size = 1.5,
           
           xlab = "Time (months)", legend.title = "", 
           pval = TRUE,
           conf.int = FALSE,
           tables.height = 0.25,
           risk.table.title = "Risk table",
           risk.table = TRUE,
           risk.table.y.text = FALSE,
           risk.table.fontsize = 4,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(14, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(14, "bold", "black"))
) + guides(colour = guide_legend(ncol = 1))

surv_model <-
  survfit(Surv(time = os_time, event = os_event) ~ tert_v_s_ratio, data = adipose_data)
ggsurvplot(surv_model, data = adipose_data,
           title = "Overall Survival analysis",
           font.main = c(22, "bold", "black"),
           font.x = c(20, "bold", "black"),
           font.y = c(20, "bold", "black"),
           font.legend = c(20, "black"),
           font.tickslab = c(18, "bold", "black"),
           size = 1.5,
           
           xlab = "Time (months)", legend.title = "", 
           pval = TRUE,
           conf.int = FALSE,
           tables.height = 0.25,
           risk.table.title = "Risk table",
           risk.table = TRUE,
           risk.table.y.text = FALSE,
           risk.table.fontsize = 4,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(14, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(14, "bold", "black"))
) + guides(colour = guide_legend(ncol = 1))
```
</div>

<div class = "col-md-6">
```{r, fig.height = 8}
surv_model <-
  survfit(Surv(time = os_time, event = os_event) ~ clusters_muscle_area_cm2, data = adipose_data)
ggsurvplot(surv_model, data = adipose_data,
           title = "Overall Survival analysis",
           font.main = c(22, "bold", "black"),
           font.x = c(20, "bold", "black"),
           font.y = c(20, "bold", "black"),
           font.legend = c(20, "black"),
           font.tickslab = c(18, "bold", "black"),
           size = 1.5,
           
           xlab = "Time (months)", legend.title = "", 
           pval = TRUE,
           conf.int = FALSE,
           tables.height = 0.25,
           risk.table.title = "Risk table",
           risk.table = TRUE,
           risk.table.y.text = FALSE,
           risk.table.fontsize = 4,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(14, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(14, "bold", "black"))
) + guides(colour = guide_legend(ncol = 1))

surv_model <-
  survfit(Surv(time = os_time, event = os_event) ~ clusters_muscle_area_cm2_ind, data = adipose_data)
ggsurvplot(surv_model, data = adipose_data,
           title = "Overall Survival analysis",
           font.main = c(22, "bold", "black"),
           font.x = c(20, "bold", "black"),
           font.y = c(20, "bold", "black"),
           font.legend = c(20, "black"),
           font.tickslab = c(18, "bold", "black"),
           size = 1.5,
           
           xlab = "Time (months)", legend.title = "", 
           pval = TRUE,
           conf.int = FALSE,
           tables.height = 0.25,
           risk.table.title = "Risk table",
           risk.table = TRUE,
           risk.table.y.text = FALSE,
           risk.table.fontsize = 4,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(14, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(14, "bold", "black"))
) + guides(colour = guide_legend(ncol = 1))

surv_model <-
  survfit(Surv(time = os_time, event = os_event) ~ clusters_imat_area_cm2, data = adipose_data)
ggsurvplot(surv_model, data = adipose_data,
           title = "Overall Survival analysis",
           font.main = c(22, "bold", "black"),
           font.x = c(20, "bold", "black"),
           font.y = c(20, "bold", "black"),
           font.legend = c(20, "black"),
           font.tickslab = c(18, "bold", "black"),
           size = 1.5,
           
           xlab = "Time (months)", legend.title = "", 
           pval = TRUE,
           conf.int = FALSE,
           tables.height = 0.25,
           risk.table.title = "Risk table",
           risk.table = TRUE,
           risk.table.y.text = FALSE,
           risk.table.fontsize = 4,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(14, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(14, "bold", "black"))
) + guides(colour = guide_legend(ncol = 1))

surv_model <-
  survfit(Surv(time = os_time, event = os_event) ~ clusters_imat_area_cm2_ind, data = adipose_data)
ggsurvplot(surv_model, data = adipose_data,
           title = "Overall Survival analysis",
           font.main = c(22, "bold", "black"),
           font.x = c(20, "bold", "black"),
           font.y = c(20, "bold", "black"),
           font.legend = c(20, "black"),
           font.tickslab = c(18, "bold", "black"),
           size = 1.5,
           
           xlab = "Time (months)", legend.title = "", 
           pval = TRUE,
           conf.int = FALSE,
           tables.height = 0.25,
           risk.table.title = "Risk table",
           risk.table = TRUE,
           risk.table.y.text = FALSE,
           risk.table.fontsize = 4,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(14, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(14, "bold", "black"))
) + guides(colour = guide_legend(ncol = 1))

surv_model <-
  survfit(Surv(time = os_time, event = os_event) ~ clusters_vat_area_cm2, data = adipose_data)
ggsurvplot(surv_model, data = adipose_data,
           title = "Overall Survival analysis",
           font.main = c(22, "bold", "black"),
           font.x = c(20, "bold", "black"),
           font.y = c(20, "bold", "black"),
           font.legend = c(20, "black"),
           font.tickslab = c(18, "bold", "black"),
           size = 1.5,
           
           xlab = "Time (months)", legend.title = "", 
           pval = TRUE,
           conf.int = FALSE,
           tables.height = 0.25,
           risk.table.title = "Risk table",
           risk.table = TRUE,
           risk.table.y.text = FALSE,
           risk.table.fontsize = 4,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(14, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(14, "bold", "black"))
) + guides(colour = guide_legend(ncol = 1))

surv_model <-
  survfit(Surv(time = os_time, event = os_event) ~ clusters_vat_area_cm2_ind, data = adipose_data)
ggsurvplot(surv_model, data = adipose_data,
           title = "Overall Survival analysis",
           font.main = c(22, "bold", "black"),
           font.x = c(20, "bold", "black"),
           font.y = c(20, "bold", "black"),
           font.legend = c(20, "black"),
           font.tickslab = c(18, "bold", "black"),
           size = 1.5,
           
           xlab = "Time (months)", legend.title = "", 
           pval = TRUE,
           conf.int = FALSE,
           tables.height = 0.25,
           risk.table.title = "Risk table",
           risk.table = TRUE,
           risk.table.y.text = FALSE,
           risk.table.fontsize = 4,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(14, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(14, "bold", "black"))
) + guides(colour = guide_legend(ncol = 1))

surv_model <-
  survfit(Surv(time = os_time, event = os_event) ~ clusters_sat_area_cm2, data = adipose_data)
ggsurvplot(surv_model, data = adipose_data,
           title = "Overall Survival analysis",
           font.main = c(22, "bold", "black"),
           font.x = c(20, "bold", "black"),
           font.y = c(20, "bold", "black"),
           font.legend = c(20, "black"),
           font.tickslab = c(18, "bold", "black"),
           size = 1.5,
           
           xlab = "Time (months)", legend.title = "", 
           pval = TRUE,
           conf.int = FALSE,
           tables.height = 0.25,
           risk.table.title = "Risk table",
           risk.table = TRUE,
           risk.table.y.text = FALSE,
           risk.table.fontsize = 4,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(14, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(14, "bold", "black"))
) + guides(colour = guide_legend(ncol = 1))

surv_model <-
  survfit(Surv(time = os_time, event = os_event) ~ clusters_sat_area_cm2_ind, data = adipose_data)
ggsurvplot(surv_model, data = adipose_data,
           title = "Overall Survival analysis",
           font.main = c(22, "bold", "black"),
           font.x = c(20, "bold", "black"),
           font.y = c(20, "bold", "black"),
           font.legend = c(20, "black"),
           font.tickslab = c(18, "bold", "black"),
           size = 1.5,
           
           xlab = "Time (months)", legend.title = "", 
           pval = TRUE,
           conf.int = FALSE,
           tables.height = 0.25,
           risk.table.title = "Risk table",
           risk.table = TRUE,
           risk.table.y.text = FALSE,
           risk.table.fontsize = 4,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(14, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(14, "bold", "black"))
) + guides(colour = guide_legend(ncol = 1))

surv_model <-
  survfit(Surv(time = os_time, event = os_event) ~ clusters_total_fat_area, data = adipose_data)
ggsurvplot(surv_model, data = adipose_data,
           title = "Overall Survival analysis",
           font.main = c(22, "bold", "black"),
           font.x = c(20, "bold", "black"),
           font.y = c(20, "bold", "black"),
           font.legend = c(20, "black"),
           font.tickslab = c(18, "bold", "black"),
           size = 1.5,
           
           xlab = "Time (months)", legend.title = "", 
           pval = TRUE,
           conf.int = FALSE,
           tables.height = 0.25,
           risk.table.title = "Risk table",
           risk.table = TRUE,
           risk.table.y.text = FALSE,
           risk.table.fontsize = 4,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(14, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(14, "bold", "black"))
) + guides(colour = guide_legend(ncol = 1))

surv_model <-
  survfit(Surv(time = os_time, event = os_event) ~ clusters_total_fat_area_ind, data = adipose_data)
ggsurvplot(surv_model, data = adipose_data,
           title = "Overall Survival analysis",
           font.main = c(22, "bold", "black"),
           font.x = c(20, "bold", "black"),
           font.y = c(20, "bold", "black"),
           font.legend = c(20, "black"),
           font.tickslab = c(18, "bold", "black"),
           size = 1.5,
           
           xlab = "Time (months)", legend.title = "", 
           pval = TRUE,
           conf.int = FALSE,
           tables.height = 0.25,
           risk.table.title = "Risk table",
           risk.table = TRUE,
           risk.table.y.text = FALSE,
           risk.table.fontsize = 4,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(14, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(14, "bold", "black"))
) + guides(colour = guide_legend(ncol = 1))

surv_model <-
  survfit(Surv(time = os_time, event = os_event) ~ clusters_muscle_mean_hu, data = adipose_data)
ggsurvplot(surv_model, data = adipose_data,
           title = "Overall Survival analysis",
           font.main = c(22, "bold", "black"),
           font.x = c(20, "bold", "black"),
           font.y = c(20, "bold", "black"),
           font.legend = c(20, "black"),
           font.tickslab = c(18, "bold", "black"),
           size = 1.5,
           
           xlab = "Time (months)", legend.title = "", 
           pval = TRUE,
           conf.int = FALSE,
           tables.height = 0.25,
           risk.table.title = "Risk table",
           risk.table = TRUE,
           risk.table.y.text = FALSE,
           risk.table.fontsize = 4,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(14, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(14, "bold", "black"))
) + guides(colour = guide_legend(ncol = 1))

surv_model <-
  survfit(Surv(time = os_time, event = os_event) ~ clusters_imat_mean_hu, data = adipose_data)
ggsurvplot(surv_model, data = adipose_data,
           title = "Overall Survival analysis",
           font.main = c(22, "bold", "black"),
           font.x = c(20, "bold", "black"),
           font.y = c(20, "bold", "black"),
           font.legend = c(20, "black"),
           font.tickslab = c(18, "bold", "black"),
           size = 1.5,
           
           xlab = "Time (months)", legend.title = "", 
           pval = TRUE,
           conf.int = FALSE,
           tables.height = 0.25,
           risk.table.title = "Risk table",
           risk.table = TRUE,
           risk.table.y.text = FALSE,
           risk.table.fontsize = 4,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(14, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(14, "bold", "black"))
) + guides(colour = guide_legend(ncol = 1))

surv_model <-
  survfit(Surv(time = os_time, event = os_event) ~ clusters_muscle_hu_sd, data = adipose_data)
ggsurvplot(surv_model, data = adipose_data,
           title = "Overall Survival analysis",
           font.main = c(22, "bold", "black"),
           font.x = c(20, "bold", "black"),
           font.y = c(20, "bold", "black"),
           font.legend = c(20, "black"),
           font.tickslab = c(18, "bold", "black"),
           size = 1.5,
           
           xlab = "Time (months)", legend.title = "", 
           pval = TRUE,
           conf.int = FALSE,
           tables.height = 0.25,
           risk.table.title = "Risk table",
           risk.table = TRUE,
           risk.table.y.text = FALSE,
           risk.table.fontsize = 4,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(14, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(14, "bold", "black"))
) + guides(colour = guide_legend(ncol = 1))

surv_model <-
  survfit(Surv(time = os_time, event = os_event) ~ clusters_v_s_ratio, data = adipose_data)
ggsurvplot(surv_model, data = adipose_data,
           title = "Overall Survival analysis",
           font.main = c(22, "bold", "black"),
           font.x = c(20, "bold", "black"),
           font.y = c(20, "bold", "black"),
           font.legend = c(20, "black"),
           font.tickslab = c(18, "bold", "black"),
           size = 1.5,
           
           xlab = "Time (months)", legend.title = "", 
           pval = TRUE,
           conf.int = FALSE,
           tables.height = 0.25,
           risk.table.title = "Risk table",
           risk.table = TRUE,
           risk.table.y.text = FALSE,
           risk.table.fontsize = 4,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(14, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(14, "bold", "black"))
) + guides(colour = guide_legend(ncol = 1))
```
</div>
</div>

<br>
```{r, fig.height = 8}
surv_model <-
  survfit(Surv(time = os_time, event = os_event) ~ clusters_non_ind, data = adipose_data)
ggsurvplot(surv_model, data = adipose_data,
           title = "Overall Survival analysis",
           font.main = c(20, "bold", "black"),
           font.x = c(18, "bold", "black"),
           font.y = c(18, "bold", "black"),
           font.legend = c(16, "black"),
           font.tickslab = c(16, "bold", "black"),
           size = 1.5,
           xlab = "Time (months)", legend.title = "", 
           pval = TRUE,
           conf.int = FALSE,
           tables.height = 0.25,
           risk.table.title = "Risk table",
           risk.table = TRUE,
           risk.table.y.text = FALSE,
           risk.table.fontsize = 4,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(14, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(14, "bold", "black"))
) + guides(colour = guide_legend(ncol = 1))
```
<br>

## HR for tertiles
###
Multivariable analyses are adjusted by `+ raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type`.  
For visceral features the first table is not adjusted by ascites while the second table is.  

### OS
```{r HR tertiles os}
tbl1 <- adipose_data %>% select(os_event, os_time,
                                tert_muscle_area_cm2, 
                                raceeth1, age_at_diagnosis, tnm_cs_mixed_group_stage, 
                                treatment_type) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$os_time,
                             event = adipose_data$os_event)),
                   exponentiate = TRUE, 
                 include = tert_muscle_area_cm2) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <-
  coxph(Surv(time = adipose_data$os_time,
         event = adipose_data$os_event) ~ tert_muscle_area_cm2 + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_muscle_area_cm2) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

tbl1 <- adipose_data %>% select(os_event, os_time,
                                tert_muscle_area_cm2_ind, 
                                raceeth1, age_at_diagnosis, tnm_cs_mixed_group_stage, 
                                treatment_type) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$os_time,
                             event = adipose_data$os_event)),
                   exponentiate = TRUE, 
                 include = tert_muscle_area_cm2_ind) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <-
  coxph(Surv(time = adipose_data$os_time,
         event = adipose_data$os_event) ~ tert_muscle_area_cm2_ind + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_muscle_area_cm2_ind) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

tbl1 <- adipose_data %>% select(os_event, os_time,
                                tert_imat_area_cm2, 
                                raceeth1, age_at_diagnosis, tnm_cs_mixed_group_stage, 
                                treatment_type) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$os_time,
                             event = adipose_data$os_event)),
                   exponentiate = TRUE, 
                 include = tert_imat_area_cm2) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <-
  coxph(Surv(time = adipose_data$os_time,
         event = adipose_data$os_event) ~ tert_imat_area_cm2 + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_imat_area_cm2) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

tbl1 <- adipose_data %>% select(os_event, os_time,
                                tert_imat_area_cm2_ind, 
                                raceeth1, age_at_diagnosis, tnm_cs_mixed_group_stage, 
                                treatment_type) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$os_time,
                             event = adipose_data$os_event)),
                   exponentiate = TRUE, 
                 include = tert_imat_area_cm2_ind) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <-
  coxph(Surv(time = adipose_data$os_time,
         event = adipose_data$os_event) ~ tert_imat_area_cm2_ind + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_imat_area_cm2_ind) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

tbl1 <- adipose_data %>% select(os_event, os_time,
                                tert_vat_area_cm2, 
                                raceeth1, age_at_diagnosis, tnm_cs_mixed_group_stage, 
                                treatment_type) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$os_time,
                             event = adipose_data$os_event)),
                   exponentiate = TRUE, 
                 include = tert_vat_area_cm2) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <-
  coxph(Surv(time = adipose_data$os_time,
         event = adipose_data$os_event) ~ tert_vat_area_cm2 + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_vat_area_cm2) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

tbl1 <- adipose_data %>% select(os_event, os_time,
                                tert_vat_area_cm2, 
                                raceeth1, age_at_diagnosis, tnm_cs_mixed_group_stage, 
                                treatment_type, ascites) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$os_time,
                             event = adipose_data$os_event)),
                   exponentiate = TRUE, 
                   label = list(tert_vat_area_cm2 ~ "tert_vat_area_cm2 / ascites"),
                 include = tert_vat_area_cm2) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <-
  coxph(Surv(time = adipose_data$os_time,
         event = adipose_data$os_event) ~ tert_vat_area_cm2 + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type + ascites,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 label = list(tert_vat_area_cm2 ~ "tert_vat_area_cm2 / ascites"),
                 include = tert_vat_area_cm2) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

tbl1 <- adipose_data %>% select(os_event, os_time,
                                tert_vat_area_cm2_ind, 
                                raceeth1, age_at_diagnosis, tnm_cs_mixed_group_stage, 
                                treatment_type) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$os_time,
                             event = adipose_data$os_event)),
                   exponentiate = TRUE, 
                 include = tert_vat_area_cm2_ind) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <-
  coxph(Surv(time = adipose_data$os_time,
         event = adipose_data$os_event) ~ tert_vat_area_cm2_ind + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_vat_area_cm2_ind) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

tbl1 <- adipose_data %>% select(os_event, os_time,
                                tert_vat_area_cm2_ind, 
                                raceeth1, age_at_diagnosis, tnm_cs_mixed_group_stage, 
                                treatment_type, ascites) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$os_time,
                             event = adipose_data$os_event)),
                   exponentiate = TRUE, 
                   label = list(tert_vat_area_cm2_ind ~ "tert_vat_area_cm2_ind / ascites"),
                 include = tert_vat_area_cm2_ind) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <-
  coxph(Surv(time = adipose_data$os_time,
         event = adipose_data$os_event) ~ tert_vat_area_cm2_ind + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type + ascites,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 label = list(tert_vat_area_cm2_ind ~ "tert_vat_area_cm2_ind / ascites"),
                 include = tert_vat_area_cm2_ind) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

tbl1 <- adipose_data %>% select(os_event, os_time,
                                tert_sat_area_cm2, 
                                raceeth1, age_at_diagnosis, tnm_cs_mixed_group_stage, 
                                treatment_type) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$os_time,
                             event = adipose_data$os_event)),
                   exponentiate = TRUE, 
                 include = tert_sat_area_cm2) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <-
  coxph(Surv(time = adipose_data$os_time,
         event = adipose_data$os_event) ~ tert_sat_area_cm2 + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_sat_area_cm2) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

tbl1 <- adipose_data %>% select(os_event, os_time,
                                tert_sat_area_cm2_ind, 
                                raceeth1, age_at_diagnosis, tnm_cs_mixed_group_stage, 
                                treatment_type) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$os_time,
                             event = adipose_data$os_event)),
                   exponentiate = TRUE, 
                 include = tert_sat_area_cm2_ind) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <-
  coxph(Surv(time = adipose_data$os_time,
         event = adipose_data$os_event) ~ tert_sat_area_cm2_ind + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_sat_area_cm2_ind) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

tbl1 <- adipose_data %>% select(os_event, os_time,
                                tert_total_fat_area, 
                                raceeth1, age_at_diagnosis, tnm_cs_mixed_group_stage, 
                                treatment_type) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$os_time,
                             event = adipose_data$os_event)),
                   exponentiate = TRUE, 
                 include = tert_total_fat_area) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <-
  coxph(Surv(time = adipose_data$os_time,
         event = adipose_data$os_event) ~ tert_total_fat_area + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_total_fat_area) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

tbl1 <- adipose_data %>% select(os_event, os_time,
                                tert_total_fat_area_ind, 
                                raceeth1, age_at_diagnosis, tnm_cs_mixed_group_stage, 
                                treatment_type) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$os_time,
                             event = adipose_data$os_event)),
                   exponentiate = TRUE, 
                 include = tert_total_fat_area_ind) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <-
  coxph(Surv(time = adipose_data$os_time,
         event = adipose_data$os_event) ~ tert_total_fat_area_ind + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_total_fat_area_ind) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

tbl1 <- adipose_data %>% select(os_event, os_time,
                                tert_muscle_mean_hu, 
                                raceeth1, age_at_diagnosis, tnm_cs_mixed_group_stage, 
                                treatment_type) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$os_time,
                             event = adipose_data$os_event)),
                   exponentiate = TRUE, 
                 include = tert_muscle_mean_hu) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <-
  coxph(Surv(time = adipose_data$os_time,
         event = adipose_data$os_event) ~ tert_muscle_mean_hu + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_muscle_mean_hu) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

tbl1 <- adipose_data %>% select(os_event, os_time,
                                tert_imat_mean_hu, 
                                raceeth1, age_at_diagnosis, tnm_cs_mixed_group_stage, 
                                treatment_type) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$os_time,
                             event = adipose_data$os_event)),
                   exponentiate = TRUE, 
                 include = tert_imat_mean_hu) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <-
  coxph(Surv(time = adipose_data$os_time,
         event = adipose_data$os_event) ~ tert_imat_mean_hu + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_imat_mean_hu) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

tbl1 <- adipose_data %>% select(os_event, os_time,
                                tert_muscle_hu_sd, 
                                raceeth1, age_at_diagnosis, tnm_cs_mixed_group_stage, 
                                treatment_type) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$os_time,
                             event = adipose_data$os_event)),
                   exponentiate = TRUE, 
                 include = tert_muscle_hu_sd) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <-
  coxph(Surv(time = adipose_data$os_time,
         event = adipose_data$os_event) ~ tert_muscle_hu_sd + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_muscle_hu_sd) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

tbl1 <- adipose_data %>% select(os_event, os_time,
                                tert_v_s_ratio, 
                                raceeth1, age_at_diagnosis, tnm_cs_mixed_group_stage, 
                                treatment_type) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$os_time,
                             event = adipose_data$os_event)),
                   exponentiate = TRUE, 
                 include = tert_v_s_ratio) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <-
  coxph(Surv(time = adipose_data$os_time,
         event = adipose_data$os_event) ~ tert_v_s_ratio + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_v_s_ratio) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

tbl1 <- adipose_data %>% select(os_event, os_time,
                                tert_v_s_ratio, 
                                raceeth1, age_at_diagnosis, tnm_cs_mixed_group_stage, 
                                treatment_type, ascites) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$os_time,
                             event = adipose_data$os_event)),
                   exponentiate = TRUE, 
                   label = list(tert_v_s_ratio ~ "tert_v_s_ratio / ascites"),
                 include = tert_v_s_ratio) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <-
  coxph(Surv(time = adipose_data$os_time,
         event = adipose_data$os_event) ~ tert_v_s_ratio + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type + ascites,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 label = list(tert_v_s_ratio ~ "tert_v_s_ratio / ascites"),
                 include = tert_v_s_ratio) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))
```
<br>

### Recurrence
```{r HR tertiles recurrence}
tbl1 <- adipose_data %>% select(rec_event, recurrence_time,
                                tert_muscle_area_cm2, 
                                raceeth1, age_at_diagnosis, tnm_cs_mixed_group_stage, 
                                treatment_type) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$recurrence_time,
                             event = adipose_data$rec_event)),
                   exponentiate = TRUE, 
                   include = tert_muscle_area_cm2) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <-
  coxph(Surv(time = adipose_data$recurrence_time,
         event = adipose_data$rec_event) ~ tert_muscle_area_cm2 + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_muscle_area_cm2) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

tbl1 <- adipose_data %>% select(rec_event, recurrence_time,
                                tert_muscle_area_cm2_ind, 
                                raceeth1, age_at_diagnosis, tnm_cs_mixed_group_stage, 
                                treatment_type) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$recurrence_time,
                             event = adipose_data$rec_event)),
                   exponentiate = TRUE, 
                 include = tert_muscle_area_cm2_ind) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <-
  coxph(Surv(time = adipose_data$recurrence_time,
         event = adipose_data$rec_event) ~ tert_muscle_area_cm2_ind + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_muscle_area_cm2_ind) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

tbl1 <- adipose_data %>% select(rec_event, recurrence_time,
                                tert_imat_area_cm2, 
                                raceeth1, age_at_diagnosis, tnm_cs_mixed_group_stage, 
                                treatment_type) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$recurrence_time,
                             event = adipose_data$rec_event)),
                   exponentiate = TRUE, 
                 include = tert_imat_area_cm2) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <-
  coxph(Surv(time = adipose_data$recurrence_time,
         event = adipose_data$rec_event) ~ tert_imat_area_cm2 + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_imat_area_cm2) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

tbl1 <- adipose_data %>% select(rec_event, recurrence_time,
                                tert_imat_area_cm2_ind, 
                                raceeth1, age_at_diagnosis, tnm_cs_mixed_group_stage, 
                                treatment_type) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$recurrence_time,
                             event = adipose_data$rec_event)),
                   exponentiate = TRUE, 
                 include = tert_imat_area_cm2_ind) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <-
  coxph(Surv(time = adipose_data$recurrence_time,
         event = adipose_data$rec_event) ~ tert_imat_area_cm2_ind + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_imat_area_cm2_ind) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

tbl1 <- adipose_data %>% select(rec_event, recurrence_time,
                                tert_vat_area_cm2, 
                                raceeth1, age_at_diagnosis, tnm_cs_mixed_group_stage, 
                                treatment_type) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$recurrence_time,
                             event = adipose_data$rec_event)),
                   exponentiate = TRUE, 
                 include = tert_vat_area_cm2) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <-
  coxph(Surv(time = adipose_data$recurrence_time,
         event = adipose_data$rec_event) ~ tert_vat_area_cm2 + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_vat_area_cm2) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

tbl1 <- adipose_data %>% select(rec_event, recurrence_time,
                                tert_vat_area_cm2, 
                                raceeth1, age_at_diagnosis, tnm_cs_mixed_group_stage, 
                                treatment_type, ascites) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$recurrence_time,
                             event = adipose_data$rec_event)),
                   exponentiate = TRUE, 
                   label = list(tert_vat_area_cm2 ~ "tert_vat_area_cm2 / ascites"),
                 include = tert_vat_area_cm2) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <-
  coxph(Surv(time = adipose_data$recurrence_time,
         event = adipose_data$rec_event) ~ tert_vat_area_cm2 + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type + ascites,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 label = list(tert_vat_area_cm2 ~ "tert_vat_area_cm2 / ascites"),
                 include = tert_vat_area_cm2) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

tbl1 <- adipose_data %>% select(rec_event, recurrence_time,
                                tert_vat_area_cm2_ind, 
                                raceeth1, age_at_diagnosis, tnm_cs_mixed_group_stage, 
                                treatment_type) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$recurrence_time,
                             event = adipose_data$rec_event)),
                   exponentiate = TRUE, 
                 include = tert_vat_area_cm2_ind) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <-
  coxph(Surv(time = adipose_data$recurrence_time,
         event = adipose_data$rec_event) ~ tert_vat_area_cm2_ind + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_vat_area_cm2_ind) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))


tbl1 <- adipose_data %>% select(rec_event, recurrence_time,
                                tert_vat_area_cm2_ind, 
                                raceeth1, age_at_diagnosis, tnm_cs_mixed_group_stage, 
                                treatment_type, ascites) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$recurrence_time,
                             event = adipose_data$rec_event)),
                   exponentiate = TRUE, 
                   label = list(tert_vat_area_cm2_ind ~ "tert_vat_area_cm2_ind / ascites"),
                 include = tert_vat_area_cm2_ind) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <-
  coxph(Surv(time = adipose_data$recurrence_time,
         event = adipose_data$rec_event) ~ tert_vat_area_cm2_ind + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type + ascites,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 label = list(tert_vat_area_cm2_ind ~ "tert_vat_area_cm2_ind / ascites"),
                 include = tert_vat_area_cm2_ind) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

tbl1 <- adipose_data %>% select(rec_event, recurrence_time,
                                tert_sat_area_cm2, 
                                raceeth1, age_at_diagnosis, tnm_cs_mixed_group_stage, 
                                treatment_type) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$recurrence_time,
                             event = adipose_data$rec_event)),
                   exponentiate = TRUE, 
                 include = tert_sat_area_cm2) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <-
  coxph(Surv(time = adipose_data$recurrence_time,
         event = adipose_data$rec_event) ~ tert_sat_area_cm2 + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_sat_area_cm2) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

tbl1 <- adipose_data %>% select(rec_event, recurrence_time,
                                tert_sat_area_cm2_ind, 
                                raceeth1, age_at_diagnosis, tnm_cs_mixed_group_stage, 
                                treatment_type) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$recurrence_time,
                             event = adipose_data$rec_event)),
                   exponentiate = TRUE, 
                 include = tert_sat_area_cm2_ind) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <-
  coxph(Surv(time = adipose_data$recurrence_time,
         event = adipose_data$rec_event) ~ tert_sat_area_cm2_ind + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_sat_area_cm2_ind) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

tbl1 <- adipose_data %>% select(rec_event, recurrence_time,
                                tert_total_fat_area, 
                                raceeth1, age_at_diagnosis, tnm_cs_mixed_group_stage, 
                                treatment_type) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$recurrence_time,
                             event = adipose_data$rec_event)),
                   exponentiate = TRUE, 
                 include = tert_total_fat_area) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <-
  coxph(Surv(time = adipose_data$recurrence_time,
         event = adipose_data$rec_event) ~ tert_total_fat_area + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_total_fat_area) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

tbl1 <- adipose_data %>% select(rec_event, recurrence_time,
                                tert_total_fat_area_ind, 
                                raceeth1, age_at_diagnosis, tnm_cs_mixed_group_stage, 
                                treatment_type) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$recurrence_time,
                             event = adipose_data$rec_event)),
                   exponentiate = TRUE, 
                 include = tert_total_fat_area_ind) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <-
  coxph(Surv(time = adipose_data$recurrence_time,
         event = adipose_data$rec_event) ~ tert_total_fat_area_ind + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_total_fat_area_ind) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

tbl1 <- adipose_data %>% select(rec_event, recurrence_time,
                                tert_muscle_mean_hu, 
                                raceeth1, age_at_diagnosis, tnm_cs_mixed_group_stage, 
                                treatment_type) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$recurrence_time,
                             event = adipose_data$rec_event)),
                   exponentiate = TRUE, 
                 include = tert_muscle_mean_hu) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <-
  coxph(Surv(time = adipose_data$recurrence_time,
         event = adipose_data$rec_event) ~ tert_muscle_mean_hu + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_muscle_mean_hu) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

tbl1 <- adipose_data %>% select(rec_event, recurrence_time,
                                tert_imat_mean_hu, 
                                raceeth1, age_at_diagnosis, tnm_cs_mixed_group_stage, 
                                treatment_type) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$recurrence_time,
                             event = adipose_data$rec_event)),
                   exponentiate = TRUE, 
                 include = tert_imat_mean_hu) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <-
  coxph(Surv(time = adipose_data$recurrence_time,
         event = adipose_data$rec_event) ~ tert_imat_mean_hu + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_imat_mean_hu) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

tbl1 <- adipose_data %>% select(rec_event, recurrence_time,
                                tert_muscle_hu_sd, 
                                raceeth1, age_at_diagnosis, tnm_cs_mixed_group_stage, 
                                treatment_type) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$recurrence_time,
                             event = adipose_data$rec_event)),
                   exponentiate = TRUE, 
                 include = tert_muscle_hu_sd) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <-
  coxph(Surv(time = adipose_data$recurrence_time,
         event = adipose_data$rec_event) ~ tert_muscle_hu_sd + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_muscle_hu_sd) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

tbl1 <- adipose_data %>% select(rec_event, recurrence_time,
                                tert_v_s_ratio, 
                                raceeth1, age_at_diagnosis, tnm_cs_mixed_group_stage, 
                                treatment_type) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$recurrence_time,
                             event = adipose_data$rec_event)),
                   exponentiate = TRUE, 
                 include = tert_v_s_ratio) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <-
  coxph(Surv(time = adipose_data$recurrence_time,
         event = adipose_data$rec_event) ~ tert_v_s_ratio + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_v_s_ratio) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

tbl1 <- adipose_data %>% select(rec_event, recurrence_time,
                                tert_v_s_ratio, 
                                raceeth1, age_at_diagnosis, tnm_cs_mixed_group_stage, 
                                treatment_type, ascites) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$recurrence_time,
                             event = adipose_data$rec_event)),
                   exponentiate = TRUE, 
                   label = list(tert_v_s_ratio ~ "tert_v_s_ratio / ascites"),
                 include = tert_v_s_ratio) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <-
  coxph(Surv(time = adipose_data$recurrence_time,
         event = adipose_data$rec_event) ~ tert_v_s_ratio + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type + ascites,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 label = list(tert_v_s_ratio ~ "tert_v_s_ratio / ascites"),
                 include = tert_v_s_ratio) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))
```

## Adjusted by debulking status

Multivariable analyses are adjusted by `+ raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type + debulking_status`.  
For visceral features the first table is not adjusted by ascites while the second table is.  

### OS
```{r HR tertiles os adj debul}
tbl1 <- adipose_data %>% select(os_event, os_time,
                                tert_muscle_area_cm2, 
                                raceeth1, age_at_diagnosis, 
                                tnm_cs_mixed_group_stage, 
                                debulking_status,
                                treatment_type) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$os_time,
                             event = adipose_data$os_event)),
                   exponentiate = TRUE, 
                 include = tert_muscle_area_cm2) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <-
  coxph(Surv(time = adipose_data$os_time,
         event = adipose_data$os_event) ~ 
          tert_muscle_area_cm2 + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type + debulking_status,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_muscle_area_cm2) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

tbl1 <- adipose_data %>% select(os_event, os_time,
                                tert_muscle_area_cm2_ind, 
                                raceeth1, age_at_diagnosis, 
                                tnm_cs_mixed_group_stage, 
                                debulking_status,
                                treatment_type) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$os_time,
                             event = adipose_data$os_event)),
                   exponentiate = TRUE, 
                 include = tert_muscle_area_cm2_ind) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <-
  coxph(Surv(time = adipose_data$os_time,
         event = adipose_data$os_event) ~ 
          tert_muscle_area_cm2_ind + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type + debulking_status,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_muscle_area_cm2_ind) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

tbl1 <- adipose_data %>% select(os_event, os_time,
                                tert_imat_area_cm2, 
                                raceeth1, age_at_diagnosis, 
                                tnm_cs_mixed_group_stage, 
                                debulking_status,
                                treatment_type) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$os_time,
                             event = adipose_data$os_event)),
                   exponentiate = TRUE, 
                 include = tert_imat_area_cm2) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <-
  coxph(Surv(time = adipose_data$os_time,
         event = adipose_data$os_event) ~ 
          tert_imat_area_cm2 + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type + debulking_status,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_imat_area_cm2) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

tbl1 <- adipose_data %>% select(os_event, os_time,
                                tert_imat_area_cm2_ind, 
                                raceeth1, age_at_diagnosis, 
                                tnm_cs_mixed_group_stage, 
                                debulking_status,
                                treatment_type) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$os_time,
                             event = adipose_data$os_event)),
                   exponentiate = TRUE, 
                 include = tert_imat_area_cm2_ind) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <-
  coxph(Surv(time = adipose_data$os_time,
         event = adipose_data$os_event) ~ 
          tert_imat_area_cm2_ind + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type + debulking_status,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_imat_area_cm2_ind) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

tbl1 <- adipose_data %>% select(os_event, os_time,
                                tert_vat_area_cm2, 
                                raceeth1, age_at_diagnosis, 
                                tnm_cs_mixed_group_stage, 
                                debulking_status,
                                treatment_type) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$os_time,
                             event = adipose_data$os_event)),
                   exponentiate = TRUE, 
                 include = tert_vat_area_cm2) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <-
  coxph(Surv(time = adipose_data$os_time,
         event = adipose_data$os_event) ~ 
          tert_vat_area_cm2 + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type + debulking_status,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_vat_area_cm2) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

tbl1 <- adipose_data %>% select(os_event, os_time,
                                tert_vat_area_cm2, 
                                raceeth1, age_at_diagnosis, 
                                tnm_cs_mixed_group_stage, 
                                debulking_status,
                                treatment_type, ascites) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$os_time,
                             event = adipose_data$os_event)),
                   exponentiate = TRUE, 
                   label = list(tert_vat_area_cm2 ~ "tert_vat_area_cm2 / ascites"),
                 include = tert_vat_area_cm2) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <-
  coxph(Surv(time = adipose_data$os_time,
         event = adipose_data$os_event) ~ 
          tert_vat_area_cm2 + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type + debulking_status + ascites,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 label = list(tert_vat_area_cm2 ~ "tert_vat_area_cm2 / ascites"),
                 include = tert_vat_area_cm2) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

tbl1 <- adipose_data %>% select(os_event, os_time,
                                tert_vat_area_cm2_ind, 
                                raceeth1, age_at_diagnosis, 
                                tnm_cs_mixed_group_stage, 
                                debulking_status,
                                treatment_type) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$os_time,
                             event = adipose_data$os_event)),
                   exponentiate = TRUE, 
                 include = tert_vat_area_cm2_ind) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <-
  coxph(Surv(time = adipose_data$os_time,
         event = adipose_data$os_event) ~ 
          tert_vat_area_cm2_ind + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type + debulking_status,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_vat_area_cm2_ind) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

tbl1 <- adipose_data %>% select(os_event, os_time,
                                tert_vat_area_cm2_ind, 
                                raceeth1, age_at_diagnosis, 
                                tnm_cs_mixed_group_stage, 
                                debulking_status,
                                treatment_type, ascites) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$os_time,
                             event = adipose_data$os_event)),
                   exponentiate = TRUE, 
                   label = list(tert_vat_area_cm2_ind ~ "tert_vat_area_cm2_ind / ascites"),
                 include = tert_vat_area_cm2_ind) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <-
  coxph(Surv(time = adipose_data$os_time,
         event = adipose_data$os_event) ~ 
          tert_vat_area_cm2_ind + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type + debulking_status + ascites,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 label = list(tert_vat_area_cm2_ind ~ "tert_vat_area_cm2_ind / ascites"),
                 include = tert_vat_area_cm2_ind) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

tbl1 <- adipose_data %>% select(os_event, os_time,
                                tert_sat_area_cm2, 
                                raceeth1, age_at_diagnosis, 
                                tnm_cs_mixed_group_stage, 
                                debulking_status,
                                treatment_type) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$os_time,
                             event = adipose_data$os_event)),
                   exponentiate = TRUE, 
                 include = tert_sat_area_cm2) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <-
  coxph(Surv(time = adipose_data$os_time,
         event = adipose_data$os_event) ~ 
          tert_sat_area_cm2 + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type + debulking_status,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_sat_area_cm2) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

tbl1 <- adipose_data %>% select(os_event, os_time,
                                tert_sat_area_cm2_ind, 
                                raceeth1, age_at_diagnosis, 
                                tnm_cs_mixed_group_stage, 
                                debulking_status,
                                treatment_type) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$os_time,
                             event = adipose_data$os_event)),
                   exponentiate = TRUE, 
                 include = tert_sat_area_cm2_ind) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <-
  coxph(Surv(time = adipose_data$os_time,
         event = adipose_data$os_event) ~ 
          tert_sat_area_cm2_ind + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type + debulking_status,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_sat_area_cm2_ind) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

tbl1 <- adipose_data %>% select(os_event, os_time,
                                tert_total_fat_area, 
                                raceeth1, age_at_diagnosis, 
                                tnm_cs_mixed_group_stage, 
                                debulking_status,
                                treatment_type) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$os_time,
                             event = adipose_data$os_event)),
                   exponentiate = TRUE, 
                 include = tert_total_fat_area) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <-
  coxph(Surv(time = adipose_data$os_time,
         event = adipose_data$os_event) ~ 
          tert_total_fat_area + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type + debulking_status,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_total_fat_area) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

tbl1 <- adipose_data %>% select(os_event, os_time,
                                tert_total_fat_area_ind, 
                                raceeth1, age_at_diagnosis, 
                                tnm_cs_mixed_group_stage, 
                                debulking_status,
                                treatment_type) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$os_time,
                             event = adipose_data$os_event)),
                   exponentiate = TRUE, 
                 include = tert_total_fat_area_ind) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <-
  coxph(Surv(time = adipose_data$os_time,
         event = adipose_data$os_event) ~ 
          tert_total_fat_area_ind + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type + debulking_status,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_total_fat_area_ind) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

tbl1 <- adipose_data %>% select(os_event, os_time,
                                tert_muscle_mean_hu, 
                                raceeth1, age_at_diagnosis, 
                                tnm_cs_mixed_group_stage, 
                                debulking_status,
                                treatment_type) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$os_time,
                             event = adipose_data$os_event)),
                   exponentiate = TRUE, 
                 include = tert_muscle_mean_hu) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <-
  coxph(Surv(time = adipose_data$os_time,
         event = adipose_data$os_event) ~ 
          tert_muscle_mean_hu + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type + debulking_status,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_muscle_mean_hu) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

tbl1 <- adipose_data %>% select(os_event, os_time,
                                tert_imat_mean_hu, 
                                raceeth1, age_at_diagnosis, 
                                tnm_cs_mixed_group_stage, 
                                debulking_status,
                                treatment_type) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$os_time,
                             event = adipose_data$os_event)),
                   exponentiate = TRUE, 
                 include = tert_imat_mean_hu) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <-
  coxph(Surv(time = adipose_data$os_time,
         event = adipose_data$os_event) ~ 
          tert_imat_mean_hu + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type + debulking_status,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_imat_mean_hu) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

tbl1 <- adipose_data %>% select(os_event, os_time,
                                tert_muscle_hu_sd, 
                                raceeth1, age_at_diagnosis, 
                                tnm_cs_mixed_group_stage, 
                                debulking_status,
                                treatment_type) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$os_time,
                             event = adipose_data$os_event)),
                   exponentiate = TRUE, 
                 include = tert_muscle_hu_sd) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <-
  coxph(Surv(time = adipose_data$os_time,
         event = adipose_data$os_event) ~ 
          tert_muscle_hu_sd + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type + debulking_status,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_muscle_hu_sd) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

tbl1 <- adipose_data %>% select(os_event, os_time,
                                tert_v_s_ratio, 
                                raceeth1, age_at_diagnosis, 
                                tnm_cs_mixed_group_stage, 
                                debulking_status,
                                treatment_type) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$os_time,
                             event = adipose_data$os_event)),
                   exponentiate = TRUE, 
                 include = tert_v_s_ratio) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <-
  coxph(Surv(time = adipose_data$os_time,
         event = adipose_data$os_event) ~ 
          tert_v_s_ratio + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type + debulking_status,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_v_s_ratio) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

tbl1 <- adipose_data %>% select(os_event, os_time,
                                tert_v_s_ratio, 
                                raceeth1, age_at_diagnosis, 
                                tnm_cs_mixed_group_stage, 
                                debulking_status,
                                treatment_type, ascites) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$os_time,
                             event = adipose_data$os_event)),
                   exponentiate = TRUE, 
                   label = list(tert_v_s_ratio ~ "tert_v_s_ratio / ascites"),
                 include = tert_v_s_ratio) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <-
  coxph(Surv(time = adipose_data$os_time,
         event = adipose_data$os_event) ~ 
          tert_v_s_ratio + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type + debulking_status + ascites,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 label = list(tert_v_s_ratio ~ "tert_v_s_ratio / ascites"),
                 include = tert_v_s_ratio) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))
```
<br>

### Recurrence
```{r HR tertiles recurrence adj debul}
tbl1 <- adipose_data %>% select(rec_event, recurrence_time,
                                tert_muscle_area_cm2, 
                                raceeth1, age_at_diagnosis, 
                                tnm_cs_mixed_group_stage, 
                                debulking_status,
                                treatment_type) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$recurrence_time,
                             event = adipose_data$rec_event)),
                   exponentiate = TRUE, 
                   include = tert_muscle_area_cm2) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <-
  coxph(Surv(time = adipose_data$recurrence_time,
         event = adipose_data$rec_event) ~ 
          tert_muscle_area_cm2 + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type + debulking_status,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_muscle_area_cm2) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

tbl1 <- adipose_data %>% select(rec_event, recurrence_time,
                                tert_muscle_area_cm2_ind, 
                                raceeth1, age_at_diagnosis, 
                                tnm_cs_mixed_group_stage, 
                                debulking_status,
                                treatment_type) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$recurrence_time,
                             event = adipose_data$rec_event)),
                   exponentiate = TRUE, 
                 include = tert_muscle_area_cm2_ind) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <-
  coxph(Surv(time = adipose_data$recurrence_time,
         event = adipose_data$rec_event) ~ 
          tert_muscle_area_cm2_ind + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type + debulking_status,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_muscle_area_cm2_ind) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

tbl1 <- adipose_data %>% select(rec_event, recurrence_time,
                                tert_imat_area_cm2, 
                                raceeth1, age_at_diagnosis, 
                                tnm_cs_mixed_group_stage, 
                                debulking_status,
                                treatment_type) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$recurrence_time,
                             event = adipose_data$rec_event)),
                   exponentiate = TRUE, 
                 include = tert_imat_area_cm2) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <-
  coxph(Surv(time = adipose_data$recurrence_time,
         event = adipose_data$rec_event) ~ 
          tert_imat_area_cm2 + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type + debulking_status,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_imat_area_cm2) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

tbl1 <- adipose_data %>% select(rec_event, recurrence_time,
                                tert_imat_area_cm2_ind, 
                                raceeth1, age_at_diagnosis, 
                                tnm_cs_mixed_group_stage, 
                                debulking_status,
                                treatment_type) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$recurrence_time,
                             event = adipose_data$rec_event)),
                   exponentiate = TRUE, 
                 include = tert_imat_area_cm2_ind) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <-
  coxph(Surv(time = adipose_data$recurrence_time,
         event = adipose_data$rec_event) ~ 
          tert_imat_area_cm2_ind + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type + debulking_status,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_imat_area_cm2_ind) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

tbl1 <- adipose_data %>% select(rec_event, recurrence_time,
                                tert_vat_area_cm2, 
                                raceeth1, age_at_diagnosis, 
                                tnm_cs_mixed_group_stage, 
                                debulking_status,
                                treatment_type) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$recurrence_time,
                             event = adipose_data$rec_event)),
                   exponentiate = TRUE, 
                 include = tert_vat_area_cm2) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <-
  coxph(Surv(time = adipose_data$recurrence_time,
         event = adipose_data$rec_event) ~ 
          tert_vat_area_cm2 + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type + debulking_status,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_vat_area_cm2) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

tbl1 <- adipose_data %>% select(rec_event, recurrence_time,
                                tert_vat_area_cm2, 
                                raceeth1, age_at_diagnosis, 
                                tnm_cs_mixed_group_stage, 
                                debulking_status,
                                treatment_type, ascites) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$recurrence_time,
                             event = adipose_data$rec_event)),
                   exponentiate = TRUE, 
                   label = list(tert_vat_area_cm2 ~ "tert_vat_area_cm2 / ascites"),
                 include = tert_vat_area_cm2) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <-
  coxph(Surv(time = adipose_data$recurrence_time,
         event = adipose_data$rec_event) ~ 
          tert_vat_area_cm2 + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type + debulking_status + ascites,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 label = list(tert_vat_area_cm2 ~ "tert_vat_area_cm2 / ascites"),
                 include = tert_vat_area_cm2) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

tbl1 <- adipose_data %>% select(rec_event, recurrence_time,
                                tert_vat_area_cm2_ind, 
                                raceeth1, age_at_diagnosis, 
                                tnm_cs_mixed_group_stage, 
                                debulking_status,
                                treatment_type) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$recurrence_time,
                             event = adipose_data$rec_event)),
                   exponentiate = TRUE, 
                 include = tert_vat_area_cm2_ind) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <-
  coxph(Surv(time = adipose_data$recurrence_time,
         event = adipose_data$rec_event) ~ 
          tert_vat_area_cm2_ind + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type + debulking_status,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_vat_area_cm2_ind) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))


tbl1 <- adipose_data %>% select(rec_event, recurrence_time,
                                tert_vat_area_cm2_ind, 
                                raceeth1, age_at_diagnosis, 
                                tnm_cs_mixed_group_stage, 
                                debulking_status,
                                treatment_type, ascites) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$recurrence_time,
                             event = adipose_data$rec_event)),
                   exponentiate = TRUE, 
                   label = list(tert_vat_area_cm2_ind ~ "tert_vat_area_cm2_ind / ascites"),
                 include = tert_vat_area_cm2_ind) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <-
  coxph(Surv(time = adipose_data$recurrence_time,
         event = adipose_data$rec_event) ~ 
          tert_vat_area_cm2_ind + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type + debulking_status + ascites,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 label = list(tert_vat_area_cm2_ind ~ "tert_vat_area_cm2_ind / ascites"),
                 include = tert_vat_area_cm2_ind) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

tbl1 <- adipose_data %>% select(rec_event, recurrence_time,
                                tert_sat_area_cm2, 
                                raceeth1, age_at_diagnosis, 
                                tnm_cs_mixed_group_stage, 
                                debulking_status,
                                treatment_type) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$recurrence_time,
                             event = adipose_data$rec_event)),
                   exponentiate = TRUE, 
                 include = tert_sat_area_cm2) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <-
  coxph(Surv(time = adipose_data$recurrence_time,
         event = adipose_data$rec_event) ~ 
          tert_sat_area_cm2 + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type + debulking_status,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_sat_area_cm2) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

tbl1 <- adipose_data %>% select(rec_event, recurrence_time,
                                tert_sat_area_cm2_ind, 
                                raceeth1, age_at_diagnosis, 
                                tnm_cs_mixed_group_stage, 
                                debulking_status,
                                treatment_type) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$recurrence_time,
                             event = adipose_data$rec_event)),
                   exponentiate = TRUE, 
                 include = tert_sat_area_cm2_ind) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <-
  coxph(Surv(time = adipose_data$recurrence_time,
         event = adipose_data$rec_event) ~ 
          tert_sat_area_cm2_ind + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type + debulking_status,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_sat_area_cm2_ind) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

tbl1 <- adipose_data %>% select(rec_event, recurrence_time,
                                tert_total_fat_area, 
                                raceeth1, age_at_diagnosis, 
                                tnm_cs_mixed_group_stage, 
                                debulking_status,
                                treatment_type) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$recurrence_time,
                             event = adipose_data$rec_event)),
                   exponentiate = TRUE, 
                 include = tert_total_fat_area) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <-
  coxph(Surv(time = adipose_data$recurrence_time,
         event = adipose_data$rec_event) ~ 
          tert_total_fat_area + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type + debulking_status,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_total_fat_area) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

tbl1 <- adipose_data %>% select(rec_event, recurrence_time,
                                tert_total_fat_area_ind, 
                                raceeth1, age_at_diagnosis, 
                                tnm_cs_mixed_group_stage, 
                                debulking_status,
                                treatment_type) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$recurrence_time,
                             event = adipose_data$rec_event)),
                   exponentiate = TRUE, 
                 include = tert_total_fat_area_ind) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <-
  coxph(Surv(time = adipose_data$recurrence_time,
         event = adipose_data$rec_event) ~ 
          tert_total_fat_area_ind + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type + debulking_status,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_total_fat_area_ind) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

tbl1 <- adipose_data %>% select(rec_event, recurrence_time,
                                tert_muscle_mean_hu, 
                                raceeth1, age_at_diagnosis, 
                                tnm_cs_mixed_group_stage, 
                                debulking_status,
                                treatment_type) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$recurrence_time,
                             event = adipose_data$rec_event)),
                   exponentiate = TRUE, 
                 include = tert_muscle_mean_hu) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <-
  coxph(Surv(time = adipose_data$recurrence_time,
         event = adipose_data$rec_event) ~ 
          tert_muscle_mean_hu + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type + debulking_status,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_muscle_mean_hu) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

tbl1 <- adipose_data %>% select(rec_event, recurrence_time,
                                tert_imat_mean_hu, 
                                raceeth1, age_at_diagnosis, 
                                tnm_cs_mixed_group_stage, 
                                debulking_status,
                                treatment_type) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$recurrence_time,
                             event = adipose_data$rec_event)),
                   exponentiate = TRUE, 
                 include = tert_imat_mean_hu) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <-
  coxph(Surv(time = adipose_data$recurrence_time,
         event = adipose_data$rec_event) ~ 
          tert_imat_mean_hu + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type + debulking_status,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_imat_mean_hu) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

tbl1 <- adipose_data %>% select(rec_event, recurrence_time,
                                tert_muscle_hu_sd, 
                                raceeth1, age_at_diagnosis, 
                                tnm_cs_mixed_group_stage, 
                                debulking_status,
                                treatment_type) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$recurrence_time,
                             event = adipose_data$rec_event)),
                   exponentiate = TRUE, 
                 include = tert_muscle_hu_sd) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <-
  coxph(Surv(time = adipose_data$recurrence_time,
         event = adipose_data$rec_event) ~ 
          tert_muscle_hu_sd + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type + debulking_status,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_muscle_hu_sd) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

tbl1 <- adipose_data %>% select(rec_event, recurrence_time,
                                tert_v_s_ratio, 
                                raceeth1, age_at_diagnosis, 
                                tnm_cs_mixed_group_stage, 
                                debulking_status,
                                treatment_type) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$recurrence_time,
                             event = adipose_data$rec_event)),
                   exponentiate = TRUE, 
                 include = tert_v_s_ratio) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <-
  coxph(Surv(time = adipose_data$recurrence_time,
         event = adipose_data$rec_event) ~ 
          tert_v_s_ratio + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type + debulking_status,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_v_s_ratio) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

tbl1 <- adipose_data %>% select(rec_event, recurrence_time,
                                tert_v_s_ratio, 
                                raceeth1, age_at_diagnosis, 
                                tnm_cs_mixed_group_stage, 
                                debulking_status,
                                treatment_type, ascites) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$recurrence_time,
                             event = adipose_data$rec_event)),
                   exponentiate = TRUE, 
                   label = list(tert_v_s_ratio ~ "tert_v_s_ratio / ascites"),
                 include = tert_v_s_ratio) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <-
  coxph(Surv(time = adipose_data$recurrence_time,
         event = adipose_data$rec_event) ~ 
          tert_v_s_ratio + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type + debulking_status + ascites,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 label = list(tert_v_s_ratio ~ "tert_v_s_ratio / ascites"),
                 include = tert_v_s_ratio) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))
```

# Investigate IMAT / survival
```{r}
adipose_data %>% 
  mutate(os_event = factor(os_event)) %>% 
  ggplot(aes(x=os_time, y= imat_area_cm2, color= tert_imat_area_cm2, shape= os_event))+
  geom_point()+
  scale_shape_manual(values=c(3, 16))+
  theme_minimal()+
  facet_wrap(. ~ treatment_type)
```
In upfront chemo medium tertile we see more "+" shape
```{r}
adipose_data %>% 
  select(imat_area_cm2, tert_imat_area_cm2, os_event) %>% 
  
  tbl_summary(by= os_event
    # type = list(year_of_diagnosis ~ "categorical", 
    #                       all_dichotomous() ~ "categorical"), 
    #         statistic=list(all_continuous() ~ "{mean} ({sd})"), 
    #         digits = all_continuous() ~ 1
    )

adipose_data %>% 
  mutate(os_event = factor(os_event)) %>% 
  ggplot(aes(x=os_event, y= imat_area_cm2, color= tert_imat_area_cm2))+
  geom_boxplot()+
  # scale_shape_manual(values=c(3, 16))+
  theme_minimal()+
  facet_wrap(. ~ treatment_type)

adipose_data %>% 
  # mutate(os_event = factor(os_event)) %>% 
  group_by(tert_imat_area_cm2, os_event, treatment_type) %>% 
  summarise(mean = mean(imat_area_cm2),
            time = mean(os_time)) %>% 
  ggplot(aes(x=(mean), y= time, color= tert_imat_area_cm2))+
  geom_point()+
  # scale_shape_manual(values=c(3, 16))+
  theme_minimal()+
  facet_wrap(os_event ~ treatment_type)
```


<!-- <div class = "row"> -->
<!-- <div class = "col-md-6"> -->
<!-- ```{r} -->

<!-- ``` -->
<!-- </div> -->

<!-- <div class = "col-md-6"> -->
<!-- ```{r} -->

<!-- ``` -->
<!-- </div> -->
<!-- </div> -->

