---
title: "Adiposity Radiomics"
author: "Christelle Colin-Leitzinger"
date: "`r Sys.Date()`"
output:
  word_document:
    toc: yes
editor_options:
  chunk_output_type: console
always_allow_html: yes
---

<style type="text/css">

.figure {
   margin-top: 25px;
   margin-bottom: 100px;
}

table {
    margin-top: 10px;
    margin-bottom: 25px;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE,
                      cache = FALSE,
                      fig.align='center'
                      )
# options(gtsummary.print_engine = "gt")
# options(gtsummary.as_gt.addl_cmds = "gt::tab_options(table.font.size = 14, data_row.padding = gt::px(1))")
```

```{r library}
library(tidyverse)
library(ggplot2)
library(mclust)
library(data.table)
library(gtsummary)
library(survival)
library(survminer)
# library(VIM)
library(mice)
```

```{r load}
adipose_data <- read_rds(paste0(here::here(), "/adipose_data.rds")) %>% 
  mutate(raceeth2 = case_when(
    raceeth == "White Non-Hispanic"       ~ "White Non-Hispanic",
    raceeth == "Black Non-Hispanic" |
      raceeth == "Hispanic"               ~ "Black or Hispanic"
  ))
```

<br>

Note: I excluded the patient noted in "should exclude" variable.  
This exclude 2 out of the 3 patients with missing TNM.  

`_ind variables were calculated by dividing the initial value by (height_m_ ^ 2)`
`_HR variables were calculated by dividing the initial value by the SD overall patients`

`SMI = muscle_area_cm2 / (height_m_ * height_m_)`  
`sarcopenia is Yes when SMI ≤ 38.73 cm2/m2`  
`martin is Yes when < 41 cm2/m2`

```{r include=TRUE}
# mutate(SMI = muscle_area_cm2 / (height_m_ * height_m_)) %>% 
#   mutate(sarcopenia = case_when(
#     SMI <= 38.73                                     ~ "Yes",
#     TRUE                                             ~ "No"
#   )) %>% 
#   mutate(martin = case_when(
#     SMI < 41                                        ~ "Sarcopenia",
#     TRUE                                             ~ "No sarcopenia"
#   ))
```
<br>

***

# I.  Data summary
## 1. Table 1. Patient characteristics overall


# USE as_kable()
```{r}
adipose_data %>% 
  select(age_at_diagnosis, year_of_diagnosis, raceeth, raceeth1,
         bmi, bmi_cat, bmi_cat2,
         treatment_type, 
         debulking_status, tnm_cs_mixed_group_stage, ecog_pretrt, 
         preDx_comorbidities, preDx_hypertension, preDx_diabetes_mellitus, 
         preDx_hypercholesterolemia, preDx_cardiac_conditions, 
         preDx_chronic_kidney_disease, 
         ascites, ascites2, sarcopenia, martin,
         vital_new, os_time,
         has_the_patient_recurred, recurrence_time) %>% 
  
  tbl_summary(
    type = list(year_of_diagnosis ~ "categorical", 
                all_dichotomous() ~ "categorical"), 
    statistic=list(all_continuous() ~ "{mean} ({sd})"), 
    digits = all_continuous() ~ 1
  ) %>%  
  bold_labels() %>% add_stat_label() %>% 
  modify_footnote(update = everything() ~ NA) %>% as_kable()
```

# USE as_hux_table()
```{r}
adipose_data %>% 
  select(age_at_diagnosis, year_of_diagnosis, raceeth, raceeth1,
         bmi, bmi_cat, bmi_cat2,
         treatment_type, 
         debulking_status, tnm_cs_mixed_group_stage, ecog_pretrt, 
         preDx_comorbidities, preDx_hypertension, preDx_diabetes_mellitus, 
         preDx_hypercholesterolemia, preDx_cardiac_conditions, 
         preDx_chronic_kidney_disease, 
         ascites, ascites2, sarcopenia, martin,
         vital_new, os_time,
         has_the_patient_recurred, recurrence_time) %>% 
  
  tbl_summary(
    type = list(year_of_diagnosis ~ "categorical", 
                all_dichotomous() ~ "categorical"), 
    statistic=list(all_continuous() ~ "{mean} ({sd})"), 
    digits = all_continuous() ~ 1
  ) %>%  
  bold_labels() %>% add_stat_label() %>% 
  modify_footnote(update = everything() ~ NA) %>% as_hux_table()
```

# USE as_flex_table()
```{r}
adipose_data %>% 
  select(age_at_diagnosis, year_of_diagnosis, raceeth, raceeth1,
         bmi, bmi_cat, bmi_cat2,
         treatment_type, 
         debulking_status, tnm_cs_mixed_group_stage, ecog_pretrt, 
         preDx_comorbidities, preDx_hypertension, preDx_diabetes_mellitus, 
         preDx_hypercholesterolemia, preDx_cardiac_conditions, 
         preDx_chronic_kidney_disease, 
         ascites, ascites2, sarcopenia, martin,
         vital_new, os_time,
         has_the_patient_recurred, recurrence_time) %>% 
  
  tbl_summary(by= treatment_type,
              type = list(year_of_diagnosis ~ "categorical", 
                          all_dichotomous() ~ "categorical"), 
              statistic=list(all_continuous() ~ "{mean} ({sd})"), 
              digits = all_continuous() ~ 1
  ) %>%  
  bold_labels() %>% add_stat_label() %>% 
  add_p() %>% bold_p(t = .05) %>% 
  modify_footnote(update = everything() ~ NA) %>% as_flex_table()
```

