---
title: "Adiposity Radiomics Upfront Neoadjuvant patients"
author: "Christelle Colin-Leitzinger"
date: '`r Sys.Date()`'
output: 
  html_document:
    toc: true
    toc_float: true
    toc_collapsed: false
    theme: united
    highlight: pygments
    df_print: paged
editor_options: 
  chunk_output_type: console
---

<style type="text/css">

.figure {
   margin-top: 25px;
   margin-bottom: 100px;
}

table {
    margin-top: 10px;
    margin-bottom: 25px;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE,
                      cache = FALSE,
                      fig.align='center'
                      )
options(gtsummary.print_engine = "gt")
options(gtsummary.as_gt.addl_cmds = "gt::tab_options(table.font.size = 14, data_row.padding = gt::px(1))")
```

```{r library}
library(tidyverse)
library(mclust)
library(data.table)
library(gtsummary)
library(survival)
library(survminer)
```

```{r load test-retest}
path <- fs::path("","Volumes","Peres_Research", "Ovarian - Radiomics", "CTbased adiposity")

adipose_data <- read_rds(paste0(here::here(), "/adipose_data_with_groups.rds")) %>% 
  filter(treatment_type == "Upfront Neoadjuvant")
```

<br>

Note: I excluded the patient noted in "should exclude" variable.  
Also the patient with missing TNM was removed.  

<br>

***

# Data summary
## Table 1. Patient characteristics overall

```{r}
adipose_data %>% 
  select(age_at_diagnosis, year_of_diagnosis, raceeth, raceeth1,
         debulking_status, tnm_cs_mixed_group_stage, ecog_pretrt, 
         preDx_comorbidities, preDx_hypertension, preDx_diabetes_mellitus, 
         preDx_hypercholesterolemia, preDx_cardiac_conditions, 
         preDx_chronic_kidney_disease, 
         ascites,
         vital_new, os_time, 
         has_the_patient_recurred, recurrence_time) %>% 
  
  tbl_summary(
    type = list(year_of_diagnosis ~ "categorical", 
                          all_dichotomous() ~ "categorical"), 
            statistic=list(all_continuous() ~ "{mean} ({sd})"), 
            digits = all_continuous() ~ 1
    ) %>%  
  bold_labels() %>% add_stat_label() %>% 
  modify_footnote(update = everything() ~ NA)
```

## Table 2. CT-based measures of adiposity

```{r}
tbl1 <- adipose_data %>% 
  select(thickness, muscle_area_cm2, muscle_area_cm2_ind,
         imat_area_cm2, imat_area_cm2_ind,
         vat_area_cm2, vat_area_cm2_ind,
         sat_area_cm2, sat_area_cm2_ind,
         muscle_mean_hu,                    
         v_s_ratio, 
         total_fat_area, total_fat_area_ind) %>% 
  tbl_summary(
            statistic=list(all_continuous() ~ "{mean} ({sd})"), 
            type = list(thickness ~ "continuous"),
            digits = all_continuous() ~ 1
            ) %>%  
  bold_labels() %>% 
  modify_header(
    update = list(
      stat_0 ~ "**Mean (SD)**"))

tbl2 <- adipose_data %>% 
  select(thickness, muscle_area_cm2, muscle_area_cm2_ind,
         imat_area_cm2, imat_area_cm2_ind,
         vat_area_cm2, vat_area_cm2_ind,
         sat_area_cm2, sat_area_cm2_ind,
         muscle_mean_hu,                    
         v_s_ratio, 
         total_fat_area, total_fat_area_ind) %>% 
  tbl_summary(
            statistic=list(all_continuous() ~ "{median}"), 
            type = list(thickness ~ "continuous"),
            digits = all_continuous() ~ 1
            ) %>%  
  bold_labels()  %>% 
  modify_header(
    update = list(
      stat_0 ~ "**Median**"))
tbl3 <- adipose_data %>% 
  select(thickness, muscle_area_cm2, muscle_area_cm2_ind,
         imat_area_cm2, imat_area_cm2_ind,
         vat_area_cm2, vat_area_cm2_ind,
         sat_area_cm2, sat_area_cm2_ind,
         muscle_mean_hu,                    
         v_s_ratio, 
         total_fat_area, total_fat_area_ind) %>% 
  tbl_summary(
            statistic=list(all_continuous() ~ "{min} - {max}"), 
            type = list(thickness ~ "continuous"),
            digits = all_continuous() ~ 1
            ) %>%  
  bold_labels() %>% 
  modify_header(
    update = list(
      stat_0 ~ "**Range**"))
tbl_merge(list(tbl1, tbl2, tbl3)) %>%
  modify_spanning_header(everything() ~ NA_character_)
```

```{r, fig.width= 12, fig.height= 12}
# adipose_data %>% 
#   select(mrn, bmi_cat,
#          "muscle_area_cm2", muscle_area_cm2_ind,
#          imat_area_cm2, imat_area_cm2_ind,
#          vat_area_cm2, vat_area_cm2_ind,
#          sat_area_cm2, sat_area_cm2_ind,
#          "total_fat_area", total_fat_area_ind,
#          muscle_mean_hu,                    
#          imat_mean_hu,
#          muscle_hu_sd, v_s_ratio) %>% 
#   pivot_longer(-c(mrn, bmi_cat)) %>% 
#   ggplot(aes(x= name, y= value, color = bmi_cat))+
#   geom_boxplot()+
#   theme_minimal()+
#   coord_flip()

adipose_data %>% 
  select(mrn, bmi_cat,
         muscle_area_cm2, muscle_area_cm2_ind,
         imat_area_cm2, imat_area_cm2_ind,
         vat_area_cm2, vat_area_cm2_ind,
         sat_area_cm2, sat_area_cm2_ind,
         total_fat_area, total_fat_area_ind,
         muscle_mean_hu,                    
         v_s_ratio) %>% 
  pivot_longer(-c(mrn, bmi_cat)) %>% 
  mutate(name = factor(name, 
                       levels = c(
                         "muscle_area_cm2", "muscle_area_cm2_ind",
                         "imat_area_cm2", "imat_area_cm2_ind",
                         "vat_area_cm2", "vat_area_cm2_ind",
                         "sat_area_cm2", "sat_area_cm2_ind",
                         "total_fat_area", "total_fat_area_ind",
                         "muscle_mean_hu",                    
                         "v_s_ratio"
                       ))) %>% 
  ggplot(aes(x= bmi_cat, y= value, color = bmi_cat))+
  geom_boxplot()+
  theme_minimal()+
  coord_flip()+
  # facet_grid(cols = vars(name), scales = "free")
  facet_wrap(.~ name, scales = "free", ncol = 2)
```
<br>

```{r}
adipose_data %>% 
  select(muscle_area_cm2, muscle_area_cm2_ind,
         imat_area_cm2, imat_area_cm2_ind,
         vat_area_cm2, vat_area_cm2_ind,
         sat_area_cm2, sat_area_cm2_ind,
         muscle_mean_hu,                    
         v_s_ratio, 
         total_fat_area, total_fat_area_ind,
         treatment_type) %>% 
  tbl_summary(by = treatment_type,
            statistic=list(all_continuous() ~ "{mean} ({sd})"), 
            digits = all_continuous() ~ 1
            ) %>%  
  bold_labels() %>% add_p() %>% bold_p(t= 0.05)
```
<br>

## Unknown debulking_status look like Complete/Optimal debulking_status

```{r}
data <- adipose_data %>% 
  mutate(debulking_status = case_when(
    is.na(debulking_status)           ~ "unkn",
    TRUE                              ~ debulking_status
  ))
mysurv <- Surv(data$recurrence_time, event = data$rec_event)
myplot <- survfit(mysurv~debulking_status, data = data)
ggsurvplot(myplot, data = data,
           title = "Recurrence Analysis",
           font.main = c(20, "bold", "black"),
           font.x = c(18, "bold", "black"),
           font.y = c(18, "bold", "black"),
           font.legend = c(16, "black"),
           font.tickslab = c(16, "bold", "black"),
           size = 1.5,

           xlab = "Time in months",
           legend = "top",
           legend.title = "",
           pval = TRUE,
           conf.int = FALSE,
           # Censor
           censor = TRUE
) + guides(colour = guide_legend(ncol = 1))
```
```{r}
mysurv <- Surv(data$os_time, event = data$os_event)
myplot <- survfit(mysurv~debulking_status, data = data)
ggsurvplot(myplot, data = data,
           title = "OS Analysis",
           font.main = c(20, "bold", "black"),
           font.x = c(18, "bold", "black"),
           font.y = c(18, "bold", "black"),
           font.legend = c(16, "black"),
           font.tickslab = c(16, "bold", "black"),
           size = 1.5,

           xlab = "Time in months",
           legend = "top",
           legend.title = "",
           pval = TRUE,
           conf.int = FALSE,
           # Censor
           censor = TRUE
) + guides(colour = guide_legend(ncol = 1))
```
<br>

## KM BMI (unknown debulking status are not removed)
<br>

```{r echo=TRUE}
# BMI cat grouping
# (bmi_cat = case_when(
#     bmi < 25                    ~ "Underweight and normal weight",
#     bmi >= 25 &
#       bmi < 30                  ~ "Overweight",
#     bmi >= 30                   ~ "Obese"
#   ))
```

```{r}
mysurv <- Surv(adipose_data$recurrence_time, event = adipose_data$rec_event)
myplot <- survfit(mysurv~bmi_cat, data = adipose_data)
ggsurvplot(myplot, data = adipose_data,
           title = "Recurrence Analysis",
           font.main = c(20, "bold", "black"),
           font.x = c(18, "bold", "black"),
           font.y = c(18, "bold", "black"),
           font.legend = c(16, "black"),
           font.tickslab = c(16, "bold", "black"),
           size = 1.5,

           xlab = "Time in months",
           legend = "top",
           legend.title = "",
           # legend.labs = c("White Non-Hispanic", "Hispanic", "Black"),
           # palette = c("#03051AFF", "blue", "red"),
           pval = TRUE,
           conf.int = FALSE,
           # Censor
           censor = TRUE
) + guides(colour = guide_legend(ncol = 1))
```

```{r}
tbl1 <- adipose_data %>% select(rec_event, recurrence_time,
                            raceeth1, age_at_diagnosis, tnm_cs_mixed_group_stage, 
                            bmi, bmi_cat) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$recurrence_time,
                             event = adipose_data$rec_event)),
                   exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") %>%
  bold_labels() %>% italicize_levels()
tbl2 <- 
  coxph(Surv(time = adipose_data$recurrence_time,
             event = adipose_data$rec_event) ~ raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + bmi_cat, data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))
```

```{r}
mysurv <- Surv(adipose_data$os_time, event = adipose_data$os_event)
myplot <- survfit(mysurv~bmi_cat, data = adipose_data)
ggsurvplot(myplot, data = adipose_data,
           title = "OS Analysis",
           font.main = c(20, "bold", "black"),
           font.x = c(18, "bold", "black"),
           font.y = c(18, "bold", "black"),
           font.legend = c(16, "black"),
           font.tickslab = c(16, "bold", "black"),
           size = 1.5,

           xlab = "Time in months",
           legend = "top",
           legend.title = "",
           # legend.labs = c("White Non-Hispanic", "Hispanic", "Black"),
           # palette = c("#03051AFF", "blue", "red"),
           pval = TRUE,
           conf.int = FALSE,
           # Censor
           censor = TRUE
) + guides(colour = guide_legend(ncol = 1))
```

```{r}
tbl1 <- adipose_data %>% select(os_event, os_time,
                            raceeth1, age_at_diagnosis, tnm_cs_mixed_group_stage, 
                            bmi, bmi_cat) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$os_time,
                             event = adipose_data$os_event)),
                   exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") %>%
  bold_labels() %>% italicize_levels()
tbl2 <- 
  coxph(Surv(time = adipose_data$os_time,
             event = adipose_data$os_event) ~ raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + bmi_cat, data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))
```
<br>
<br>

## Univariable HR continous radiomics : recurrence
```{r univariable}
tbl1 <- adipose_data %>% select(rec_event, recurrence_time,
                        muscle_area_cm2_HR, muscle_area_cm2_ind_HR,
                        imat_area_cm2_HR, imat_area_cm2_ind_HR,
                        vat_area_cm2_HR, vat_area_cm2_ind_HR,
                        sat_area_cm2_HR, sat_area_cm2_ind_HR,
                        total_fat_area_HR, total_fat_area_ind_HR,
                        muscle_mean_hu_HR,                    
                        v_s_ratio_HR) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$recurrence_time,
                             event = adipose_data$rec_event)),
                   exponentiate = TRUE) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")

tbl2 <-
  coxph(Surv(time = adipose_data$recurrence_time,
         event = adipose_data$rec_event) ~ muscle_area_cm2_HR + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = muscle_area_cm2_HR) %>% bold_p(t = .05)
tbl3 <-
  coxph(Surv(time = adipose_data$recurrence_time,
         event = adipose_data$rec_event) ~ muscle_area_cm2_ind_HR + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = muscle_area_cm2_ind_HR) %>% bold_p(t = .05)
tbl4 <-
  coxph(Surv(time = adipose_data$recurrence_time,
         event = adipose_data$rec_event) ~ imat_area_cm2_HR + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = imat_area_cm2_HR) %>% bold_p(t = .05)
tbl5 <-
  coxph(Surv(time = adipose_data$recurrence_time,
         event = adipose_data$rec_event) ~ imat_area_cm2_ind_HR + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = imat_area_cm2_ind_HR) %>% bold_p(t = .05)
tbl6 <-
  coxph(Surv(time = adipose_data$recurrence_time,
         event = adipose_data$rec_event) ~ vat_area_cm2_HR + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = vat_area_cm2_HR) %>% bold_p(t = .05)
tbl7 <-
  coxph(Surv(time = adipose_data$recurrence_time,
         event = adipose_data$rec_event) ~ vat_area_cm2_ind_HR + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = vat_area_cm2_ind_HR) %>% bold_p(t = .05)
tbl8 <-
  coxph(Surv(time = adipose_data$recurrence_time,
         event = adipose_data$rec_event) ~ sat_area_cm2_HR + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = sat_area_cm2_HR) %>% bold_p(t = .05)
tbl9 <-
  coxph(Surv(time = adipose_data$recurrence_time,
         event = adipose_data$rec_event) ~ sat_area_cm2_ind_HR + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = sat_area_cm2_ind_HR) %>% bold_p(t = .05)
tbl10 <-
  coxph(Surv(time = adipose_data$recurrence_time,
         event = adipose_data$rec_event) ~ total_fat_area_HR + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = total_fat_area_HR) %>% bold_p(t = .05)
tbl11 <-
  coxph(Surv(time = adipose_data$recurrence_time,
         event = adipose_data$rec_event) ~ total_fat_area_ind_HR + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = total_fat_area_ind_HR) %>% bold_p(t = .05)
tbl12 <-
  coxph(Surv(time = adipose_data$recurrence_time,
         event = adipose_data$rec_event) ~ muscle_mean_hu_HR + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = muscle_mean_hu_HR) %>% bold_p(t = .05)
tbl13 <-
  coxph(Surv(time = adipose_data$recurrence_time,
         event = adipose_data$rec_event) ~ v_s_ratio_HR + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = v_s_ratio_HR) %>% bold_p(t = .05)
tbl14 <-
  coxph(Surv(time = adipose_data$recurrence_time,
         event = adipose_data$rec_event) ~ v_s_ratio_HR + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + ascites,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                label = list(v_s_ratio_HR ~ "V/S adjusted by ascites"),
                 include = v_s_ratio_HR) %>% bold_p(t = .05)

tbl2 <- tbl_stack(list(tbl2, tbl3, tbl4, tbl5,
               tbl6, tbl7, tbl8, tbl9, tbl10,
               tbl11, tbl12, tbl13, tbl14))

tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))
```

Adjusted for ascites
```{r}
coxph(Surv(time = adipose_data$recurrence_time,
         event = adipose_data$rec_event) ~ vat_area_cm2_HR + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + ascites,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = vat_area_cm2_HR) %>% bold_p(t = .05)
coxph(Surv(time = adipose_data$recurrence_time,
         event = adipose_data$rec_event) ~ vat_area_cm2_ind_HR + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + ascites,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = vat_area_cm2_ind_HR) %>% bold_p(t = .05)

```

## Univariable HR continous radiomics : OS
```{r}
tbl1 <- adipose_data %>% select(os_event, os_time,
                        muscle_area_cm2_HR, muscle_area_cm2_ind_HR,
                        imat_area_cm2_HR, imat_area_cm2_ind_HR,
                        vat_area_cm2_HR, vat_area_cm2_ind_HR,
                        sat_area_cm2_HR, sat_area_cm2_ind_HR,
                        total_fat_area_HR, total_fat_area_ind_HR,
                        muscle_mean_hu_HR,                    
                        v_s_ratio_HR) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$os_time,
                             event = adipose_data$os_event)),
                   exponentiate = TRUE) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")

tbl2 <-
  coxph(Surv(time = adipose_data$os_time,
         event = adipose_data$os_event) ~ muscle_area_cm2_HR + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = muscle_area_cm2_HR) %>% bold_p(t = .05)
tbl3 <-
  coxph(Surv(time = adipose_data$os_time,
         event = adipose_data$os_event) ~ muscle_area_cm2_ind_HR + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = muscle_area_cm2_ind_HR) %>% bold_p(t = .05)
tbl4 <-
  coxph(Surv(time = adipose_data$os_time,
         event = adipose_data$os_event) ~ imat_area_cm2_HR + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = imat_area_cm2_HR) %>% bold_p(t = .05)
tbl5 <-
  coxph(Surv(time = adipose_data$os_time,
         event = adipose_data$os_event) ~ imat_area_cm2_ind_HR + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = imat_area_cm2_ind_HR) %>% bold_p(t = .05)
tbl6 <-
  coxph(Surv(time = adipose_data$os_time,
         event = adipose_data$os_event) ~ vat_area_cm2_HR + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = vat_area_cm2_HR) %>% bold_p(t = .05)
tbl7 <-
  coxph(Surv(time = adipose_data$os_time,
         event = adipose_data$os_event) ~ vat_area_cm2_ind_HR + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = vat_area_cm2_ind_HR) %>% bold_p(t = .05)
tbl8 <-
  coxph(Surv(time = adipose_data$os_time,
         event = adipose_data$os_event) ~ sat_area_cm2_HR + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = sat_area_cm2_HR) %>% bold_p(t = .05)
tbl9 <-
  coxph(Surv(time = adipose_data$os_time,
         event = adipose_data$os_event) ~ sat_area_cm2_ind_HR + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = sat_area_cm2_ind_HR) %>% bold_p(t = .05)
tbl10 <-
  coxph(Surv(time = adipose_data$os_time,
         event = adipose_data$os_event) ~ total_fat_area_HR + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = total_fat_area_HR) %>% bold_p(t = .05)
tbl11 <-
  coxph(Surv(time = adipose_data$os_time,
         event = adipose_data$os_event) ~ total_fat_area_ind_HR + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = total_fat_area_ind_HR) %>% bold_p(t = .05)
tbl12 <-
  coxph(Surv(time = adipose_data$os_time,
         event = adipose_data$os_event) ~ muscle_mean_hu_HR + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = muscle_mean_hu_HR) %>% bold_p(t = .05)
tbl13 <-
  coxph(Surv(time = adipose_data$os_time,
         event = adipose_data$os_event) ~ v_s_ratio_HR + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = v_s_ratio_HR) %>% bold_p(t = .05)
tbl14 <-
  coxph(Surv(time = adipose_data$os_time,
         event = adipose_data$os_event) ~ v_s_ratio_HR + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + ascites,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 label = list(v_s_ratio_HR ~ "V/S adjusted by ascites"),
                 include = v_s_ratio_HR) %>% bold_p(t = .05)

tbl2 <- tbl_stack(list(tbl2, tbl3, tbl4, tbl5,
               tbl6, tbl7, tbl8, tbl9, tbl10,
               tbl11, tbl12, tbl13, tbl14))

tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))
```
Adjusted for ascites
```{r}
coxph(Surv(time = adipose_data$os_time,
         event = adipose_data$os_event) ~ vat_area_cm2_HR + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + ascites,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = vat_area_cm2_HR) %>% bold_p(t = .05)
coxph(Surv(time = adipose_data$os_time,
         event = adipose_data$os_event) ~ vat_area_cm2_ind_HR + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + ascites,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = vat_area_cm2_ind_HR) %>% bold_p(t = .05)
```
Difficulty to decide if indexed data is better -> Will create groups.  
<br>

***

<br>

## Visualize tertile and cluster on survival
### OS
<div class = "row">
<div class = "col-md-6">
```{r, fig.height = 8}
surv_model <-
  survfit(Surv(time = os_time, event = os_event) ~ tert_muscle_area_cm2, data = adipose_data)
ggsurvplot(surv_model, data = adipose_data,
           title = "Overall Survival analysis",
           font.main = c(22, "bold", "black"),
           font.x = c(20, "bold", "black"),
           font.y = c(20, "bold", "black"),
           font.legend = c(20, "black"),
           font.tickslab = c(18, "bold", "black"),
           size = 1.5,
           
           xlab = "Time (months)", legend.title = "", 
           pval = TRUE,
           conf.int = FALSE,
           tables.height = 0.25,
           risk.table.title = "Risk table",
           risk.table = TRUE,
           risk.table.y.text = FALSE,
           risk.table.fontsize = 4,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(14, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(14, "bold", "black"))
) + guides(colour = guide_legend(ncol = 1))

surv_model <-
  survfit(Surv(time = os_time, event = os_event) ~ tert_muscle_area_cm2_ind, data = adipose_data)
ggsurvplot(surv_model, data = adipose_data,
           title = "Overall Survival analysis",
           font.main = c(22, "bold", "black"),
           font.x = c(20, "bold", "black"),
           font.y = c(20, "bold", "black"),
           font.legend = c(20, "black"),
           font.tickslab = c(18, "bold", "black"),
           size = 1.5,
           
           xlab = "Time (months)", legend.title = "", 
           pval = TRUE,
           conf.int = FALSE,
           tables.height = 0.25,
           risk.table.title = "Risk table",
           risk.table = TRUE,
           risk.table.y.text = FALSE,
           risk.table.fontsize = 4,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(14, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(14, "bold", "black"))
) + guides(colour = guide_legend(ncol = 1))

surv_model <-
  survfit(Surv(time = os_time, event = os_event) ~ tert_imat_area_cm2, data = adipose_data)
ggsurvplot(surv_model, data = adipose_data,
           title = "Overall Survival analysis",
           font.main = c(22, "bold", "black"),
           font.x = c(20, "bold", "black"),
           font.y = c(20, "bold", "black"),
           font.legend = c(20, "black"),
           font.tickslab = c(18, "bold", "black"),
           size = 1.5,
           
           xlab = "Time (months)", legend.title = "", 
           pval = TRUE,
           conf.int = FALSE,
           tables.height = 0.25,
           risk.table.title = "Risk table",
           risk.table = TRUE,
           risk.table.y.text = FALSE,
           risk.table.fontsize = 4,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(14, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(14, "bold", "black"))
) + guides(colour = guide_legend(ncol = 1))

surv_model <-
  survfit(Surv(time = os_time, event = os_event) ~ tert_imat_area_cm2_ind, data = adipose_data)
ggsurvplot(surv_model, data = adipose_data,
           title = "Overall Survival analysis",
           font.main = c(22, "bold", "black"),
           font.x = c(20, "bold", "black"),
           font.y = c(20, "bold", "black"),
           font.legend = c(20, "black"),
           font.tickslab = c(18, "bold", "black"),
           size = 1.5,
           
           xlab = "Time (months)", legend.title = "", 
           pval = TRUE,
           conf.int = FALSE,
           tables.height = 0.25,
           risk.table.title = "Risk table",
           risk.table = TRUE,
           risk.table.y.text = FALSE,
           risk.table.fontsize = 4,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(14, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(14, "bold", "black"))
) + guides(colour = guide_legend(ncol = 1))

surv_model <-
  survfit(Surv(time = os_time, event = os_event) ~ tert_vat_area_cm2, data = adipose_data)
ggsurvplot(surv_model, data = adipose_data,
           title = "Overall Survival analysis",
           font.main = c(22, "bold", "black"),
           font.x = c(20, "bold", "black"),
           font.y = c(20, "bold", "black"),
           font.legend = c(20, "black"),
           font.tickslab = c(18, "bold", "black"),
           size = 1.5,
           
           xlab = "Time (months)", legend.title = "", 
           pval = TRUE,
           conf.int = FALSE,
           tables.height = 0.25,
           risk.table.title = "Risk table",
           risk.table = TRUE,
           risk.table.y.text = FALSE,
           risk.table.fontsize = 4,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(14, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(14, "bold", "black"))
) + guides(colour = guide_legend(ncol = 1))

surv_model <-
  survfit(Surv(time = os_time, event = os_event) ~ tert_vat_area_cm2_ind, data = adipose_data)
ggsurvplot(surv_model, data = adipose_data,
           title = "Overall Survival analysis",
           font.main = c(22, "bold", "black"),
           font.x = c(20, "bold", "black"),
           font.y = c(20, "bold", "black"),
           font.legend = c(20, "black"),
           font.tickslab = c(18, "bold", "black"),
           size = 1.5,
           
           xlab = "Time (months)", legend.title = "", 
           pval = TRUE,
           conf.int = FALSE,
           tables.height = 0.25,
           risk.table.title = "Risk table",
           risk.table = TRUE,
           risk.table.y.text = FALSE,
           risk.table.fontsize = 4,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(14, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(14, "bold", "black"))
) + guides(colour = guide_legend(ncol = 1))

surv_model <-
  survfit(Surv(time = os_time, event = os_event) ~ tert_sat_area_cm2, data = adipose_data)
ggsurvplot(surv_model, data = adipose_data,
           title = "Overall Survival analysis",
           font.main = c(22, "bold", "black"),
           font.x = c(20, "bold", "black"),
           font.y = c(20, "bold", "black"),
           font.legend = c(20, "black"),
           font.tickslab = c(18, "bold", "black"),
           size = 1.5,
           
           xlab = "Time (months)", legend.title = "", 
           pval = TRUE,
           conf.int = FALSE,
           tables.height = 0.25,
           risk.table.title = "Risk table",
           risk.table = TRUE,
           risk.table.y.text = FALSE,
           risk.table.fontsize = 4,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(14, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(14, "bold", "black"))
) + guides(colour = guide_legend(ncol = 1))

surv_model <-
  survfit(Surv(time = os_time, event = os_event) ~ tert_sat_area_cm2_ind, data = adipose_data)
ggsurvplot(surv_model, data = adipose_data,
           title = "Overall Survival analysis",
           font.main = c(22, "bold", "black"),
           font.x = c(20, "bold", "black"),
           font.y = c(20, "bold", "black"),
           font.legend = c(20, "black"),
           font.tickslab = c(18, "bold", "black"),
           size = 1.5,
           
           xlab = "Time (months)", legend.title = "", 
           pval = TRUE,
           conf.int = FALSE,
           tables.height = 0.25,
           risk.table.title = "Risk table",
           risk.table = TRUE,
           risk.table.y.text = FALSE,
           risk.table.fontsize = 4,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(14, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(14, "bold", "black"))
) + guides(colour = guide_legend(ncol = 1))


surv_model <-
  survfit(Surv(time = os_time, event = os_event) ~ tert_total_fat_area, data = adipose_data)
ggsurvplot(surv_model, data = adipose_data,
           title = "Overall Survival analysis",
           font.main = c(22, "bold", "black"),
           font.x = c(20, "bold", "black"),
           font.y = c(20, "bold", "black"),
           font.legend = c(20, "black"),
           font.tickslab = c(18, "bold", "black"),
           size = 1.5,
           
           xlab = "Time (months)", legend.title = "", 
           pval = TRUE,
           conf.int = FALSE,
           tables.height = 0.25,
           risk.table.title = "Risk table",
           risk.table = TRUE,
           risk.table.y.text = FALSE,
           risk.table.fontsize = 4,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(14, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(14, "bold", "black"))
) + guides(colour = guide_legend(ncol = 1))

surv_model <-
  survfit(Surv(time = os_time, event = os_event) ~ tert_total_fat_area_ind, data = adipose_data)
ggsurvplot(surv_model, data = adipose_data,
           title = "Overall Survival analysis",
           font.main = c(22, "bold", "black"),
           font.x = c(20, "bold", "black"),
           font.y = c(20, "bold", "black"),
           font.legend = c(20, "black"),
           font.tickslab = c(18, "bold", "black"),
           size = 1.5,
           
           xlab = "Time (months)", legend.title = "", 
           pval = TRUE,
           conf.int = FALSE,
           tables.height = 0.25,
           risk.table.title = "Risk table",
           risk.table = TRUE,
           risk.table.y.text = FALSE,
           risk.table.fontsize = 4,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(14, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(14, "bold", "black"))
) + guides(colour = guide_legend(ncol = 1))

surv_model <-
  survfit(Surv(time = os_time, event = os_event) ~ tert_muscle_mean_hu, data = adipose_data)
ggsurvplot(surv_model, data = adipose_data,
           title = "Overall Survival analysis",
           font.main = c(22, "bold", "black"),
           font.x = c(20, "bold", "black"),
           font.y = c(20, "bold", "black"),
           font.legend = c(20, "black"),
           font.tickslab = c(18, "bold", "black"),
           size = 1.5,
           
           xlab = "Time (months)", legend.title = "", 
           pval = TRUE,
           conf.int = FALSE,
           tables.height = 0.25,
           risk.table.title = "Risk table",
           risk.table = TRUE,
           risk.table.y.text = FALSE,
           risk.table.fontsize = 4,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(14, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(14, "bold", "black"))
) + guides(colour = guide_legend(ncol = 1))

surv_model <-
  survfit(Surv(time = os_time, event = os_event) ~ tert_imat_mean_hu, data = adipose_data)
ggsurvplot(surv_model, data = adipose_data,
           title = "Overall Survival analysis",
           font.main = c(22, "bold", "black"),
           font.x = c(20, "bold", "black"),
           font.y = c(20, "bold", "black"),
           font.legend = c(20, "black"),
           font.tickslab = c(18, "bold", "black"),
           size = 1.5,
           
           xlab = "Time (months)", legend.title = "", 
           pval = TRUE,
           conf.int = FALSE,
           tables.height = 0.25,
           risk.table.title = "Risk table",
           risk.table = TRUE,
           risk.table.y.text = FALSE,
           risk.table.fontsize = 4,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(14, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(14, "bold", "black"))
) + guides(colour = guide_legend(ncol = 1))

surv_model <-
  survfit(Surv(time = os_time, event = os_event) ~ tert_muscle_hu_sd, data = adipose_data)
ggsurvplot(surv_model, data = adipose_data,
           title = "Overall Survival analysis",
           font.main = c(22, "bold", "black"),
           font.x = c(20, "bold", "black"),
           font.y = c(20, "bold", "black"),
           font.legend = c(20, "black"),
           font.tickslab = c(18, "bold", "black"),
           size = 1.5,
           
           xlab = "Time (months)", legend.title = "", 
           pval = TRUE,
           conf.int = FALSE,
           tables.height = 0.25,
           risk.table.title = "Risk table",
           risk.table = TRUE,
           risk.table.y.text = FALSE,
           risk.table.fontsize = 4,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(14, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(14, "bold", "black"))
) + guides(colour = guide_legend(ncol = 1))

surv_model <-
  survfit(Surv(time = os_time, event = os_event) ~ tert_v_s_ratio, data = adipose_data)
ggsurvplot(surv_model, data = adipose_data,
           title = "Overall Survival analysis",
           font.main = c(22, "bold", "black"),
           font.x = c(20, "bold", "black"),
           font.y = c(20, "bold", "black"),
           font.legend = c(20, "black"),
           font.tickslab = c(18, "bold", "black"),
           size = 1.5,
           
           xlab = "Time (months)", legend.title = "", 
           pval = TRUE,
           conf.int = FALSE,
           tables.height = 0.25,
           risk.table.title = "Risk table",
           risk.table = TRUE,
           risk.table.y.text = FALSE,
           risk.table.fontsize = 4,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(14, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(14, "bold", "black"))
) + guides(colour = guide_legend(ncol = 1))
```
</div>

<div class = "col-md-6">
```{r, fig.height = 8}
surv_model <-
  survfit(Surv(time = os_time, event = os_event) ~ clusters_muscle_area_cm2, data = adipose_data)
ggsurvplot(surv_model, data = adipose_data,
           title = "Overall Survival analysis",
           font.main = c(22, "bold", "black"),
           font.x = c(20, "bold", "black"),
           font.y = c(20, "bold", "black"),
           font.legend = c(20, "black"),
           font.tickslab = c(18, "bold", "black"),
           size = 1.5,
           
           xlab = "Time (months)", legend.title = "", 
           pval = TRUE,
           conf.int = FALSE,
           tables.height = 0.25,
           risk.table.title = "Risk table",
           risk.table = TRUE,
           risk.table.y.text = FALSE,
           risk.table.fontsize = 4,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(14, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(14, "bold", "black"))
) + guides(colour = guide_legend(ncol = 1))

surv_model <-
  survfit(Surv(time = os_time, event = os_event) ~ clusters_muscle_area_cm2_ind, data = adipose_data)
ggsurvplot(surv_model, data = adipose_data,
           title = "Overall Survival analysis",
           font.main = c(22, "bold", "black"),
           font.x = c(20, "bold", "black"),
           font.y = c(20, "bold", "black"),
           font.legend = c(20, "black"),
           font.tickslab = c(18, "bold", "black"),
           size = 1.5,
           
           xlab = "Time (months)", legend.title = "", 
           pval = TRUE,
           conf.int = FALSE,
           tables.height = 0.25,
           risk.table.title = "Risk table",
           risk.table = TRUE,
           risk.table.y.text = FALSE,
           risk.table.fontsize = 4,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(14, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(14, "bold", "black"))
) + guides(colour = guide_legend(ncol = 1))

surv_model <-
  survfit(Surv(time = os_time, event = os_event) ~ clusters_imat_area_cm2, data = adipose_data)
ggsurvplot(surv_model, data = adipose_data,
           title = "Overall Survival analysis",
           font.main = c(22, "bold", "black"),
           font.x = c(20, "bold", "black"),
           font.y = c(20, "bold", "black"),
           font.legend = c(20, "black"),
           font.tickslab = c(18, "bold", "black"),
           size = 1.5,
           
           xlab = "Time (months)", legend.title = "", 
           pval = TRUE,
           conf.int = FALSE,
           tables.height = 0.25,
           risk.table.title = "Risk table",
           risk.table = TRUE,
           risk.table.y.text = FALSE,
           risk.table.fontsize = 4,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(14, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(14, "bold", "black"))
) + guides(colour = guide_legend(ncol = 1))

surv_model <-
  survfit(Surv(time = os_time, event = os_event) ~ clusters_imat_area_cm2_ind, data = adipose_data)
ggsurvplot(surv_model, data = adipose_data,
           title = "Overall Survival analysis",
           font.main = c(22, "bold", "black"),
           font.x = c(20, "bold", "black"),
           font.y = c(20, "bold", "black"),
           font.legend = c(20, "black"),
           font.tickslab = c(18, "bold", "black"),
           size = 1.5,
           
           xlab = "Time (months)", legend.title = "", 
           pval = TRUE,
           conf.int = FALSE,
           tables.height = 0.25,
           risk.table.title = "Risk table",
           risk.table = TRUE,
           risk.table.y.text = FALSE,
           risk.table.fontsize = 4,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(14, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(14, "bold", "black"))
) + guides(colour = guide_legend(ncol = 1))

surv_model <-
  survfit(Surv(time = os_time, event = os_event) ~ clusters_vat_area_cm2, data = adipose_data)
ggsurvplot(surv_model, data = adipose_data,
           title = "Overall Survival analysis",
           font.main = c(22, "bold", "black"),
           font.x = c(20, "bold", "black"),
           font.y = c(20, "bold", "black"),
           font.legend = c(20, "black"),
           font.tickslab = c(18, "bold", "black"),
           size = 1.5,
           
           xlab = "Time (months)", legend.title = "", 
           pval = TRUE,
           conf.int = FALSE,
           tables.height = 0.25,
           risk.table.title = "Risk table",
           risk.table = TRUE,
           risk.table.y.text = FALSE,
           risk.table.fontsize = 4,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(14, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(14, "bold", "black"))
) + guides(colour = guide_legend(ncol = 1))

surv_model <-
  survfit(Surv(time = os_time, event = os_event) ~ clusters_vat_area_cm2_ind, data = adipose_data)
ggsurvplot(surv_model, data = adipose_data,
           title = "Overall Survival analysis",
           font.main = c(22, "bold", "black"),
           font.x = c(20, "bold", "black"),
           font.y = c(20, "bold", "black"),
           font.legend = c(20, "black"),
           font.tickslab = c(18, "bold", "black"),
           size = 1.5,
           
           xlab = "Time (months)", legend.title = "", 
           pval = TRUE,
           conf.int = FALSE,
           tables.height = 0.25,
           risk.table.title = "Risk table",
           risk.table = TRUE,
           risk.table.y.text = FALSE,
           risk.table.fontsize = 4,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(14, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(14, "bold", "black"))
) + guides(colour = guide_legend(ncol = 1))

surv_model <-
  survfit(Surv(time = os_time, event = os_event) ~ clusters_sat_area_cm2, data = adipose_data)
ggsurvplot(surv_model, data = adipose_data,
           title = "Overall Survival analysis",
           font.main = c(22, "bold", "black"),
           font.x = c(20, "bold", "black"),
           font.y = c(20, "bold", "black"),
           font.legend = c(20, "black"),
           font.tickslab = c(18, "bold", "black"),
           size = 1.5,
           
           xlab = "Time (months)", legend.title = "", 
           pval = TRUE,
           conf.int = FALSE,
           tables.height = 0.25,
           risk.table.title = "Risk table",
           risk.table = TRUE,
           risk.table.y.text = FALSE,
           risk.table.fontsize = 4,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(14, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(14, "bold", "black"))
) + guides(colour = guide_legend(ncol = 1))

surv_model <-
  survfit(Surv(time = os_time, event = os_event) ~ clusters_sat_area_cm2_ind, data = adipose_data)
ggsurvplot(surv_model, data = adipose_data,
           title = "Overall Survival analysis",
           font.main = c(22, "bold", "black"),
           font.x = c(20, "bold", "black"),
           font.y = c(20, "bold", "black"),
           font.legend = c(20, "black"),
           font.tickslab = c(18, "bold", "black"),
           size = 1.5,
           
           xlab = "Time (months)", legend.title = "", 
           pval = TRUE,
           conf.int = FALSE,
           tables.height = 0.25,
           risk.table.title = "Risk table",
           risk.table = TRUE,
           risk.table.y.text = FALSE,
           risk.table.fontsize = 4,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(14, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(14, "bold", "black"))
) + guides(colour = guide_legend(ncol = 1))

surv_model <-
  survfit(Surv(time = os_time, event = os_event) ~ clusters_total_fat_area, data = adipose_data)
ggsurvplot(surv_model, data = adipose_data,
           title = "Overall Survival analysis",
           font.main = c(22, "bold", "black"),
           font.x = c(20, "bold", "black"),
           font.y = c(20, "bold", "black"),
           font.legend = c(20, "black"),
           font.tickslab = c(18, "bold", "black"),
           size = 1.5,
           
           xlab = "Time (months)", legend.title = "", 
           pval = TRUE,
           conf.int = FALSE,
           tables.height = 0.25,
           risk.table.title = "Risk table",
           risk.table = TRUE,
           risk.table.y.text = FALSE,
           risk.table.fontsize = 4,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(14, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(14, "bold", "black"))
) + guides(colour = guide_legend(ncol = 1))

surv_model <-
  survfit(Surv(time = os_time, event = os_event) ~ clusters_total_fat_area_ind, data = adipose_data)
ggsurvplot(surv_model, data = adipose_data,
           title = "Overall Survival analysis",
           font.main = c(22, "bold", "black"),
           font.x = c(20, "bold", "black"),
           font.y = c(20, "bold", "black"),
           font.legend = c(20, "black"),
           font.tickslab = c(18, "bold", "black"),
           size = 1.5,
           
           xlab = "Time (months)", legend.title = "", 
           pval = TRUE,
           conf.int = FALSE,
           tables.height = 0.25,
           risk.table.title = "Risk table",
           risk.table = TRUE,
           risk.table.y.text = FALSE,
           risk.table.fontsize = 4,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(14, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(14, "bold", "black"))
) + guides(colour = guide_legend(ncol = 1))

surv_model <-
  survfit(Surv(time = os_time, event = os_event) ~ clusters_muscle_mean_hu, data = adipose_data)
ggsurvplot(surv_model, data = adipose_data,
           title = "Overall Survival analysis",
           font.main = c(22, "bold", "black"),
           font.x = c(20, "bold", "black"),
           font.y = c(20, "bold", "black"),
           font.legend = c(20, "black"),
           font.tickslab = c(18, "bold", "black"),
           size = 1.5,
           
           xlab = "Time (months)", legend.title = "", 
           pval = TRUE,
           conf.int = FALSE,
           tables.height = 0.25,
           risk.table.title = "Risk table",
           risk.table = TRUE,
           risk.table.y.text = FALSE,
           risk.table.fontsize = 4,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(14, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(14, "bold", "black"))
) + guides(colour = guide_legend(ncol = 1))

surv_model <-
  survfit(Surv(time = os_time, event = os_event) ~ clusters_imat_mean_hu, data = adipose_data)
ggsurvplot(surv_model, data = adipose_data,
           title = "Overall Survival analysis",
           font.main = c(22, "bold", "black"),
           font.x = c(20, "bold", "black"),
           font.y = c(20, "bold", "black"),
           font.legend = c(20, "black"),
           font.tickslab = c(18, "bold", "black"),
           size = 1.5,
           
           xlab = "Time (months)", legend.title = "", 
           pval = TRUE,
           conf.int = FALSE,
           tables.height = 0.25,
           risk.table.title = "Risk table",
           risk.table = TRUE,
           risk.table.y.text = FALSE,
           risk.table.fontsize = 4,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(14, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(14, "bold", "black"))
) + guides(colour = guide_legend(ncol = 1))

surv_model <-
  survfit(Surv(time = os_time, event = os_event) ~ clusters_muscle_hu_sd, data = adipose_data)
ggsurvplot(surv_model, data = adipose_data,
           title = "Overall Survival analysis",
           font.main = c(22, "bold", "black"),
           font.x = c(20, "bold", "black"),
           font.y = c(20, "bold", "black"),
           font.legend = c(20, "black"),
           font.tickslab = c(18, "bold", "black"),
           size = 1.5,
           
           xlab = "Time (months)", legend.title = "", 
           pval = TRUE,
           conf.int = FALSE,
           tables.height = 0.25,
           risk.table.title = "Risk table",
           risk.table = TRUE,
           risk.table.y.text = FALSE,
           risk.table.fontsize = 4,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(14, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(14, "bold", "black"))
) + guides(colour = guide_legend(ncol = 1))

surv_model <-
  survfit(Surv(time = os_time, event = os_event) ~ clusters_v_s_ratio, data = adipose_data)
ggsurvplot(surv_model, data = adipose_data,
           title = "Overall Survival analysis",
           font.main = c(22, "bold", "black"),
           font.x = c(20, "bold", "black"),
           font.y = c(20, "bold", "black"),
           font.legend = c(20, "black"),
           font.tickslab = c(18, "bold", "black"),
           size = 1.5,
           
           xlab = "Time (months)", legend.title = "", 
           pval = TRUE,
           conf.int = FALSE,
           tables.height = 0.25,
           risk.table.title = "Risk table",
           risk.table = TRUE,
           risk.table.y.text = FALSE,
           risk.table.fontsize = 4,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(14, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(14, "bold", "black"))
) + guides(colour = guide_legend(ncol = 1))
```
</div>
</div>

<br>
```{r, fig.height = 8}
surv_model <-
  survfit(Surv(time = os_time, event = os_event) ~ clusters_non_ind, data = adipose_data)
ggsurvplot(surv_model, data = adipose_data,
           title = "Overall Survival analysis",
           font.main = c(20, "bold", "black"),
           font.x = c(18, "bold", "black"),
           font.y = c(18, "bold", "black"),
           font.legend = c(16, "black"),
           font.tickslab = c(16, "bold", "black"),
           size = 1.5,
           xlab = "Time (months)", legend.title = "", 
           pval = TRUE,
           conf.int = FALSE,
           tables.height = 0.25,
           risk.table.title = "Risk table",
           risk.table = TRUE,
           risk.table.y.text = FALSE,
           risk.table.fontsize = 4,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(14, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(14, "bold", "black"))
) + guides(colour = guide_legend(ncol = 1))
```
<br>

## HR for tertiles
### Recurrence
Multivariable anlyses are adjusted by `+ raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage`.  
For visceral features the first table is not adjusted by ascites while the second table is.  
```{r HR tertiles recurrence}
tbl1 <- adipose_data %>% select(rec_event, recurrence_time,
                                tert_muscle_area_cm2, 
                                raceeth1, age_at_diagnosis, tnm_cs_mixed_group_stage) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$recurrence_time,
                             event = adipose_data$rec_event)),
                   exponentiate = TRUE, 
                   include = tert_muscle_area_cm2) %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") %>%
  bold_labels() %>% italicize_levels()
tbl2 <-
  coxph(Surv(time = adipose_data$recurrence_time,
         event = adipose_data$rec_event) ~ tert_muscle_area_cm2 + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_muscle_area_cm2) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

tbl1 <- adipose_data %>% select(rec_event, recurrence_time,
                                tert_muscle_area_cm2_ind, 
                                raceeth1, age_at_diagnosis, tnm_cs_mixed_group_stage) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$recurrence_time,
                             event = adipose_data$rec_event)),
                   exponentiate = TRUE, 
                 include = tert_muscle_area_cm2_ind) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") %>%
  bold_labels() %>% italicize_levels()
tbl2 <-
  coxph(Surv(time = adipose_data$recurrence_time,
         event = adipose_data$rec_event) ~ tert_muscle_area_cm2_ind + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_muscle_area_cm2_ind) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

tbl1 <- adipose_data %>% select(rec_event, recurrence_time,
                                tert_imat_area_cm2, 
                                raceeth1, age_at_diagnosis, tnm_cs_mixed_group_stage) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$recurrence_time,
                             event = adipose_data$rec_event)),
                   exponentiate = TRUE, 
                 include = tert_imat_area_cm2) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") %>%
  bold_labels() %>% italicize_levels()
tbl2 <-
  coxph(Surv(time = adipose_data$recurrence_time,
         event = adipose_data$rec_event) ~ tert_imat_area_cm2 + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_imat_area_cm2) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

tbl1 <- adipose_data %>% select(rec_event, recurrence_time,
                                tert_imat_area_cm2_ind, 
                                raceeth1, age_at_diagnosis, tnm_cs_mixed_group_stage) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$recurrence_time,
                             event = adipose_data$rec_event)),
                   exponentiate = TRUE, 
                 include = tert_imat_area_cm2_ind) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") %>%
  bold_labels() %>% italicize_levels()
tbl2 <-
  coxph(Surv(time = adipose_data$recurrence_time,
         event = adipose_data$rec_event) ~ tert_imat_area_cm2_ind + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_imat_area_cm2_ind) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

tbl1 <- adipose_data %>% select(rec_event, recurrence_time,
                                tert_vat_area_cm2, 
                                raceeth1, age_at_diagnosis, tnm_cs_mixed_group_stage) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$recurrence_time,
                             event = adipose_data$rec_event)),
                   exponentiate = TRUE, 
                 include = tert_vat_area_cm2) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") %>%
  bold_labels() %>% italicize_levels()
tbl2 <-
  coxph(Surv(time = adipose_data$recurrence_time,
         event = adipose_data$rec_event) ~ tert_vat_area_cm2 + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_vat_area_cm2) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

tbl1 <- adipose_data %>% select(rec_event, recurrence_time,
                                tert_vat_area_cm2, 
                                raceeth1, age_at_diagnosis, tnm_cs_mixed_group_stage, 
                                ascites) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$recurrence_time,
                             event = adipose_data$rec_event)),
                   exponentiate = TRUE, 
                 include = tert_vat_area_cm2) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") %>%
  bold_labels() %>% italicize_levels()
tbl2 <-
  coxph(Surv(time = adipose_data$recurrence_time,
         event = adipose_data$rec_event) ~ tert_vat_area_cm2 + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + ascites,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_vat_area_cm2) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

tbl1 <- adipose_data %>% select(rec_event, recurrence_time,
                                tert_vat_area_cm2_ind, 
                                raceeth1, age_at_diagnosis, tnm_cs_mixed_group_stage) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$recurrence_time,
                             event = adipose_data$rec_event)),
                   exponentiate = TRUE, 
                 include = tert_vat_area_cm2_ind) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") %>%
  bold_labels() %>% italicize_levels()
tbl2 <-
  coxph(Surv(time = adipose_data$recurrence_time,
         event = adipose_data$rec_event) ~ tert_vat_area_cm2_ind + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_vat_area_cm2_ind) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))


tbl1 <- adipose_data %>% select(rec_event, recurrence_time,
                                tert_vat_area_cm2_ind, 
                                raceeth1, age_at_diagnosis, tnm_cs_mixed_group_stage, 
                                ascites) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$recurrence_time,
                             event = adipose_data$rec_event)),
                   exponentiate = TRUE, 
                 include = tert_vat_area_cm2_ind) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") %>%
  bold_labels() %>% italicize_levels()
tbl2 <-
  coxph(Surv(time = adipose_data$recurrence_time,
         event = adipose_data$rec_event) ~ tert_vat_area_cm2_ind + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + ascites,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_vat_area_cm2_ind) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

tbl1 <- adipose_data %>% select(rec_event, recurrence_time,
                                tert_sat_area_cm2, 
                                raceeth1, age_at_diagnosis, tnm_cs_mixed_group_stage) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$recurrence_time,
                             event = adipose_data$rec_event)),
                   exponentiate = TRUE, 
                 include = tert_sat_area_cm2) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") %>%
  bold_labels() %>% italicize_levels()
tbl2 <-
  coxph(Surv(time = adipose_data$recurrence_time,
         event = adipose_data$rec_event) ~ tert_sat_area_cm2 + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_sat_area_cm2) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

tbl1 <- adipose_data %>% select(rec_event, recurrence_time,
                                tert_sat_area_cm2_ind, 
                                raceeth1, age_at_diagnosis, tnm_cs_mixed_group_stage) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$recurrence_time,
                             event = adipose_data$rec_event)),
                   exponentiate = TRUE, 
                 include = tert_sat_area_cm2_ind) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") %>%
  bold_labels() %>% italicize_levels()
tbl2 <-
  coxph(Surv(time = adipose_data$recurrence_time,
         event = adipose_data$rec_event) ~ tert_sat_area_cm2_ind + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_sat_area_cm2_ind) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

tbl1 <- adipose_data %>% select(rec_event, recurrence_time,
                                tert_total_fat_area, 
                                raceeth1, age_at_diagnosis, tnm_cs_mixed_group_stage) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$recurrence_time,
                             event = adipose_data$rec_event)),
                   exponentiate = TRUE, 
                 include = tert_total_fat_area) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") %>%
  bold_labels() %>% italicize_levels()
tbl2 <-
  coxph(Surv(time = adipose_data$recurrence_time,
         event = adipose_data$rec_event) ~ tert_total_fat_area + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_total_fat_area) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

tbl1 <- adipose_data %>% select(rec_event, recurrence_time,
                                tert_total_fat_area_ind, 
                                raceeth1, age_at_diagnosis, tnm_cs_mixed_group_stage) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$recurrence_time,
                             event = adipose_data$rec_event)),
                   exponentiate = TRUE, 
                 include = tert_total_fat_area_ind) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") %>%
  bold_labels() %>% italicize_levels()
tbl2 <-
  coxph(Surv(time = adipose_data$recurrence_time,
         event = adipose_data$rec_event) ~ tert_total_fat_area_ind + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_total_fat_area_ind) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

tbl1 <- adipose_data %>% select(rec_event, recurrence_time,
                                tert_muscle_mean_hu, 
                                raceeth1, age_at_diagnosis, tnm_cs_mixed_group_stage) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$recurrence_time,
                             event = adipose_data$rec_event)),
                   exponentiate = TRUE, 
                 include = tert_muscle_mean_hu) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") %>%
  bold_labels() %>% italicize_levels()
tbl2 <-
  coxph(Surv(time = adipose_data$recurrence_time,
         event = adipose_data$rec_event) ~ tert_muscle_mean_hu + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_muscle_mean_hu) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

tbl1 <- adipose_data %>% select(rec_event, recurrence_time,
                                tert_imat_mean_hu, 
                                raceeth1, age_at_diagnosis, tnm_cs_mixed_group_stage) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$recurrence_time,
                             event = adipose_data$rec_event)),
                   exponentiate = TRUE, 
                 include = tert_imat_mean_hu) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") %>%
  bold_labels() %>% italicize_levels()
tbl2 <-
  coxph(Surv(time = adipose_data$recurrence_time,
         event = adipose_data$rec_event) ~ tert_imat_mean_hu + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_imat_mean_hu) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

tbl1 <- adipose_data %>% select(rec_event, recurrence_time,
                                tert_muscle_hu_sd, 
                                raceeth1, age_at_diagnosis, tnm_cs_mixed_group_stage) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$recurrence_time,
                             event = adipose_data$rec_event)),
                   exponentiate = TRUE, 
                 include = tert_muscle_hu_sd) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") %>%
  bold_labels() %>% italicize_levels()
tbl2 <-
  coxph(Surv(time = adipose_data$recurrence_time,
         event = adipose_data$rec_event) ~ tert_muscle_hu_sd + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_muscle_hu_sd) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

tbl1 <- adipose_data %>% select(rec_event, recurrence_time,
                                tert_v_s_ratio, 
                                raceeth1, age_at_diagnosis, tnm_cs_mixed_group_stage) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$recurrence_time,
                             event = adipose_data$rec_event)),
                   exponentiate = TRUE, 
                 include = tert_v_s_ratio) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") %>%
  bold_labels() %>% italicize_levels()
tbl2 <-
  coxph(Surv(time = adipose_data$recurrence_time,
         event = adipose_data$rec_event) ~ tert_v_s_ratio + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_v_s_ratio) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

tbl1 <- adipose_data %>% select(rec_event, recurrence_time,
                                tert_v_s_ratio, 
                                raceeth1, age_at_diagnosis, tnm_cs_mixed_group_stage, 
                                ascites) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$recurrence_time,
                             event = adipose_data$rec_event)),
                   exponentiate = TRUE, 
                 include = tert_v_s_ratio) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") %>%
  bold_labels() %>% italicize_levels()
tbl2 <-
  coxph(Surv(time = adipose_data$recurrence_time,
         event = adipose_data$rec_event) ~ tert_v_s_ratio + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + ascites,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_v_s_ratio) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))
```

### OS
```{r HR tertiles os}
tbl1 <- adipose_data %>% select(os_event, os_time,
                                tert_muscle_area_cm2, 
                                raceeth1, age_at_diagnosis, tnm_cs_mixed_group_stage) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$os_time,
                             event = adipose_data$os_event)),
                   exponentiate = TRUE, 
                 include = tert_muscle_area_cm2) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") %>%
  bold_labels() %>% italicize_levels()
tbl2 <-
  coxph(Surv(time = adipose_data$os_time,
         event = adipose_data$os_event) ~ tert_muscle_area_cm2 + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_muscle_area_cm2) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

tbl1 <- adipose_data %>% select(os_event, os_time,
                                tert_muscle_area_cm2_ind, 
                                raceeth1, age_at_diagnosis, tnm_cs_mixed_group_stage) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$os_time,
                             event = adipose_data$os_event)),
                   exponentiate = TRUE, 
                 include = tert_muscle_area_cm2_ind) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") %>%
  bold_labels() %>% italicize_levels()
tbl2 <-
  coxph(Surv(time = adipose_data$os_time,
         event = adipose_data$os_event) ~ tert_muscle_area_cm2_ind + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_muscle_area_cm2_ind) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

tbl1 <- adipose_data %>% select(os_event, os_time,
                                tert_imat_area_cm2, 
                                raceeth1, age_at_diagnosis, tnm_cs_mixed_group_stage) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$os_time,
                             event = adipose_data$os_event)),
                   exponentiate = TRUE, 
                 include = tert_imat_area_cm2) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") %>%
  bold_labels() %>% italicize_levels()
tbl2 <-
  coxph(Surv(time = adipose_data$os_time,
         event = adipose_data$os_event) ~ tert_imat_area_cm2 + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_imat_area_cm2) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

tbl1 <- adipose_data %>% select(os_event, os_time,
                                tert_imat_area_cm2_ind, 
                                raceeth1, age_at_diagnosis, tnm_cs_mixed_group_stage) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$os_time,
                             event = adipose_data$os_event)),
                   exponentiate = TRUE, 
                 include = tert_imat_area_cm2_ind) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") %>%
  bold_labels() %>% italicize_levels()
tbl2 <-
  coxph(Surv(time = adipose_data$os_time,
         event = adipose_data$os_event) ~ tert_imat_area_cm2_ind + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_imat_area_cm2_ind) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

tbl1 <- adipose_data %>% select(os_event, os_time,
                                tert_vat_area_cm2, 
                                raceeth1, age_at_diagnosis, tnm_cs_mixed_group_stage) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$os_time,
                             event = adipose_data$os_event)),
                   exponentiate = TRUE, 
                 include = tert_vat_area_cm2) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") %>%
  bold_labels() %>% italicize_levels()
tbl2 <-
  coxph(Surv(time = adipose_data$os_time,
         event = adipose_data$os_event) ~ tert_vat_area_cm2 + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_vat_area_cm2) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

tbl1 <- adipose_data %>% select(os_event, os_time,
                                tert_vat_area_cm2, 
                                raceeth1, age_at_diagnosis, tnm_cs_mixed_group_stage, 
                                ascites) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$os_time,
                             event = adipose_data$os_event)),
                   exponentiate = TRUE, 
                 include = tert_vat_area_cm2) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") %>%
  bold_labels() %>% italicize_levels()
tbl2 <-
  coxph(Surv(time = adipose_data$os_time,
         event = adipose_data$os_event) ~ tert_vat_area_cm2 + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + ascites,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_vat_area_cm2) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

tbl1 <- adipose_data %>% select(os_event, os_time,
                                tert_vat_area_cm2_ind, 
                                raceeth1, age_at_diagnosis, tnm_cs_mixed_group_stage) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$os_time,
                             event = adipose_data$os_event)),
                   exponentiate = TRUE, 
                 include = tert_vat_area_cm2_ind) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") %>%
  bold_labels() %>% italicize_levels()
tbl2 <-
  coxph(Surv(time = adipose_data$os_time,
         event = adipose_data$os_event) ~ tert_vat_area_cm2_ind + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_vat_area_cm2_ind) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

tbl1 <- adipose_data %>% select(os_event, os_time,
                                tert_vat_area_cm2_ind, 
                                raceeth1, age_at_diagnosis, tnm_cs_mixed_group_stage, 
                                ascites) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$os_time,
                             event = adipose_data$os_event)),
                   exponentiate = TRUE, 
                 include = tert_vat_area_cm2_ind) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") %>%
  bold_labels() %>% italicize_levels()
tbl2 <-
  coxph(Surv(time = adipose_data$os_time,
         event = adipose_data$os_event) ~ tert_vat_area_cm2_ind + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + ascites,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_vat_area_cm2_ind) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

tbl1 <- adipose_data %>% select(os_event, os_time,
                                tert_sat_area_cm2, 
                                raceeth1, age_at_diagnosis, tnm_cs_mixed_group_stage) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$os_time,
                             event = adipose_data$os_event)),
                   exponentiate = TRUE, 
                 include = tert_sat_area_cm2) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") %>%
  bold_labels() %>% italicize_levels()
tbl2 <-
  coxph(Surv(time = adipose_data$os_time,
         event = adipose_data$os_event) ~ tert_sat_area_cm2 + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_sat_area_cm2) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

tbl1 <- adipose_data %>% select(os_event, os_time,
                                tert_sat_area_cm2_ind, 
                                raceeth1, age_at_diagnosis, tnm_cs_mixed_group_stage) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$os_time,
                             event = adipose_data$os_event)),
                   exponentiate = TRUE, 
                 include = tert_sat_area_cm2_ind) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") %>%
  bold_labels() %>% italicize_levels()
tbl2 <-
  coxph(Surv(time = adipose_data$os_time,
         event = adipose_data$os_event) ~ tert_sat_area_cm2_ind + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_sat_area_cm2_ind) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

tbl1 <- adipose_data %>% select(os_event, os_time,
                                tert_total_fat_area, 
                                raceeth1, age_at_diagnosis, tnm_cs_mixed_group_stage) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$os_time,
                             event = adipose_data$os_event)),
                   exponentiate = TRUE, 
                 include = tert_total_fat_area) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") %>%
  bold_labels() %>% italicize_levels()
tbl2 <-
  coxph(Surv(time = adipose_data$os_time,
         event = adipose_data$os_event) ~ tert_total_fat_area + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_total_fat_area) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

tbl1 <- adipose_data %>% select(os_event, os_time,
                                tert_total_fat_area_ind, 
                                raceeth1, age_at_diagnosis, tnm_cs_mixed_group_stage) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$os_time,
                             event = adipose_data$os_event)),
                   exponentiate = TRUE, 
                 include = tert_total_fat_area_ind) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") %>%
  bold_labels() %>% italicize_levels()
tbl2 <-
  coxph(Surv(time = adipose_data$os_time,
         event = adipose_data$os_event) ~ tert_total_fat_area_ind + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_total_fat_area_ind) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

tbl1 <- adipose_data %>% select(os_event, os_time,
                                tert_muscle_mean_hu, 
                                raceeth1, age_at_diagnosis, tnm_cs_mixed_group_stage) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$os_time,
                             event = adipose_data$os_event)),
                   exponentiate = TRUE, 
                 include = tert_muscle_mean_hu) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") %>%
  bold_labels() %>% italicize_levels()
tbl2 <-
  coxph(Surv(time = adipose_data$os_time,
         event = adipose_data$os_event) ~ tert_muscle_mean_hu + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_muscle_mean_hu) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

tbl1 <- adipose_data %>% select(os_event, os_time,
                                tert_imat_mean_hu, 
                                raceeth1, age_at_diagnosis, tnm_cs_mixed_group_stage) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$os_time,
                             event = adipose_data$os_event)),
                   exponentiate = TRUE, 
                 include = tert_imat_mean_hu) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") %>%
  bold_labels() %>% italicize_levels()
tbl2 <-
  coxph(Surv(time = adipose_data$os_time,
         event = adipose_data$os_event) ~ tert_imat_mean_hu + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_imat_mean_hu) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

tbl1 <- adipose_data %>% select(os_event, os_time,
                                tert_muscle_hu_sd, 
                                raceeth1, age_at_diagnosis, tnm_cs_mixed_group_stage) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$os_time,
                             event = adipose_data$os_event)),
                   exponentiate = TRUE, 
                 include = tert_muscle_hu_sd) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") %>%
  bold_labels() %>% italicize_levels()
tbl2 <-
  coxph(Surv(time = adipose_data$os_time,
         event = adipose_data$os_event) ~ tert_muscle_hu_sd + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_muscle_hu_sd) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

tbl1 <- adipose_data %>% select(os_event, os_time,
                                tert_v_s_ratio, 
                                raceeth1, age_at_diagnosis, tnm_cs_mixed_group_stage) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$os_time,
                             event = adipose_data$os_event)),
                   exponentiate = TRUE, 
                 include = tert_v_s_ratio) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") %>%
  bold_labels() %>% italicize_levels()
tbl2 <-
  coxph(Surv(time = adipose_data$os_time,
         event = adipose_data$os_event) ~ tert_v_s_ratio + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_v_s_ratio) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

tbl1 <- adipose_data %>% select(os_event, os_time,
                                tert_v_s_ratio, 
                                raceeth1, age_at_diagnosis, tnm_cs_mixed_group_stage, 
                                ascites) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = adipose_data$os_time,
                             event = adipose_data$os_event)),
                   exponentiate = TRUE, 
                 include = tert_v_s_ratio) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") %>%
  bold_labels() %>% italicize_levels()
tbl2 <-
  coxph(Surv(time = adipose_data$os_time,
         event = adipose_data$os_event) ~ tert_v_s_ratio + raceeth1 + age_at_diagnosis + tnm_cs_mixed_group_stage + ascites,
    data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_v_s_ratio) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))
```

















