---
title: "Preliminary analysis R01 Resubmission"
author: "Christelle Colin-Leitzinger"
date: '`r Sys.Date()`'
output: 
  html_document:
    toc: true
    toc_float: true
    toc_collapsed: false
    theme: united
    highlight: pygments
    df_print: paged
editor_options: 
  chunk_output_type: console
---

<style type="text/css">

.figure {
   margin-top: 25px;
   margin-bottom: 100px;
}

table {
    margin-top: 10px;
    margin-bottom: 25px;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE,
                      cache = FALSE,
                      fig.align='center'
                      )
```

```{r library}
library(tidyverse)
library(ggplot2)
library(gtsummary)
library(survival)
library(survminer)
theme_gtsummary_compact()
theme_set(theme_classic())
```

```{r load}
adipose_data <- read_rds(paste0(here::here(), "/adipose_data.rds")) %>% 
  mutate(id = as.character(id)) %>% 
  mutate(pfs_event = case_when(
    vital_new == "Dead"                      ~ 1,
    TRUE                                     ~ rec_event
  )) %>% 
  mutate(pfs_time = recurrence_time)
roswell_data <- read_rds(paste0(here::here(), "/roswell_data.rds"))
```

```{r cleaning}
full_data <- bind_rows(adipose_data %>% mutate(study = "Moffitt"),
                       roswell_data %>% mutate(study = "Roswell"))
```

```{r tertile}
full_data <- full_data %>% 
  mutate(tnm_cs_mixed_group_stage = case_when(
    tnm_cs_mixed_group_stage == "I-II"                  ~ "I-II",
    tnm_cs_mixed_group_stage == "III" |
      tnm_cs_mixed_group_stage == "IV"                  ~ "III-IV",
    TRUE                                                ~ "III-IV"
  )) %>% 
  mutate(tertile = ntile(imat_area_cm2, 3)) %>% 
  mutate(tert_imat_area_cm2 = case_when(
    tertile == 1 ~ "Low",
    tertile == 2 ~ "Medium",
    tertile == 3 ~ "High",
  )) %>% 
  
  mutate(tertile = ntile(vat_area_cm2, 3)) %>% 
  mutate(tert_vat_area_cm2 = case_when(
    tertile == 1 ~ "Low",
    tertile == 2 ~ "Medium",
    tertile == 3 ~ "High",
  )) %>% 
  
  mutate(tertile = ntile(sat_area_cm2, 3)) %>% 
  mutate(tert_sat_area_cm2 = case_when(
    tertile == 1 ~ "Low",
    tertile == 2 ~ "Medium",
    tertile == 3 ~ "High",
  )) %>% 
  
  mutate(tertile = ntile(total_fat_area, 3)) %>% 
  mutate(tert_total_fat_area = case_when(
    tertile == 1 ~ "Low",
    tertile == 2 ~ "Medium",
    tertile == 3 ~ "High",
  )) %>% 
  select(-tertile) %>% 
  mutate(across(starts_with("tert_"), ~ factor(., levels = c("Low", "Medium", "High"))))
```
# 1. Tables 1. Patient characteristics and body composition depots overall, by study and by treatment type (neo vs. debulking) 
## overall
```{r}
full_data %>% 
  select(age_at_diagnosis, 
         bmi, bmi_cat,
         treatment_type, 
         tnm_cs_mixed_group_stage, 
         os_event, os_time,
         pfs_event, pfs_time,
         sat_area_cm2, imat_area_cm2, 
         vat_area_cm2, total_fat_area,
         starts_with("tert_")) %>% 
  tbl_summary(
    type = list(all_dichotomous() ~ "categorical"), 
            statistic=list(all_continuous() ~ "{mean} ({sd})"), 
            digits = all_continuous() ~ 1
    ) %>%  
  bold_labels() %>% add_stat_label() %>% 
  modify_footnote(update = everything() ~ NA)
```

## by study
```{r}
full_data %>% 
  select(age_at_diagnosis, study,
         bmi, bmi_cat,
         treatment_type, 
         tnm_cs_mixed_group_stage, 
         os_event, os_time,
         pfs_event, pfs_time,
         sat_area_cm2, imat_area_cm2, 
         vat_area_cm2, total_fat_area,
         starts_with("tert_")) %>% 
  tbl_summary(by = study,
    type = list(all_dichotomous() ~ "categorical"), 
            statistic=list(all_continuous() ~ "{mean} ({sd})"), 
            digits = all_continuous() ~ 1
    ) %>%  
  bold_labels() %>% add_stat_label() %>% 
  add_p() %>% bold_p(t = .05) %>% 
  modify_footnote(update = everything() ~ NA)
```

## by treatment type
```{r}
full_data %>% 
  select(age_at_diagnosis, 
         bmi, bmi_cat,
         treatment_type, 
         tnm_cs_mixed_group_stage, 
         os_event, os_time,
         pfs_event, pfs_time,
         sat_area_cm2, imat_area_cm2, 
         vat_area_cm2, total_fat_area,
         starts_with("tert_")) %>% 
  tbl_summary(by = treatment_type,
    type = list(all_dichotomous() ~ "categorical"), 
            statistic=list(all_continuous() ~ "{mean} ({sd})"), 
            digits = all_continuous() ~ 1
    ) %>%  
  bold_labels() %>% add_stat_label() %>% 
  add_p() %>% bold_p(t = .05) %>% 
  modify_footnote(update = everything() ~ NA)
```

## Plots 
```{r, fig.width= 12, fig.height= 12}
full_data %>% 
  select(mrn, bmi_cat,
         imat_area_cm2,
         vat_area_cm2,
         sat_area_cm2,
         total_fat_area) %>% 
  rename(c("IMAT" = imat_area_cm2,
           "VAT" = vat_area_cm2,
           "SAT" = sat_area_cm2,
           "TAT" = total_fat_area)) %>% 
  pivot_longer(-c(mrn, bmi_cat)) %>% 
  mutate(name = factor(name,
                       levels = c(
                         "IMAT",
                         "VAT",
                         "SAT",
                         "TAT"
                       ))) %>%
  filter(!is.na(bmi_cat)) %>% 
  ggplot(aes(x= bmi_cat, y= value, color = bmi_cat))+
  geom_boxplot()+
  labs(x= NULL, y= "Body Composition Depot",
       color= "Imputed BMI category")+
  scale_color_viridis_d(option = "G", end = c(0.8))+
  theme_classic()+ 
  theme(legend.position="bottom")+
  coord_flip()+
  facet_wrap(.~ name, scales = "free_x", ncol = 2)

full_data %>% 
  select(mrn, study,
         imat_area_cm2,
         vat_area_cm2,
         sat_area_cm2,
         total_fat_area) %>% 
  rename(c("IMAT" = imat_area_cm2,
           "VAT" = vat_area_cm2,
           "SAT" = sat_area_cm2,
           "TAT" = total_fat_area)) %>% 
  pivot_longer(-c(mrn, study)) %>% 
  mutate(name = factor(name,
                       levels = c(
                         "IMAT",
                         "VAT",
                         "SAT",
                         "TAT"
                       ))) %>%
  ggplot(aes(x= study, y= value, color = study))+
  geom_boxplot()+
  labs(x= NULL, y= "Body Composition Depot",
       color= "")+
  scale_color_viridis_d(option = "A",begin = c(0.2), end = c(0.8))+
  theme_classic()+ 
  theme(legend.position="bottom")+
  coord_flip()+
  facet_wrap(.~ name, scales = "free_x", ncol = 2)
```
<br>
<br>

# 2. Table 2 – Association of BMI and each body composition depot with PFS overall and by treatment type

Multivariable analyses are adjusted for `+ age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type + study`.  

## Overall
```{r HR tertiles PFS}
tbl1 <- full_data %>% select(pfs_event, pfs_time,
                                bmi_cat) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = full_data$pfs_time,
                             event = full_data$pfs_event)),
                   exponentiate = TRUE) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <-
  coxph(Surv(time = full_data$pfs_time,
             event = full_data$pfs_event) ~ 
          bmi_cat + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type + study,
        data =  full_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = bmi_cat) %>% bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

print("PH assumption")
coxph(Surv(time = full_data$pfs_time,
             event = full_data$pfs_event) ~ bmi_cat + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type + study,
        data =  full_data)  %>% 
  cox.zph()

tbl1 <- full_data %>% select(pfs_event, pfs_time,
                                tert_imat_area_cm2) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = full_data$pfs_time,
                             event = full_data$pfs_event)),
                   exponentiate = TRUE) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <-
  coxph(Surv(time = full_data$pfs_time,
             event = full_data$pfs_event) ~ 
          tert_imat_area_cm2 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type + study,
        data =  full_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_imat_area_cm2) %>% bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

print("PH assumption")
coxph(Surv(time = full_data$pfs_time,
             event = full_data$pfs_event) ~ tert_imat_area_cm2 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type + study,
        data =  full_data)  %>% 
  cox.zph()

tbl1 <- full_data %>% select(pfs_event, pfs_time,
                                tert_vat_area_cm2) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = full_data$pfs_time,
                             event = full_data$pfs_event)),
                   exponentiate = TRUE) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <-
  coxph(Surv(time = full_data$pfs_time,
             event = full_data$pfs_event) ~ 
          tert_vat_area_cm2 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type + study,
        data =  full_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_vat_area_cm2) %>% bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

print("PH assumption")
coxph(Surv(time = full_data$pfs_time,
             event = full_data$pfs_event) ~ tert_vat_area_cm2 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type + study,
        data =  full_data)  %>% 
  cox.zph()

tbl1 <- full_data %>% select(pfs_event, pfs_time,
                                tert_sat_area_cm2) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = full_data$pfs_time,
                             event = full_data$pfs_event)),
                   exponentiate = TRUE) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <-
  coxph(Surv(time = full_data$pfs_time,
             event = full_data$pfs_event) ~ 
          tert_sat_area_cm2 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type + study,
        data =  full_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_sat_area_cm2) %>% bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

print("PH assumption")
coxph(Surv(time = full_data$pfs_time,
             event = full_data$pfs_event) ~ tert_sat_area_cm2 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type + study,
        data =  full_data)  %>% 
  cox.zph()

tbl1 <- full_data %>% select(pfs_event, pfs_time,
                                tert_total_fat_area) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = full_data$pfs_time,
                             event = full_data$pfs_event)),
                   exponentiate = TRUE) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <-
  coxph(Surv(time = full_data$pfs_time,
             event = full_data$pfs_event) ~ 
          tert_total_fat_area + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type + study,
        data =  full_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_total_fat_area) %>% bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

print("PH assumption")
coxph(Surv(time = full_data$pfs_time,
             event = full_data$pfs_event) ~ tert_total_fat_area + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type + study,
        data =  full_data)  %>% 
  cox.zph()
```
<br>
<br>

## By treatment type

```{r Stratified treatment pfs}
full_data_neo <- full_data %>% 
  filter(treatment_type == "Upfront Neoadjuvant")

full_data_surg <- full_data %>% 
  filter(treatment_type == "Upfront Surgery")
```

Multivariable analyses are adjusted for `+ age_at_diagnosis + tnm_cs_mixed_group_stage + study`.  

### Upfront Chemo
```{r}
tbl1 <- full_data_neo %>% select(pfs_event, pfs_time,
                                bmi_cat) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = full_data_neo$pfs_time,
                             event = full_data_neo$pfs_event)),
                   exponentiate = TRUE) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <-
  coxph(Surv(time = full_data_neo$pfs_time,
             event = full_data_neo$pfs_event) ~ 
          bmi_cat + age_at_diagnosis + tnm_cs_mixed_group_stage + study,
        data =  full_data_neo) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = bmi_cat) %>% bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

tbl1 <- full_data_neo %>% select(pfs_event, pfs_time,
                                tert_imat_area_cm2) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = full_data_neo$pfs_time,
                             event = full_data_neo$pfs_event)),
                   exponentiate = TRUE, 
                   include = tert_imat_area_cm2) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <-
  coxph(Surv(time = full_data_neo$pfs_time,
             event = full_data_neo$pfs_event) ~ 
          tert_imat_area_cm2 + age_at_diagnosis + tnm_cs_mixed_group_stage + study,
        data =  full_data_neo) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_imat_area_cm2) %>% bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

tbl1 <- full_data_neo %>% select(pfs_event, pfs_time,
                                tert_vat_area_cm2) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = full_data_neo$pfs_time,
                             event = full_data_neo$pfs_event)),
                   exponentiate = TRUE, 
                   include = tert_vat_area_cm2) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <-
  coxph(Surv(time = full_data_neo$pfs_time,
             event = full_data_neo$pfs_event) ~ 
          tert_vat_area_cm2 + age_at_diagnosis + tnm_cs_mixed_group_stage + study,
        data =  full_data_neo) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_vat_area_cm2) %>% bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

tbl1 <- full_data_neo %>% select(pfs_event, pfs_time,
                                tert_sat_area_cm2) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = full_data_neo$pfs_time,
                             event = full_data_neo$pfs_event)),
                   exponentiate = TRUE, 
                   include = tert_sat_area_cm2) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <-
  coxph(Surv(time = full_data_neo$pfs_time,
             event = full_data_neo$pfs_event) ~ 
          tert_sat_area_cm2 + age_at_diagnosis + tnm_cs_mixed_group_stage + study,
        data =  full_data_neo) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_sat_area_cm2) %>% bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

tbl1 <- full_data_neo %>% select(pfs_event, pfs_time,
                                tert_total_fat_area) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = full_data_neo$pfs_time,
                             event = full_data_neo$pfs_event)),
                   exponentiate = TRUE, 
                   include = tert_total_fat_area) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <-
  coxph(Surv(time = full_data_neo$pfs_time,
             event = full_data_neo$pfs_event) ~ 
          tert_total_fat_area + age_at_diagnosis + tnm_cs_mixed_group_stage + study,
        data =  full_data_neo) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_total_fat_area) %>% bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))
```
<br>
<br>

### Upfront Surgery
```{r}
tbl1 <- full_data_surg %>% select(pfs_event, pfs_time,
                                bmi_cat) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = full_data_surg$pfs_time,
                             event = full_data_surg$pfs_event)),
                   exponentiate = TRUE) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <-
  coxph(Surv(time = full_data_surg$pfs_time,
             event = full_data_surg$pfs_event) ~ 
          bmi_cat + age_at_diagnosis + tnm_cs_mixed_group_stage + study,
        data =  full_data_surg) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = bmi_cat) %>% bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

tbl1 <- full_data_surg %>% select(pfs_event, pfs_time,
                                tert_imat_area_cm2) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = full_data_surg$pfs_time,
                             event = full_data_surg$pfs_event)),
                   exponentiate = TRUE, 
                   include = tert_imat_area_cm2) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <-
  coxph(Surv(time = full_data_surg$pfs_time,
             event = full_data_surg$pfs_event) ~ 
          tert_imat_area_cm2 + age_at_diagnosis + tnm_cs_mixed_group_stage + study,
        data =  full_data_surg) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_imat_area_cm2) %>% bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

tbl1 <- full_data_surg %>% select(pfs_event, pfs_time,
                                tert_vat_area_cm2) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = full_data_surg$pfs_time,
                             event = full_data_surg$pfs_event)),
                   exponentiate = TRUE, 
                   include = tert_vat_area_cm2) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <-
  coxph(Surv(time = full_data_surg$pfs_time,
             event = full_data_surg$pfs_event) ~ 
          tert_vat_area_cm2 + age_at_diagnosis + tnm_cs_mixed_group_stage + study,
        data =  full_data_surg) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_vat_area_cm2) %>% bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

tbl1 <- full_data_surg %>% select(pfs_event, pfs_time,
                                tert_sat_area_cm2) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = full_data_surg$pfs_time,
                             event = full_data_surg$pfs_event)),
                   exponentiate = TRUE, 
                   include = tert_sat_area_cm2) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <-
  coxph(Surv(time = full_data_surg$pfs_time,
             event = full_data_surg$pfs_event) ~ 
          tert_sat_area_cm2 + age_at_diagnosis + tnm_cs_mixed_group_stage + study,
        data =  full_data_surg) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_sat_area_cm2) %>% bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

tbl1 <- full_data_surg %>% select(pfs_event, pfs_time,
                                tert_total_fat_area) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = full_data_surg$pfs_time,
                             event = full_data_surg$pfs_event)),
                   exponentiate = TRUE, 
                   include = tert_total_fat_area) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <-
  coxph(Surv(time = full_data_surg$pfs_time,
             event = full_data_surg$pfs_event) ~ 
          tert_total_fat_area + age_at_diagnosis + tnm_cs_mixed_group_stage + study,
        data =  full_data_surg) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_total_fat_area) %>% bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))
```
<br>
<br>

#	3. Table 3 – Association of BMI and each body composition depot with OS overall and by treatment type

Multivariable analyses are adjusted for `+ age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type + study`.  

## Overall
```{r HR tertiles os}
tbl1 <- full_data %>% select(os_event, os_time,
                                bmi_cat) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = full_data$os_time,
                             event = full_data$os_event)),
                   exponentiate = TRUE) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <-
  coxph(Surv(time = full_data$os_time,
             event = full_data$os_event) ~ 
          bmi_cat + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type + study,
        data =  full_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = bmi_cat) %>% bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

print("PH assumption")
coxph(Surv(time = full_data$os_time,
             event = full_data$os_event) ~ bmi_cat + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type + study,
        data =  full_data)  %>% 
  cox.zph()

tbl1 <- full_data %>% select(os_event, os_time,
                                tert_imat_area_cm2) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = full_data$os_time,
                             event = full_data$os_event)),
                   exponentiate = TRUE) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <-
  coxph(Surv(time = full_data$os_time,
             event = full_data$os_event) ~ 
          tert_imat_area_cm2 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type + study,
        data =  full_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_imat_area_cm2) %>% bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

print("PH assumption")
coxph(Surv(time = full_data$os_time,
             event = full_data$os_event) ~ tert_imat_area_cm2 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type + study,
        data =  full_data)  %>% 
  cox.zph()

tbl1 <- full_data %>% select(os_event, os_time,
                                tert_vat_area_cm2) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = full_data$os_time,
                             event = full_data$os_event)),
                   exponentiate = TRUE) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <-
  coxph(Surv(time = full_data$os_time,
             event = full_data$os_event) ~ 
          tert_vat_area_cm2 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type + study,
        data =  full_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_vat_area_cm2) %>% bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

print("PH assumption")
coxph(Surv(time = full_data$os_time,
             event = full_data$os_event) ~ tert_vat_area_cm2 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type + study,
        data =  full_data)  %>% 
  cox.zph()

tbl1 <- full_data %>% select(os_event, os_time,
                                tert_sat_area_cm2) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = full_data$os_time,
                             event = full_data$os_event)),
                   exponentiate = TRUE) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <-
  coxph(Surv(time = full_data$os_time,
             event = full_data$os_event) ~ 
          tert_sat_area_cm2 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type + study,
        data =  full_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_sat_area_cm2) %>% bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

print("PH assumption")
coxph(Surv(time = full_data$os_time,
             event = full_data$os_event) ~ tert_sat_area_cm2 + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type + study,
        data =  full_data)  %>% 
  cox.zph()

tbl1 <- full_data %>% select(os_event, os_time,
                                tert_total_fat_area) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = full_data$os_time,
                             event = full_data$os_event)),
                   exponentiate = TRUE) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <-
  coxph(Surv(time = full_data$os_time,
             event = full_data$os_event) ~ 
          tert_total_fat_area + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type + study,
        data =  full_data) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_total_fat_area) %>% bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

print("PH assumption")
coxph(Surv(time = full_data$os_time,
             event = full_data$os_event) ~ tert_total_fat_area + age_at_diagnosis + tnm_cs_mixed_group_stage + treatment_type + study,
        data =  full_data)  %>% 
  cox.zph()
```
<br>
<br>

## By treatment type

```{r Stratified treatment os}
full_data_neo <- full_data %>% 
  filter(treatment_type == "Upfront Neoadjuvant")

full_data_surg <- full_data %>% 
  filter(treatment_type == "Upfront Surgery")
```

Multivariable analyses are adjusted for `+ age_at_diagnosis + tnm_cs_mixed_group_stage + study`.  

### Upfront Chemo
```{r}
tbl1 <- full_data_neo %>% select(os_event, os_time,
                                bmi_cat) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = full_data_neo$os_time,
                             event = full_data_neo$os_event)),
                   exponentiate = TRUE) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <-
  coxph(Surv(time = full_data_neo$os_time,
             event = full_data_neo$os_event) ~ 
          bmi_cat + age_at_diagnosis + tnm_cs_mixed_group_stage + study,
        data =  full_data_neo) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = bmi_cat) %>% bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

tbl1 <- full_data_neo %>% select(os_event, os_time,
                                tert_imat_area_cm2) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = full_data_neo$os_time,
                             event = full_data_neo$os_event)),
                   exponentiate = TRUE, 
                   include = tert_imat_area_cm2) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <-
  coxph(Surv(time = full_data_neo$os_time,
             event = full_data_neo$os_event) ~ 
          tert_imat_area_cm2 + age_at_diagnosis + tnm_cs_mixed_group_stage + study,
        data =  full_data_neo) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_imat_area_cm2) %>% bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

tbl1 <- full_data_neo %>% select(os_event, os_time,
                                tert_vat_area_cm2) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = full_data_neo$os_time,
                             event = full_data_neo$os_event)),
                   exponentiate = TRUE, 
                   include = tert_vat_area_cm2) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <-
  coxph(Surv(time = full_data_neo$os_time,
             event = full_data_neo$os_event) ~ 
          tert_vat_area_cm2 + age_at_diagnosis + tnm_cs_mixed_group_stage + study,
        data =  full_data_neo) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_vat_area_cm2) %>% bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

tbl1 <- full_data_neo %>% select(os_event, os_time,
                                tert_sat_area_cm2) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = full_data_neo$os_time,
                             event = full_data_neo$os_event)),
                   exponentiate = TRUE, 
                   include = tert_sat_area_cm2) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <-
  coxph(Surv(time = full_data_neo$os_time,
             event = full_data_neo$os_event) ~ 
          tert_sat_area_cm2 + age_at_diagnosis + tnm_cs_mixed_group_stage + study,
        data =  full_data_neo) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_sat_area_cm2) %>% bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

tbl1 <- full_data_neo %>% select(os_event, os_time,
                                tert_total_fat_area) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = full_data_neo$os_time,
                             event = full_data_neo$os_event)),
                   exponentiate = TRUE, 
                   include = tert_total_fat_area) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <-
  coxph(Surv(time = full_data_neo$os_time,
             event = full_data_neo$os_event) ~ 
          tert_total_fat_area + age_at_diagnosis + tnm_cs_mixed_group_stage + study,
        data =  full_data_neo) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_total_fat_area) %>% bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))
```
<br>
<br>

### Upfront Surgery
```{r}
tbl1 <- full_data_surg %>% select(os_event, os_time,
                                bmi_cat) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = full_data_surg$os_time,
                             event = full_data_surg$os_event)),
                   exponentiate = TRUE) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <-
  coxph(Surv(time = full_data_surg$os_time,
             event = full_data_surg$os_event) ~ 
          bmi_cat + age_at_diagnosis + tnm_cs_mixed_group_stage + study,
        data =  full_data_surg) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = bmi_cat) %>% bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

tbl1 <- full_data_surg %>% select(os_event, os_time,
                                tert_imat_area_cm2) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = full_data_surg$os_time,
                             event = full_data_surg$os_event)),
                   exponentiate = TRUE, 
                   include = tert_imat_area_cm2) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <-
  coxph(Surv(time = full_data_surg$os_time,
             event = full_data_surg$os_event) ~ 
          tert_imat_area_cm2 + age_at_diagnosis + tnm_cs_mixed_group_stage + study,
        data =  full_data_surg) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_imat_area_cm2) %>% bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

tbl1 <- full_data_surg %>% select(os_event, os_time,
                                tert_vat_area_cm2) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = full_data_surg$os_time,
                             event = full_data_surg$os_event)),
                   exponentiate = TRUE, 
                   include = tert_vat_area_cm2) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <-
  coxph(Surv(time = full_data_surg$os_time,
             event = full_data_surg$os_event) ~ 
          tert_vat_area_cm2 + age_at_diagnosis + tnm_cs_mixed_group_stage + study,
        data =  full_data_surg) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_vat_area_cm2) %>% bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

tbl1 <- full_data_surg %>% select(os_event, os_time,
                                tert_sat_area_cm2) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = full_data_surg$os_time,
                             event = full_data_surg$os_event)),
                   exponentiate = TRUE, 
                   include = tert_sat_area_cm2) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <-
  coxph(Surv(time = full_data_surg$os_time,
             event = full_data_surg$os_event) ~ 
          tert_sat_area_cm2 + age_at_diagnosis + tnm_cs_mixed_group_stage + study,
        data =  full_data_surg) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_sat_area_cm2) %>% bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))

tbl1 <- full_data_surg %>% select(os_event, os_time,
                                tert_total_fat_area) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = full_data_surg$os_time,
                             event = full_data_surg$os_event)),
                   exponentiate = TRUE, 
                   include = tert_total_fat_area) %>% 
  bold_labels() %>% italicize_levels() %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <-
  coxph(Surv(time = full_data_surg$os_time,
             event = full_data_surg$os_event) ~ 
          tert_total_fat_area + age_at_diagnosis + tnm_cs_mixed_group_stage + study,
        data =  full_data_surg) %>%
  tbl_regression(exponentiate = TRUE, 
                 include = tert_total_fat_area) %>% bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))
```
<br>
<br>

