---
title: "5 years censor BCI analysis in Moffitt/Roswell data"
author: "Christelle Colin-Leitzinger"
date: '`r Sys.Date()`'
output: 
  html_document:
    toc: true
    toc_float: true
    toc_collapsed: false
    theme: united
    highlight: pygments
    df_print: paged
    code_folding: hide
editor_options: 
  chunk_output_type: console
---

<style type="text/css">

.figure {
   margin-top: 25px;
   margin-bottom: 100px;
}

table {
    margin-top: 10px;
    margin-bottom: 25px;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE,
                      cache = FALSE,
                      fig.align='center'
                      )
```

```{r library}
library(tidyverse)
library(ggplot2)
# library(mclust)
# library(data.table)
library(labelled)
library(gtsummary)
library(survival)
library(survminer)
# library(lubridate)
theme_gtsummary_compact()
theme_set(theme_classic())
```

```{r load}
adipose_data <- read_rds(paste0(here::here(), "/combined body comp data_2025-03-12.rds"))
```

# 1. Table S1. Patient characteristics and body composition depots by site
```{r Table S1}
adipose_data %>% 
  select(age_at_diagnosis, 
         tnm_cs_mixed_group_stage,
         debulking_status, 
         muscle_area_cm2, imat_area_cm2, vat_area_cm2, 
         sat_area_cm2, total_fat_area,
         BCI,
         site) %>% 
  tbl_summary(by = site,
              digits = all_continuous() ~ 1
  ) %>%  
  bold_labels() %>% add_overall() %>% 
  add_p() %>% bold_p() %>% 
  # add_stat_label() %>% 
  modify_footnote(update = everything() ~ NA)
```

# 2. Preparation of training/validation datasets
Here I created a 75% training dataset and 25% validation set split so Moffitt and Roswell cases are represented in both data in the same proportion.
```{r data split, echo = TRUE, class.source= 'fold-hide'}
library(tidymodels)
# Splitting the data
set.seed(1234)
# 3/4 of the data into the training set but split evenly within sites
data_split <- initial_split(adipose_data, prop = .75, strata = site)
# write_rds(data_split, paste0("data_split_", today(), ".rds"))
data_split <- 
  read_rds(paste0(here::here(), 
                  "/data_split_2025-03-12.rds"))
# Create training and training data sets:
training_data <- training(data_split) %>% 
  mutate(os_time_5year = case_when(
    os_time_from_dx_Jan2025 <= 5 * 12           ~ os_time_from_dx_Jan2025,
    os_time_from_dx_Jan2025 > 5 * 12            ~ 60,
    TRUE                                        ~ NA_real_
  )) %>% 
  mutate(os_event_5year = case_when(
    os_time_from_dx_Jan2025 <= 60               ~ os_event_Jan2025,
    os_time_from_dx_Jan2025 > 60                ~ 0,
    TRUE                                        ~ NA_real_
  )) %>% 
  mutate(recurrence_time_5year = case_when(
    rec_time_from_dx_Jan2025 <= 5 * 12           ~ rec_time_from_dx_Jan2025,
    rec_time_from_dx_Jan2025 > 5 * 12            ~ 60,
    TRUE                                        ~ NA_real_
  )) %>% 
  mutate(recurrence_event_5year = case_when(
    rec_time_from_dx_Jan2025 <= 60               ~ rec_event_Jan2025,
    rec_time_from_dx_Jan2025 > 60                ~ 0,
    TRUE                                        ~ NA_real_
  ))
  
validation_data  <- testing(data_split) %>% 
  mutate(os_time_5year = case_when(
    os_time_from_dx_Jan2025 <= 5 * 12           ~ os_time_from_dx_Jan2025,
    os_time_from_dx_Jan2025 > 5 * 12            ~ 60,
    TRUE                                        ~ NA_real_
  )) %>% 
  mutate(os_event_5year = case_when(
    os_time_from_dx_Jan2025 <= 60               ~ os_event_Jan2025,
    os_time_from_dx_Jan2025 > 60                ~ 0,
    TRUE                                        ~ NA_real_
  )) %>% 
  mutate(recurrence_time_5year = case_when(
    rec_time_from_dx_Jan2025 <= 5 * 12           ~ rec_time_from_dx_Jan2025,
    rec_time_from_dx_Jan2025 > 5 * 12            ~ 60,
    TRUE                                        ~ NA_real_
  )) %>% 
  mutate(recurrence_event_5year = case_when(
    rec_time_from_dx_Jan2025 <= 60               ~ rec_event_Jan2025,
    rec_time_from_dx_Jan2025 > 60                ~ 0,
    TRUE                                        ~ NA_real_
  ))

```

# 3. Table 1. Patient characteristics and body composition depots by dataset
```{r Table 1}
training_data %>% 
  mutate(dataset = "Training") %>% 
  bind_rows(., 
            validation_data %>% 
              mutate(dataset = "Validation")) %>% 
  select(age_at_diagnosis, 
         tnm_cs_mixed_group_stage,
         debulking_status, 
         muscle_area_cm2, imat_area_cm2, vat_area_cm2, 
         sat_area_cm2, total_fat_area,
         BCI,
         site, dataset) %>% 
  tbl_summary(by = dataset,
              digits = all_continuous() ~ 1
  ) %>%  
  bold_labels() %>% add_overall() %>% 
  add_p() %>% bold_p() %>% 
  # add_stat_label() %>% 
  modify_footnote(update = everything() ~ NA)
```

# 4.Estimate a cut point based on the training dataset
I have been using a cutpoint estimation method using the `maxstat` package directly while it seems Roswell used the `survminer` package. The later actually determine the optimal cutpoint using the maximally selected rank statistics from the `maxstat` R package.   
I checked both ways just in case and the cutpoint estimate is the same.

## Survminer package - cutpoint estimation on the training data
```{r cut point surminer, echo = TRUE, class.source= 'fold-hide'}
res.cut <- surv_cutpoint(training_data, time = "os_time_5year", event = "os_event_5year",
   variables = c("BCI"))

plot(res.cut, "BCI")
```

```{r make cat, echo = TRUE, class.source= 'fold-hide'}
training_data_cat <- training_data %>% 
  mutate(BCI_cat = case_when(
    BCI <= res.cut[["cutpoint"]][["cutpoint"]]           ~ "Low",
    BCI > res.cut[["cutpoint"]][["cutpoint"]]            ~ "High"
  ), BCI_moffitt_cat = factor(BCI_moffitt_cat, 
                              levels = c("High", "Low")))

validation_data_cat <- validation_data %>% 
  mutate(BCI_cat = case_when(
    BCI <= res.cut[["cutpoint"]][["cutpoint"]]           ~ "Low",
    BCI > res.cut[["cutpoint"]][["cutpoint"]]            ~ "High"
  ), BCI_moffitt_cat = factor(BCI_moffitt_cat, 
                              levels = c("High", "Low")))
```

# 5. Table 2. Patient characteristics and body composition depots by BCI categories
```{r Table 2}
training_data_cat %>% 
  mutate(dataset = "Training") %>% 
  bind_rows(., 
            validation_data_cat %>% 
              mutate(dataset = "Validation")) %>% 
  select(age_at_diagnosis, 
         tnm_cs_mixed_group_stage,
         debulking_status, 
         muscle_area_cm2, imat_area_cm2, vat_area_cm2, 
         sat_area_cm2, total_fat_area,
         BCI, BCI_cat,
         site, dataset) %>% 
  tbl_summary(by = BCI_cat,
              digits = all_continuous() ~ 1
  ) %>%  
  bold_labels() %>% add_overall() %>% 
  add_p() %>% bold_p() %>% 
  # add_stat_label() %>% 
  modify_footnote(update = everything() ~ NA)
```


# 5. KM by cutpoint analysis (training data)
```{r KM, fig.height=6}
myplot <- survfit(Surv(os_time_5year, event = os_event_5year) ~ BCI_cat, data = training_data_cat)
ggsurvplot(myplot, data = training_data_cat,
           title = "OS Analysis",
           font.main = c(20, "bold", "black"),
           font.x = c(18, "bold", "black"),
           font.y = c(18, "bold", "black"),
           font.legend = c(16, "black"),
           font.tickslab = c(16, "bold", "black"),
           size = 1,

           xlab = "Time (months)",
           legend = "top",
           legend.title = "",
           # legend.labs = c("Low", "High"),
           pval = TRUE,
           conf.int = FALSE,
           # Censor
           censor = TRUE,
           risk.table = TRUE
) #%++% guides(colour = guide_legend(ncol = 1))

```


```{r}
myplot <- survfit(Surv(recurrence_time_5year, event = recurrence_event_5year) ~ BCI_cat, data = training_data_cat)
ggsurvplot(myplot, data = training_data_cat,
           title = "PFS Analysis",
           font.main = c(20, "bold", "black"),
           font.x = c(18, "bold", "black"),
           font.y = c(18, "bold", "black"),
           font.legend = c(16, "black"),
           font.tickslab = c(16, "bold", "black"),
           size = 1.5,

           xlab = "Time in months",
           legend = "top",
           legend.title = "",
           # legend.labs = c("Low", "High"),
           pval = TRUE,
           conf.int = FALSE,
           # Censor
           censor = TRUE,
           risk.table = TRUE
) #%++% guides(colour = guide_legend(ncol = 1))
```

# 6. HR (training data)
## OS
```{r HR OS}
coxph(Surv(os_time_5year, event = os_event_5year) ~ 
        BCI_cat + age_at_diagnosis + tnm_cs_mixed_group_stage + debulking_status + site, 
      data = training_data_cat) %>%
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% 
  add_n(location = "level")
```

## PFS
```{r}
coxph(Surv(recurrence_time_5year, event = recurrence_event_5year) ~ 
        BCI_cat + age_at_diagnosis + tnm_cs_mixed_group_stage + debulking_status + site, 
      data = training_data_cat) %>%
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% 
  add_n(location = "level")
```

# 7. KM by cutpoint analysis (validation data)
```{r KM validation, fig.height=6}
myplot <- survfit(Surv(os_time_5year, event = os_event_5year) ~ BCI_cat, data = validation_data_cat)
ggsurvplot(myplot, data = validation_data_cat,
           title = "OS Analysis",
           font.main = c(20, "bold", "black"),
           font.x = c(18, "bold", "black"),
           font.y = c(18, "bold", "black"),
           font.legend = c(16, "black"),
           font.tickslab = c(16, "bold", "black"),
           size = 1,

           xlab = "Time (months)",
           legend = "top",
           legend.title = "",
           # legend.labs = c("Low", "High"),
           pval = TRUE,
           conf.int = FALSE,
           # Censor
           censor = TRUE,
           risk.table = TRUE
) #%++% guides(colour = guide_legend(ncol = 1))

```

```{r}
myplot <- survfit(Surv(recurrence_time_5year, event = recurrence_event_5year) ~ BCI_cat, data = validation_data_cat)
ggsurvplot(myplot, data = validation_data_cat,
           title = "PFS Analysis",
           font.main = c(20, "bold", "black"),
           font.x = c(18, "bold", "black"),
           font.y = c(18, "bold", "black"),
           font.legend = c(16, "black"),
           font.tickslab = c(16, "bold", "black"),
           size = 1.5,

           xlab = "Time in months",
           legend = "top",
           legend.title = "",
           # legend.labs = c("Low", "High"),
           pval = TRUE,
           conf.int = FALSE,
           # Censor
           censor = TRUE,
           risk.table = TRUE
) %++% guides(colour = guide_legend(ncol = 1))
```

# 8. HR (validation data)
## OS
```{r HR OS validation}
coxph(Surv(os_time_5year, event = os_event_5year) ~ 
        BCI_cat + age_at_diagnosis + tnm_cs_mixed_group_stage + debulking_status + site, 
      data = validation_data_cat) %>%
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% 
  add_n(location = "level")
```

## PFS
```{r}
coxph(Surv(recurrence_time_5year, event = recurrence_event_5year) ~ 
        BCI_cat + age_at_diagnosis + tnm_cs_mixed_group_stage + debulking_status + site, 
      data = validation_data_cat) %>%
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% 
  add_n(location = "level")
```
















