---
title: "Untitled"
author: "Christelle Colin-Leitzinger"
date: '`r Sys.Date()`'
output: 
  html_document:
    toc: true
    toc_float: true
    toc_collapsed: false
    theme: united
    highlight: pygments
    df_print: paged
editor_options: 
  chunk_output_type: console
---

<style type="text/css">

.figure {
   margin-top: 25px;
   margin-bottom: 100px;
}

table {
    margin-top: 10px;
    margin-bottom: 25px;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE,
                      cache = FALSE,
                      fig.align='center'
                      )
```

```{r library}
library(tidyverse)
library(ggplot2)
library(mclust)
library(data.table)
library(labelled)
library(gtsummary)
library(survival)
library(survminer)
library(mice)
library(lubridate)
theme_gtsummary_compact()
theme_set(theme_classic())
```

```{r load}
adipose_data <- read_rds(paste0(here::here(), "/adipose_data2024-11-15.rds")) %>% 
  mutate(raceeth2 = case_when(
    raceeth == "White Non-Hispanic"          ~ "White Non-Hispanic",
    raceeth == "Black Non-Hispanic" |
      raceeth == "Hispanic"                  ~ "Black or Hispanic"
  )) %>% 
  
  mutate(pfs_event = case_when(
    vital_new == "Dead"                      ~ 1,
    TRUE                                     ~ rec_event
  )) %>%
  mutate(has_the_patient_progressed = case_when(
    os_event == 1                           ~ "Progression",
    os_event == 0                           ~ "No Progression"
  )) %>%
  mutate(pfs_time = recurrence_time) %>% 
  mutate(debulking_status = case_when(
    debulking_status == "Complete"           ~ "Optimal",
    debulking_status == "Optimal"            ~ "Optimal",
    debulking_status == "Suboptimal"         ~ "Suboptimal",
    is.na(debulking_status)                  ~ "Unknown"
  ), debulking_status = factor(debulking_status,
                               levels = c("Suboptimal", "Optimal", "Unknown"))) %>% 
  mutate(tnm_cs_mixed_group_stage = case_when(
    is.na(tnm_cs_mixed_group_stage)          ~ "Unknown",
    TRUE                                     ~ tnm_cs_mixed_group_stage
  ), tnm_cs_mixed_group_stage = factor(tnm_cs_mixed_group_stage,
                                       levels = c("I-II", "III", "IV", "Unknown")))
```

# Investigate BCI
```{r table BCI}
adipose_data %>% 
  select(BCI, BCI_roswell_cat) %>% 
  
  tbl_summary(
    # type = list(year_of_diagnosis ~ "categorical", 
    #                       all_dichotomous() ~ "categorical"), 
            statistic=list(all_continuous() ~ "{mean} ({min}-{max})"), 
            digits = all_continuous() ~ 1
    ) %>%  
  bold_labels() %>% add_stat_label() %>% 
  modify_footnote(update = everything() ~ NA)
```

```{r plot BCI}
adipose_data %>% 
  select(
    BCI, BCI_roswell_cat
  ) %>% 
  ggplot(aes(x = BCI_roswell_cat, y= BCI, color = BCI_roswell_cat))+
  geom_boxplot()+
  geom_jitter()+
  scale_color_viridis_d(option = "G", end = c(0.8))+
  theme(legend.position="bottom")

adipose_data %>% 
  select(
    BCI, SMA, BCI_roswell_cat
  ) %>% 
  ggplot(aes(x = SMA, y= BCI, shape = BCI_roswell_cat, color = BCI > 10))+
  geom_point()+
  scale_color_viridis_d(option = "G", end = c(0.8))+
  theme(legend.position="bottom")

adipose_data %>% 
  select(
    BCI, height_m_, BCI_roswell_cat
  ) %>% 
  ggplot(aes(x = height_m_, y= BCI, shape = BCI_roswell_cat, color = BCI > 10))+
  geom_point()+
  scale_color_viridis_d(option = "G", end = c(0.8))+
  theme(legend.position="bottom")

adipose_data %>% 
  select(
    BCI, sat_area_cm2, BCI_roswell_cat
  ) %>% 
  ggplot(aes(x = sat_area_cm2, y= BCI, shape = BCI_roswell_cat, color = BCI > 10))+
  geom_point()+
  scale_color_viridis_d(option = "G", end = c(0.8))+
  theme(legend.position="bottom")

adipose_data %>% 
  select(
    BCI, vat_area_cm2, BCI_roswell_cat
  ) %>% 
  ggplot(aes(x = vat_area_cm2, y= BCI, shape = BCI_roswell_cat, color = BCI > 10))+
  geom_point()+
  scale_color_viridis_d(option = "G", end = c(0.8))+
  theme(legend.position="bottom")

adipose_data %>% 
  select(
    BCI, imat_area_cm2, BCI_roswell_cat
  ) %>% 
  ggplot(aes(x = imat_area_cm2, y= BCI, shape = BCI_roswell_cat, color = BCI > 10))+
  geom_point()+
  scale_color_viridis_d(option = "G", end = c(0.8))+
  theme(legend.position="bottom")
```

# Investigate survival using Roswell BCI cut points
## HR complete case (I left debulking status as strata term as we had it in strata for our analysis)
### Overall pop
#### OS
```{r HR OS overall pop}
coxph(Surv(time = adipose_data$os_time,
             event = adipose_data$os_event) ~ 
          BCI + age_at_diagnosis + tnm_cs_mixed_group_stage + strata(debulking_status),
        data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")

coxph(Surv(time = adipose_data$os_time,
             event = adipose_data$os_event) ~ 
          BCI_roswell_cat + age_at_diagnosis + tnm_cs_mixed_group_stage + strata(debulking_status),
        data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")
```

#### PFS
```{r HR PFS overall pop}
coxph(Surv(time = adipose_data$pfs_time,
             event = adipose_data$pfs_event) ~ 
          BCI + age_at_diagnosis + tnm_cs_mixed_group_stage + strata(debulking_status),
        data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")

coxph(Surv(time = adipose_data$pfs_time,
             event = adipose_data$pfs_event) ~ 
          BCI_roswell_cat + age_at_diagnosis + tnm_cs_mixed_group_stage + strata(debulking_status),
        data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")
```

### HR in stage III-IV
```{r}
adipose_data_stage3_4 <- adipose_data %>% 
  filter(tnm_cs_mixed_group_stage %in% c("III", "IV"))
```

#### OS
```{r HR OS stage3-4}
coxph(Surv(time = adipose_data_stage3_4$os_time,
             event = adipose_data_stage3_4$os_event) ~ 
          BCI + age_at_diagnosis + strata(debulking_status),
        data =  adipose_data_stage3_4) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")

coxph(Surv(time = adipose_data_stage3_4$os_time,
             event = adipose_data_stage3_4$os_event) ~ 
          BCI_roswell_cat + age_at_diagnosis + strata(debulking_status),
        data =  adipose_data_stage3_4) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")
```

#### PFS
```{r HR PFS stage3-4}
coxph(Surv(time = adipose_data_stage3_4$pfs_time,
             event = adipose_data_stage3_4$pfs_event) ~ 
          BCI + age_at_diagnosis + strata(debulking_status),
        data =  adipose_data_stage3_4) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")

coxph(Surv(time = adipose_data_stage3_4$pfs_time,
             event = adipose_data_stage3_4$pfs_event) ~ 
          BCI_roswell_cat + age_at_diagnosis + strata(debulking_status),
        data =  adipose_data_stage3_4) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")
```

## KM
### Overall pop
#### OS
```{r KM OS overall pop}
mysurv <- Surv(adipose_data$os_time, event = adipose_data$os_event)
myplot <- survfit(mysurv~BCI_roswell_cat, data = adipose_data)
ggsurvplot(myplot, data = adipose_data,
           title = "OS Analysis",
           font.main = c(20, "bold", "black"),
           font.x = c(18, "bold", "black"),
           font.y = c(18, "bold", "black"),
           font.legend = c(16, "black"),
           font.tickslab = c(16, "bold", "black"),
           size = 1.5,

           xlab = "Time in months",
           legend = "top",
           legend.title = "",
           # legend.labs = c("Low", "High"),
           pval = TRUE,
           conf.int = FALSE,
           # Censor
           censor = TRUE
) %++% guides(colour = guide_legend(ncol = 1))
```

#### PFS
```{r KM PFS overall pop}
mysurv <- Surv(adipose_data$pfs_time, event = adipose_data$pfs_event)
myplot <- survfit(mysurv~BCI_roswell_cat, data = adipose_data)
ggsurvplot(myplot, data = adipose_data,
           title = "PFS Analysis",
           font.main = c(20, "bold", "black"),
           font.x = c(18, "bold", "black"),
           font.y = c(18, "bold", "black"),
           font.legend = c(16, "black"),
           font.tickslab = c(16, "bold", "black"),
           size = 1.5,

           xlab = "Time in months",
           legend = "top",
           legend.title = "",
           # legend.labs = c("Low", "High"),
           pval = TRUE,
           conf.int = FALSE,
           # Censor
           censor = TRUE
) %++% guides(colour = guide_legend(ncol = 1))
```

### Stage III-IV
#### OS
```{r KM OS stage3-4}
mysurv <- Surv(adipose_data_stage3_4$os_time, event = adipose_data_stage3_4$os_event)
myplot <- survfit(mysurv~BCI_roswell_cat, data = adipose_data_stage3_4)
ggsurvplot(myplot, data = adipose_data_stage3_4,
           title = "OS Analysis",
           font.main = c(20, "bold", "black"),
           font.x = c(18, "bold", "black"),
           font.y = c(18, "bold", "black"),
           font.legend = c(16, "black"),
           font.tickslab = c(16, "bold", "black"),
           size = 1.5,

           xlab = "Time in months",
           legend = "top",
           legend.title = "",
           # legend.labs = c("Low", "High"),
           pval = TRUE,
           conf.int = FALSE,
           # Censor
           censor = TRUE
) %++% guides(colour = guide_legend(ncol = 1))
```

#### PFS
```{r KM PFS stage3-4}
mysurv <- Surv(adipose_data_stage3_4$pfs_time, event = adipose_data_stage3_4$pfs_event)
myplot <- survfit(mysurv~BCI_roswell_cat, data = adipose_data_stage3_4)
ggsurvplot(myplot, data = adipose_data_stage3_4,
           title = "PFS Analysis",
           font.main = c(20, "bold", "black"),
           font.x = c(18, "bold", "black"),
           font.y = c(18, "bold", "black"),
           font.legend = c(16, "black"),
           font.tickslab = c(16, "bold", "black"),
           size = 1.5,

           xlab = "Time in months",
           legend = "top",
           legend.title = "",
           # legend.labs = c("Low", "High"),
           pval = TRUE,
           conf.int = FALSE,
           # Censor
           censor = TRUE
) %++% guides(colour = guide_legend(ncol = 1))
```


# Estimate a cut point specific to Moffitt dataset
## BCI as a unique factor
each plot has a diffrent p-value method
```{r cut points BCI}
library(maxstat)

set.seed(1234)
mstat <- maxstat.test(Surv(time = adipose_data$os_time,
             event = adipose_data$os_event) ~ BCI,
        data =  adipose_data, 
                      smethod="LogRank", pmethod="exactGauss", 
                      abseps=0.01)
mstat
plot(mstat)


mstat <- maxstat.test(Surv(time = adipose_data$os_time,
             event = adipose_data$os_event) ~ BCI,
        data =  adipose_data, 
                      smethod="LogRank", pmethod="Lau92", 
                      abseps=0.01)
mstat
plot(mstat)

mstat <- maxstat.test(Surv(time = adipose_data$os_time,
             event = adipose_data$os_event) ~ BCI,
        data =  adipose_data, 
                      smethod="LogRank", pmethod="Lau94", 
                      abseps=0.01)
mstat
plot(mstat)

mstat <- maxstat.test(Surv(time = adipose_data$os_time,
             event = adipose_data$os_event) ~ BCI,
        data =  adipose_data, 
                      smethod="LogRank", pmethod="HL", 
                      abseps=0.01)
mstat
plot(mstat)

mstat <- maxstat.test(Surv(time = adipose_data$os_time,
             event = adipose_data$os_event) ~ BCI,
        data =  adipose_data, 
                      smethod="LogRank", pmethod="condMC", 
                      abseps=0.01)
mstat
plot(mstat)
```

## BCI + age_at_diagnosis
```{r cut points BCI + age_at_diagnosis}
mstat <- maxstat.test(Surv(time = adipose_data$os_time,
             event = adipose_data$os_event) ~ age_at_diagnosis + BCI,
        data =  adipose_data, 
                      smethod="LogRank", pmethod="exactGauss", 
                      abseps=0.01)
mstat
plot(mstat)
```

## HR complete case (I left debulking status as strata term as we had it in strata for our analysis)
### Overall pop
#### OS
```{r HR moffitt OS overall pop}
coxph(Surv(time = adipose_data$os_time,
             event = adipose_data$os_event) ~ 
          BCI_moffitt_cat + age_at_diagnosis + tnm_cs_mixed_group_stage + strata(debulking_status),
        data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")
```

#### PFS
```{r HR moffitt PFS overall pop}
coxph(Surv(time = adipose_data$pfs_time,
             event = adipose_data$pfs_event) ~ 
          BCI_moffitt_cat + age_at_diagnosis + tnm_cs_mixed_group_stage + strata(debulking_status),
        data =  adipose_data) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")
```
### In stage III-IV
#### OS
```{r HR moffitt OS stage3-4}
coxph(Surv(time = adipose_data_stage3_4$os_time,
             event = adipose_data_stage3_4$os_event) ~ 
          BCI_moffitt_cat + age_at_diagnosis + strata(debulking_status),
        data =  adipose_data_stage3_4) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")
```

#### PFS
```{r HR moffitt PFS  stage3-4}
coxph(Surv(time = adipose_data_stage3_4$pfs_time,
             event = adipose_data_stage3_4$pfs_event) ~ 
          BCI_moffitt_cat + age_at_diagnosis + strata(debulking_status),
        data =  adipose_data_stage3_4) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% 
  add_nevent(location = "level") %>% add_n(location = "level")
```

## KM
### Overall pop
```{r KM OS moffitt overall pop}
mysurv <- Surv(adipose_data$os_time, event = adipose_data$os_event)
myplot <- survfit(mysurv~BCI_moffitt_cat, data = adipose_data)
ggsurvplot(myplot, data = adipose_data,
           title = "OS Analysis",
           font.main = c(20, "bold", "black"),
           font.x = c(18, "bold", "black"),
           font.y = c(18, "bold", "black"),
           font.legend = c(16, "black"),
           font.tickslab = c(16, "bold", "black"),
           size = 1.5,

           xlab = "Time in months",
           legend = "top",
           legend.title = "",
           # legend.labs = c("Low", "High"),
           pval = TRUE,
           conf.int = FALSE,
           # Censor
           censor = TRUE
) %++% guides(colour = guide_legend(ncol = 1))
```

```{r KM PFS moffitt overall pop}
mysurv <- Surv(adipose_data$pfs_time, event = adipose_data$pfs_event)
myplot <- survfit(mysurv~BCI_moffitt_cat, data = adipose_data)
ggsurvplot(myplot, data = adipose_data,
           title = "PFS Analysis",
           font.main = c(20, "bold", "black"),
           font.x = c(18, "bold", "black"),
           font.y = c(18, "bold", "black"),
           font.legend = c(16, "black"),
           font.tickslab = c(16, "bold", "black"),
           size = 1.5,

           xlab = "Time in months",
           legend = "top",
           legend.title = "",
           # legend.labs = c("Low", "High"),
           pval = TRUE,
           conf.int = FALSE,
           # Censor
           censor = TRUE
) %++% guides(colour = guide_legend(ncol = 1))
```

# Stage III-IV
```{r KM OS moffitt stage3-4}
mysurv <- Surv(adipose_data_stage3_4$os_time, event = adipose_data_stage3_4$os_event)
myplot <- survfit(mysurv~BCI_moffitt_cat, data = adipose_data_stage3_4)
ggsurvplot(myplot, data = adipose_data_stage3_4,
           title = "OS Analysis",
           font.main = c(20, "bold", "black"),
           font.x = c(18, "bold", "black"),
           font.y = c(18, "bold", "black"),
           font.legend = c(16, "black"),
           font.tickslab = c(16, "bold", "black"),
           size = 1.5,

           xlab = "Time in months",
           legend = "top",
           legend.title = "",
           # legend.labs = c("Low", "High"),
           pval = TRUE,
           conf.int = FALSE,
           # Censor
           censor = TRUE
) %++% guides(colour = guide_legend(ncol = 1))
```

```{r KM PFS moffitt stage3-4}
mysurv <- Surv(adipose_data_stage3_4$pfs_time, event = adipose_data_stage3_4$pfs_event)
myplot <- survfit(mysurv~BCI_moffitt_cat, data = adipose_data_stage3_4)
ggsurvplot(myplot, data = adipose_data_stage3_4,
           title = "PFS Analysis",
           font.main = c(20, "bold", "black"),
           font.x = c(18, "bold", "black"),
           font.y = c(18, "bold", "black"),
           font.legend = c(16, "black"),
           font.tickslab = c(16, "bold", "black"),
           size = 1.5,

           xlab = "Time in months",
           legend = "top",
           legend.title = "",
           # legend.labs = c("Low", "High"),
           pval = TRUE,
           conf.int = FALSE,
           # Censor
           censor = TRUE
) %++% guides(colour = guide_legend(ncol = 1))
```

