---
title: "Moffitt New Models"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_collapsed: false
    theme: united
    highlight: pygments
editor_options: 
  chunk_output_type: console
---

data must include the following features: survstat, survtime, ht_first_met, PRE_SMA_1, PRE_SUBQ_1, PRE_IMA_1, PRE_VAT_1, PRE_TAT_1

survstat = survival status   
survtime = survival time   
ht_first_met = height in meters   
PRE_SMA_1 = skeletal muscle area, equivalent to muscle_area_cm2

PRE_SUBQ_1 = skeletal muscle area, equivalent to imat_area_cm2
    
PRE_IMA_1 = intramuscular adipose area, equivalent to vat_area_cm2
    
PRE_VAT_1 = visceral adipose area, equivalent to sat_area_cm2
    
PRE_TAT_1 = total adipose area, equivalent to total_fat_area

    
necessary libraries
```{r, message=FALSE}
library(dplyr)
library(recipes)
library(glmnet)
library(selectiveInference)
library(lars)
library(L0Learn)
library(survminer)
library(survival)
library(gtsummary)
theme_gtsummary_compact()
```

load data and models
```{r christelle added load and clean, echo=FALSE}
library(tidyverse)
###_______________________ custom function _______________________###
fct_name_repair <- function(colnms) {
  tolower(gsub("[, ()=/]", "_", colnms))
}
###_______________________________________________________________###

path <- fs::path("","Volumes","Peres_Research", "Ovarian - Radiomics")
body_comp <-
  readxl::read_xlsx(paste0(path, "/CTbased adiposity",
                           "/dataset/CT data 09272021.xlsx"),
                    .name_repair = fct_name_repair) %>% 
  `colnames<-`(str_replace(colnames(.), "__", "_"))
# clinical_data <-
#   read_csv(paste0(path, "/CTbased adiposity",
#                   "/dataset/ForDan_clinical_modif_06092022.csv"))
updated_survival <- 
  read_rds(paste0(path, 
                  "/Grant applications/Miles for Moffitt/data/",
                  "processed data/Ovarian_Normalized_Radiomics_Features_30Apr2025.rds")) %>% 
  `colnames<-`(str_replace(colnames(.), "__", "_")) %>% 
  mutate(baseline_ct_scan_date = as.Date(baseline_ct_scan_date, format = "%m/%d/%Y")) %>% 
  distinct(mrn, .keep_all = TRUE)

moffitt_data <- left_join(body_comp, updated_survival, 
                          by=c("mrn", "date_of_diagnosis", "baseline_ct_scan_date")) %>% # keep patient with ct image
  purrr::keep(~!all(is.na(.))) %>%
  # Eight patients were excluded due to coverage artifacts
  filter(is.na(should_exclude)) %>% 
  # Outcome
  mutate(survtime = round(interval(start = date_of_diagnosis, end = fwdate_most_recent)/
                                   duration(n=1, units = "months"), 2)) %>% 
  mutate(race_all = str_to_sentence(race_cancer_registry)) %>% 
  mutate(race = case_when(
    race_all == "White"       ~ "White",
    race_all == "Black"       ~ "Black",
    race_all == "Unkno"       ~ NA_character_,
    !is.na(race_all)          ~ "Other"
  )) %>% 
  mutate(ethnicity = case_when(
    ethnicity_cancer_registry == "UNKNOWN"               ~ NA_character_,
    ethnicity_cancer_registry == "NON-SPANISH"           ~ "Non-Hispanic",
    !is.na(ethnicity_cancer_registry)                    ~ "Hispanic"
  )) %>% 
  mutate(debulking = case_when(
    debulking_status == "incomplete records"                    ~ NA_character_,
    str_detect(debulking_status, "^optimal \\(")                ~ "Optimal",
    str_detect(debulking_status, "^suboptimal \\(")             ~ "Suboptimal",
    str_detect(debulking_status, "^complete \\(")               ~ "Optimal"
  )) %>% 
  mutate(weight_kg = case_when(
    weight_unit == "kg" |
      weight_unit == "Kg"                  ~ weight,
    weight_unit == "lbs"                   ~ weight / 2.205
  )) %>% 
  mutate(bmi = weight_kg / (height_m_ * height_m_)) %>% 
  mutate(bmi_cat = case_when(
    bmi < 25                    ~ "<25 kg/m²",
    bmi >= 25 &
      bmi < 30                  ~ "25-30 kg/m²",
    bmi >= 30                   ~ "≥30 kg/m²"
  )) %>%
  mutate(bmi_cat = factor(bmi_cat, levels = c("<25 kg/m²", "25-30 kg/m²", "≥30 kg/m²"))) %>% 

  dplyr::select(moffitt_id = id,
         ht_first_met = height_m_,
         PRE_SMA_1 = muscle_area_cm2, 
         PRE_IMA_1 = imat_area_cm2,
         PRE_VAT_1 = vat_area_cm2, 
         PRE_SUBQ_1 = sat_area_cm2, 
         PRE_TAT_1 = total_fat_area, 
         survstat = os_event, 
         survtime, 
         age_at_diagnosis, 
         year_of_diagnosis, 
         race, race_all, ethnicity, 
         tnm_cs_mixed_group_stage,
         treatment_type,
         debulking,
         weight_kg,
         bmi, bmi_cat
         ) %>% 
  filter(!is.na(PRE_SMA_1))
```


```{r}
data <- moffitt_data
```

```{r}
set.seed(1)

### read in data: xlsx or csv

#data = read.xlsx("C://PhD work//EOC-body-comp//De-ID Data Set for Moffitt 04032024.xlsx", 1)
# data = read.csv("C://PhD work//EOC-body-comp//De-ID Data Set for Moffitt 04032024.csv")

#check whether data has necessary columns
features = c("survstat", "survtime", "ht_first_met", "PRE_SMA_1", "PRE_SUBQ_1", "PRE_IMA_1", "PRE_VAT_1", "PRE_TAT_1")

#all features must be in imported data, should return TRUE
#if returns FALSE, data is missing some features or features are incorrectly named

all(features %in% colnames(data))
```

# Moffitt patient characteristics
## Clinical table
```{r Patient characteristics}
moffitt_data %>%
  select("Age" = age_at_diagnosis, 
         "Diagnosis (year)" = year_of_diagnosis,
         Race = race, Ethnicity = ethnicity, "Stage" = tnm_cs_mixed_group_stage,
         "first course treatment" = treatment_type,
         "Debulking status" = debulking,
         "Weight (kg)" = weight_kg,
         "BMI (continuous)" = bmi, "BMI (categorical)" = bmi_cat,
         survstat, survtime, ht_first_met, PRE_SMA_1, PRE_SUBQ_1, PRE_IMA_1, PRE_VAT_1, PRE_TAT_1
         ) %>%
  tbl_summary(type = list(c(survstat, "Diagnosis (year)"
                             ) ~ "categorical",
                         c(all_continuous()) ~ "continuous2"),
              statistic = list(all_continuous() ~ c("{median} ({p25}, {p75})", "{min}, {max}"))
              ) %>%
  bold_labels() %>%
  # add_p() %>% bold_p() %>% add_overall() %>% 
  modify_header(label ~ "**Patient characteristics**",
                all_stat_cols() ~ "**{level}**, N = {n}")
```

## KM and Survival table of Moffitt patients. Show how many patients were alive or dead at 1, 3, 5, 8, 10 years after diagnosis
```{r, message=FALSE, warning=FALSE, fig.height=8, fig.width=10}
ggsurvplot(survfit(Surv(survtime, survstat) ~ 1,
                   data = moffitt_data),
           font.main = c(20, "bold", "black"),
           font.x = c(18, "bold", "black"),
           font.y = c(18, "bold", "black"),
           font.legend = c(16, "black"),
           font.tickslab = c(16, "bold", "black"),
           size = 1.5,

           xlab = "Time (months)",
           legend = "top",
           pval = TRUE,
           conf.int = FALSE,
           # Censor
           censor = TRUE,
           cumevents = TRUE,
           risk.table = TRUE, #"nrisk_cumevents",
           break.time.by = 12
)
```


# Models
Load saved models trained on Roswell data
EOC_Models includes: recipe features, cvfit_lasso, beta, fit_lasso_inf, larfit, cv_lars_lar, fit_lars_lar, cvfit_L0

```{r}
# load("C://PhD work//EOC-body-comp//EOC_models.RData")
load(paste0(here::here(),
            "/data/raw_data/model/EOC_models.RData"))
```


Generate feature matrix from baseline CT features
```{r warning=FALSE}
#isolate features of interest and calculate indexes
data_indices = data %>%
        dplyr::select(survstat, ht_first_met, PRE_SMA_1, PRE_SUBQ_1, 
                      PRE_IMA_1, PRE_VAT_1, PRE_TAT_1) %>%
        mutate(SMI = PRE_SMA_1/ht_first_met) %>%
        mutate(SFI = PRE_SUBQ_1/ht_first_met) %>%
        mutate(VFI = PRE_VAT_1/ht_first_met) %>%
        mutate(IMAI = PRE_IMA_1/ht_first_met) %>%
        mutate(TATI = PRE_TAT_1/ht_first_met) %>% 
        dplyr::select(-c(ht_first_met)) %>%
        mutate(across(everything(), as.numeric))


#generate ratios, polynomials, and products of features
rec = recipe(survstat ~ ., data = data_indices) %>%
    step_mutate(
      ratio = PRE_SMA_1/PRE_SUBQ_1,
      ratio2 = PRE_SMA_1/PRE_IMA_1,
      ratio3  = PRE_SMA_1/PRE_VAT_1,
      ratio4  = PRE_SMA_1/PRE_TAT_1,
      ratio5  = PRE_SUBQ_1/PRE_SMA_1,
      ratio6  = PRE_SUBQ_1/PRE_IMA_1,
      ratio7  = PRE_SUBQ_1/PRE_VAT_1,
      ratio8  = PRE_SUBQ_1/PRE_TAT_1,
      ratio9  = PRE_IMA_1/PRE_SMA_1,
      ratio10  = PRE_IMA_1/PRE_SUBQ_1,
      ratio11  = PRE_IMA_1/PRE_VAT_1,
      ratio12  = PRE_IMA_1/PRE_TAT_1,
      ratio13  = PRE_VAT_1/PRE_TAT_1,
      ratio14  = PRE_VAT_1/PRE_SMA_1,
      ratio15  = PRE_VAT_1/PRE_IMA_1,
      ratio16  = PRE_VAT_1/PRE_SUBQ_1
      ) %>%
    step_poly(all_numeric_predictors(), options = list(raw = TRUE)) %>%
    step_interact(terms = ~ all_predictors():all_predictors()) %>%
    step_zv(all_numeric_predictors()) %>%
    step_normalize(all_numeric_predictors()) %>%
    prep()

data_final = juice(rec)
data_final = data_final[recipe_features]
X = model.matrix(survstat ~ . - 1, data = data_final)
y = data_final$survstat


#ensure X is scaled and centered, both expression should return TRUE
max(apply(X, 2, mean)) < 0.001
max(apply(X, 2, sd)) < 1.001
```
Predict regression values using new data
```{r}
#normal Lasso, alpha 0.1
lasso_preds = predict(cvfit_lasso, newx = X, s = "lambda.min", type = "response")
lasso_preds_1se = predict(cvfit_lasso, newx = X, s = "lambda.1se", type = "response")

#lasso with selective inference

vars = fit_lasso_inf$vars[which(fit_lasso_inf$pv < 0.1)]
intercept = beta@x[1]
index_inf = which(fit_lasso_inf$pv<0.1)+1 #add one because beta keeps intercept as first index

coefs_inf = beta@x[index_inf]
lasso_preds_inf = intercept + as.matrix(data_final[vars]) %*% as.vector(coefs_inf)

#lar from selective inference package, full path
lar_preds = predict(larfit, X, s = 335)[,1]

#lar from lars package with cross-validation
best_step <- which.min(cv_lars_lar$cv)  # index of best CV error
lar_lars_preds = predict(fit_lars_lar, newx = X, s = best_step, mode = "step")$fit

#L0 regularization
optimalGammaIndex = which.min(lapply(cvfit_L0$cvMeans, min))
optimalGamma = cvfit_L0$fit$gamma[optimalGammaIndex]
optimalLambdaIndex = which.min(cvfit_L0$cvMeans[[optimalGammaIndex]])
optimalLambda = cvfit_L0$fit$lambda[[optimalGammaIndex]][optimalLambdaIndex]
L0_preds = predict(cvfit_L0, newx=X, lambda = optimalLambda, gamma = optimalGamma)@x
```


Pull base features of interest to create simplified data frame and append predictions
```{r}

#data = read.xlsx("C://PhD work//EOC-body-comp//De-ID Data Set for Moffitt 04032024.xlsx", 1)
# data = read.csv("C://PhD work//EOC-body-comp//De-ID Data Set for Moffitt 04032024.csv")
data <- moffitt_data

data = data %>%
  dplyr::select(survstat, survtime, ht_first_met, PRE_SMA_1, PRE_SUBQ_1, PRE_IMA_1, PRE_VAT_1, PRE_TAT_1) %>%
  mutate(SMI = PRE_SMA_1/ht_first_met) %>%
  mutate(SFI = PRE_SUBQ_1/ht_first_met) %>%
  mutate(VFI = PRE_VAT_1/ht_first_met) %>%
  mutate(IMAI = PRE_IMA_1/ht_first_met) %>%
  mutate(TATI = PRE_TAT_1/ht_first_met) %>% 
  mutate(SMD = PRE_SMA_1/PRE_IMA_1) %>%
  mutate(DMAI = 1.918519 + -0.001840*PRE_VAT_1/ht_first_met^2 + -0.041920*PRE_SMA_1/ht_first_met^2 + 0.004743*PRE_SUBQ_1/ht_first_met^2) %>%
  mutate(BCHI = SMD*DMAI) %>%
  dplyr::select(-ht_first_met) %>%
  mutate(across(everything(), as.numeric))

#SMD = SMA/IMA
res.cut <- surv_cutpoint(data, time = "survtime", event = "survstat",
   variables = c("SMD"))
plot(res.cut)
res.cat <- surv_categorize(res.cut)
logrank_SMD <- survdiff(Surv(survtime, survstat) ~ SMD, data = res.cat)
logrank_SMD

fit_SMD <- survfit(Surv(survtime, survstat) ~ SMD, data = res.cat)
ggsurvplot(fit_SMD, data = res.cat, risk.table = TRUE, conf.int = FALSE, pval = TRUE)

#BCHI = DMAI * SMD
res.cut <- surv_cutpoint(data, time = "survtime", event = "survstat",
   variables = c("BCHI"))
plot(res.cut)
res.cat <- surv_categorize(res.cut)
logrank_BCHI <- survdiff(Surv(survtime, survstat) ~ BCHI, data = res.cat)
logrank_BCHI

fit_BCHI <- survfit(Surv(survtime, survstat) ~ BCHI, data = res.cat)
ggsurvplot(fit_BCHI, data = res.cat, risk.table = TRUE, conf.int = FALSE, pval = TRUE)


#normal lasso
data$lasso_pred = lasso_preds[,1]
res.cut <- surv_cutpoint(data, time = "survtime", event = "survstat",
   variables = c("lasso_pred"))
plot(res.cut)
res.cat <- surv_categorize(res.cut)
logrank_lasso <- survdiff(Surv(survtime, survstat) ~ lasso_pred, data = res.cat)
logrank_lasso

fit_lasso <- survfit(Surv(survtime, survstat) ~ lasso_pred, data = res.cat)
ggsurvplot(fit_lasso, data = res.cat, risk.table = TRUE, conf.int = FALSE, pval = TRUE)

#normal lasso 1se
data$lasso_1se_pred = lasso_preds_1se[,1]
res.cut <- surv_cutpoint(data, time = "survtime", event = "survstat",
   variables = c("lasso_1se_pred"))
plot(res.cut)
res.cat <- surv_categorize(res.cut)
logrank_lasso_1se <- survdiff(Surv(survtime, survstat) ~ lasso_1se_pred, data = res.cat)
logrank_lasso_1se

fit_lasso_1se <- survfit(Surv(survtime, survstat) ~ lasso_1se_pred, data = res.cat)
ggsurvplot(fit_lasso_1se, data = res.cat, risk.table = TRUE, conf.int = FALSE, pval = TRUE)

#inference lasso
data$lasso_inf_pred = lasso_preds_inf[,1]
res.cut <- surv_cutpoint(data, time = "survtime", event = "survstat",
   variables = c("lasso_inf_pred"))
plot(res.cut)
res.cat <- surv_categorize(res.cut)
logrank_lasso_inf <- survdiff(Surv(survtime, survstat) ~ lasso_inf_pred, data = res.cat)
logrank_lasso_inf

fit_lasso_inf <- survfit(Surv(survtime, survstat) ~ lasso_inf_pred, data = res.cat)
ggsurvplot(fit_lasso_inf, data = res.cat, risk.table = TRUE, conf.int = FALSE, pval = TRUE)

#lar selectiveinference package
data$lar_pred = lar_preds
res.cut <- surv_cutpoint(data, time = "survtime", event = "survstat",
   variables = c("lar_pred"))
plot(res.cut)
res.cat <- surv_categorize(res.cut)
logrank_lar <- survdiff(Surv(survtime, survstat) ~ lar_pred, data = res.cat)
logrank_lar

fit_lar <- survfit(Surv(survtime, survstat) ~ lar_pred, data = res.cat)
ggsurvplot(fit_lar, data = res.cat, risk.table = TRUE, conf.int = FALSE, pval = TRUE)

#lar lars package
data$lars_lar_pred = lar_lars_preds
res.cut <- surv_cutpoint(data, time = "survtime", event = "survstat",
   variables = c("lars_lar_pred"))
plot(res.cut)
res.cat <- surv_categorize(res.cut)
logrank_lars_lar <- survdiff(Surv(survtime, survstat) ~ lars_lar_pred, data = res.cat)
logrank_lars_lar

fit_lars_lar <- survfit(Surv(survtime, survstat) ~ lars_lar_pred, data = res.cat)
ggsurvplot(fit_lars_lar, data = res.cat, risk.table = TRUE, conf.int = FALSE, pval = TRUE)

#L0
data$L0_pred = L0_preds
res.cut <- surv_cutpoint(data, time = "survtime", event = "survstat",
   variables = c("L0_pred"))
plot(res.cut)
res.cat <- surv_categorize(res.cut)
logrank_L0 <- survdiff(Surv(survtime, survstat) ~ L0_pred, data = res.cat)
logrank_L0

fit_L0 <- survfit(Surv(survtime, survstat) ~ L0_pred, data = res.cat)
ggsurvplot(fit_L0, data = res.cat, risk.table = TRUE, conf.int = FALSE, pval = TRUE)

```



